### 2016-03-16 paper/Paper.tex
bugifx in the code in refund()

\documentclass[9pt,oneside]{amsart}
\usepackage{url}
\usepackage{cancel}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{hyperref}

\newcommand{\hcancel}[1]{%
    \tikz[baseline=(tocancel.base)]{
        \node[inner sep=0pt,outer sep=0pt] (tocancel) {#1};
        \draw[black] (tocancel.south west) -- (tocancel.north east);
    }%
}%

\definecolor{lightyellow}{rgb}{1,0.98,0.9}
\definecolor{lightpink}{rgb}{1,0.94,0.95}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\newcommand*\eg{e.g.\@\xspace}
\newcommand*\Eg{e.g.\@\xspace}
\newcommand*\ie{i.e.\@\xspace}
%\renewcommand{\itemhook}{\setlength{\topsep}{0pt}  \setlength{\itemsep}{0pt}\setlength{\leftmargin}{15pt}}

\title{Decentralized autonomous organization to manage a trust\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}}
\author{
    Christoph Jentzsch\\
    Founder \& CTO, Slock.it\\
    christoph.jentzsch@slock.it
}
\begin{document}

\begin{abstract}
This document describes the first implementation of a Decentralized Autonomous Organization (DAO) decentralizing the management of a trust. This concept, as well as the majority robbing the minority attack vector are discussed, and a solution is proposed. Furthermore, a practical implementation of this type of DAO using smart contracts written in Solidity on the Ethereum blockchain is presented and described in detail.
\end{abstract}

\maketitle

\setlength{\columnsep}{20pt}
\begin{multicols}{2}

\section{Introduction}\label{sec:introduction}

Historically, the management of trusts has always been centralized. A group of individuals (trustees) would write a contract and combine their resources into one trust, which was then managed by a single person or company, with the trustees losing the power to directly control their money. The rise of crowdfunding (\cite{2015CFReport}), has lowered the barrier of entry to fund projects and has allowed for small contributors to participate in large projects. The money raised still carries the risk of being mismanaged by the company receiving the funding which all too often fails to follow through on its promises or outright disappears without a trace (\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}). Thanks to the development of Ethereum (\cite{buterin2013ethereum,Wood2014ethereum}), a blockchain technology which integrates a Turing complete programming language and the ability to process smart contracts, it is now possible to create an organization allowing the “trustees” to maintain direct control of their funds while still bundling many smaller contributions together to achieve a larger goal. We have written smart contracts (\cite{szabo1997formalizing, miller1997future}) that form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain. In this paper we detail the concept of a DAO managing a trust using a concrete example.

After explaining the concept of the DAO, we will cover the ``Majority Robbing the Minority Attack'' and propose a solution, the ``DAO split''. Finally, we will explore the smart contracts and conclude with a more detailed specification of the ``DAO split''.

The code for the smart contracts is located at: \url{https://github.com/slockit/DAO/}

\section{Concept}
This section will cover the underlying concept of the DAO and what it is able to do.

After the DAO is deployed on the Ethereum blockchain, anyone is able to fund it by sending ether (the digital fuel powering the Ethereum network) to the address of the DAO’s smart contract during a period of time set aside for the initial funding. In exchange, tokens are created which represent membership as well as ownership of a portion of the DAO; these tokens are assigned to the account that sent the ether. The amount of tokens created is proportional to the amount of ether transferred. The price per token varies over time (see section \ref{TokenPrice}). The ownership of these tokens can be transferred to other accounts using transactions on the Ethereum blockchain, as soon as the funding period is over.
When deploying the contract, a minimum DAO funding goal and the period of time allowed for the initial funding are chosen. In the event the minimum funding amount is not reached at the end of the funding period, every contributor is refunded their ether. After the funding period has ended, we denote the total ether raised by $\Xi_{\text{raised}}$ and the total amount of tokens created by $T_{\text{total}}$. 
This DAO purely manages funds. In itself, it does not have the capabilities to build a product, write code or develop hardware. It requires a service provider to accomplish these and other goals, which it hires by signing off on a proposal. Every member of the DAO is allowed to submit proposals to spend a portion of the total ether raised, denoted by $\Xi_{\text{transfer}}$, on funding projects. If the proposal is approved, the ether is sent to another smart contract representing the proposed project. Such smart contracts can be parameterized and enable the DAO to interact with and influence the project being funded.
An example of such an agreement between the DAO and a project to be funded can be found in the appendix (\ref{app:SampleOffer}).

Members of the DAO cast votes weighted by the amount of tokens they control.  Tokens are divisible, indistinguishable, fungible and can easily be transferred between accounts. Within the contracts, the individual actions of members, cannot be directly determined. There is a set timeframe $t_p$ to debate and vote on any given proposal. In our example, this timeframe is set by the creator of the proposal, and is required to be at least two weeks for a regular proposal.

After $t_p$ has passed, any token holder can call a function in the DAO contract that will verify that the majority voted in favor of the proposal and that quorum was reached; the function will execute the proposal if this is the case. If this is not the case, the proposal will be closed. The minimum quorum represents the minimum number of tokens required for a vote to be valid, is denoted by $q_{min}$, and calculated as follows:
\begin{equation}
 q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{total}})}
 \label{minQuorum}
\end{equation}
Where $d$ is the \verb|minQuorumDivisor|. This parameter’s default value is $5$, but it will double in the case the quorum has not been met for over a year.
$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward token as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}). The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received.

This means, initially a quorum of  $20\%$ of all tokens is required for any proposal to pass. In the event $\Xi_{\text{transfer}}$ equals the amount of ether raised during the funding period plus the rewards received, then a quorum of $53.33\%$ is required.

In order to prevent proposal spam, a minimal deposit is required to be paid when creating a proposal, which gets refunded if quorum is achieved, if quorum is not achieved, the proposal deposit stays with the DAO. The value of the proposal deposit can be changed from the default value by the DAO through another proposal.

\section{Notation}
Throughout this paper, $\Xi$ always represents an amount of ether in its base unit wei. Which is defined as $1 \: \text{Wei} = 10^{-18} \: \text{Ether}$ (\cite{Wood2014ethereum}).
Similarly, DAO tokens are denoted with $T$ and always represent the amount of DAO tokens in its base unit. Which we define as $10^{-16}$ DAO token.
\section{Majority robs minority attack}
A problem every DAO has to mitigate is the ability for the majority to rob the minority. An attacker with $51\%$ of the tokens, acquired either during the funding period or purchased afterwards, could make a proposal to send all the funds to themselves. Since they would hold the majority of the tokens, they would always be able to pass their proposals.

To prevent this, the minority always needs the option to retrieve their portion of the funds. This is done by splitting the DAO into two. In the case an individual, or a group of token holders, strongly disagree with a proposal and want to retrieve their portion of the funds before the proposal gets executed, they can submit a special type of proposal to form a new DAO. The minority can then vote to move their funds to this new DAO, leaving the majority alone only able to spend their own money.
This idea originates from a blog post by Vitalik Buterin (\cite{Vitalik2015subjectivity}).

A problem this simple fix doesn’t address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely. An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some of them could be unaware of the situation and won't do this. For the DAO to be considered safe, it is required that inactive token holders will not lose their funds. Our proposed solution is implemented by limiting each individual DAO to a single service provider. This service provider controls the only account that can receive ether from the DAO, across all proposals. In addition, the service provider can build a “whitelist” of addresses that the DAO is allowed to send funds to. This gives the service provider of the DAO considerable power. To prevent the abuse of this power, it is possible for the DAO to vote for a new service provider, which may result in a split of the DAO as described above.

Any token holder can make a proposal to vote for a new service provider. In effect, even a single token holder is able to both retrieve their remaining portion of ether and maintain their right to any future rewards associated to their previous contribution, as these will be sent to the new DAO automatically. Rewards are defined as any ether received by the DAO generated from products the DAO funded so far and are explained in further detail in section \ref{RewardToken}.

The process of choosing a new service provider is as follows:
Any token holder can start a proposal to vote for a new service provider. For this proposal there is no proposal deposit to be paid, otherwise the attacker could vote for an extremely high deposit, preventing any splits. The debating period for this proposal is $10$ days.
This is $4$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through. There is no quorum requirement, so that every token holder has the ability to split into their own DAO. 
The debating period is used to discuss the new service provider and conduct an informal vote. The result of the vote has no actual consequence, it is purely instructional. After this first voting round, token holders can cast a second vote to confirm the result. In the case a majority opts to  keep the original service provider, the minority can either change their vote to keep the original service provider in order to avoid a split, or inversely they can confirm their vote for a new service provider and move their portion of the funds to a new DAO.

\section{Token Price} \label{TokenPrice}
In order to reward contributors who purchase tokens early during the funding period, since they had less information, and hence a greater risk, than contributors who joined later, they will pay less than contributors who joined later.
For the DAO described here, we have chosen the following price schedule:
\begin{equation}
 P(t) = \begin{cases}
0.01 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
0.01 + 0.005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
0.015 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in it’s base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether payed, denoted in wei.
This results in a constant price in the beginning, until $2$ weeks before the end of the token sale. At this time the price increased daily by $0.005 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant price of $0.015 \: \Xi_c$ per base unit of DAO token.

This price increase leads to a situation where a single contributor, who has bought tokens during the initial price, can split the DAO right after the end of the sale and would get more ether out than they put in due to other contributors paying a higher price (\cite{GriffDiscussion}).
In order to avoid that possibility, all ether that is payed above the initial price of the token, will be sent to an extra account. Denoted as \verb|extraBalance| in \ref{app:TokenSale}. This money can be sent back to the DAO through a proposal after the DAO has spent at least this amount of ether.
This rule is implemented in the internal function \verb|isRecipientAllowed| in section \ref{DAO}.

\section{Contracts}
This section will detail the smart contracts implementing the aforementioned concept. The contracts are written in the programming language Solidity (\cite{ReitwiessnerWoodSolidity}).
Each contract has member variables and functions which can be externally called by sending a transaction to the Ethereum network with the DAO contract address as the recipient and the method ID (optional with parameters) as data. In this section we will discuss the meaning of the variables and the functions in detail.

The main contract is called 'DAO'. It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenSale'. ‘Token’ defines the inner workings of the DAO Token and ‘TokenSale’ defines how the DAO token is purchased for ether. In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from the service provider to the DAO could look like.
\end{multicols}

\subsection{Token}
\begin{verbatim}
contract TokenInterface {
    mapping (address => uint256) balances;
    mapping (address => mapping (address => uint256)) allowed;
    uint256 public totalSupply;
    function balanceOf(address _owner) constant returns (uint256 balance);
    function transfer(address _to, uint256 _amount) returns (bool success);
    function transferFrom(address _from, address _to, uint256 _amount) returns (bool success);
    function approve(address _spender, uint256 _amount) returns (bool success);
    function allowance(address _owner, address _spender) constant returns (uint256 remaining);

    event Transfer(address indexed _from, address indexed _to, uint256 _amount);
    event Approval(address indexed _owner, address indexed _spender, uint256 _amount);
}
\end{verbatim} 
\begin{multicols}{2}

Above is the interface of the ‘Token’ contract. The interfaces of these contracts are used in the text of this document to give a simple overview of the functions and variables used in the contract, the full implementation can be found in the appendix (\ref{app:Token}). This contract represents the standard token as described here:
\url{https://github.com/ethereum/wiki/wiki/Standardized_Contract_APIs}, and the contract \url{https://github.com/ConsenSys/Tokens/blob/master/Token_Contracts/contracts/Standard_Token.sol} was used as a starting point for the contract’s creation.

The map \verb|balances| stores the number of DAO tokens which are controlled by an address. All contracts which derive from \verb|TokenInterface| can directly modify this map, but only $4$ functions do so: \verb|buyTokenProxy|, \verb|transfer| , \verb|transferFrom| and \verb|splitDAO|.

The map \verb|allowed| is used to track the previously specified addresses that are allowed to send tokens on someone else's behalf.

The integer \verb|totalSupply| is the total number of DAO tokens in existence. The \verb|public| keyword creates a function with the same name as the variable which returns its value so that it is publically available.

The function \verb|balanceOf| returns the balance of the specified address.

The function \verb|transfer| is used to send token from the sender of the message to another address.

The function \verb|transferFrom| is used to transfer tokens on behalf of someone else who has approved the transfer in advance using the \verb|approve| function.

The function \verb|approve| can be used by the DAO token owner to specify a certain \verb|spender| to transfer a specified \verb|value| from their account using the \verb|transferFrom| function. To check whether a certain address is allowed to spend DAO tokens on behalf of someone else, the \verb|allowance| function can be used, which returns the number of tokens which can be spent by the \verb|spender|. This is similar to writing a check.

The event \verb|Transfer| is used to inform lightweight clients about changes in \verb|balances|.

The event \verb|Approval| is used to inform lightweight clients about changes in \verb|allowed|.
\end{multicols}

\subsection{TokenSale}
\begin{verbatim}
contract TokenSaleInterface {
    uint public closingTime;   
    uint public minValue;  
    bool public isFunded;   
    address public privateSale;
    ManagedAccount extraBalance;
    mapping (address => uint256) weiGiven;

    function TokenSale(uint _minValue, uint _closingTime);
    function buyTokenProxy(address _tokenHolder) returns (bool success);
    function refund();
    function divisor() returns (uint divisor);

    event FundingToDate(uint value);
    event SoldToken(address indexed to, uint amount);
    event Refund(address indexed to, uint value);
}
\end{verbatim}
\begin{multicols}{2}
Above is the interface of the \verb|TokenSale| contract (\ref{app:TokenSale}).

The integer \verb|closingTime| is the (unix) time at which the token sale ends.

The integer \verb|minValue| is the number of wei which are needed to be received by the DAO in order to get funded.

The boolean \verb|isFunded| is true if DAO has reached its minimum funding goal, false otherwise.

The address \verb|privateSale| is used for DAO splits - if it is set to 0, then it is a public sale, otherwise, only the address stored in \verb|privateSale| is allowed to purchase tokens.

The managed account (\ref{app:ManagedAccount}) \verb|extraBalance| is used to hold the excess ether which is received after the token price is increased during the sale. Anything that has been paid above the initial price goes to this account.

The map \verb|weiGiven| stores the amount of wei given by each contributor during the sale and is only used to refund the contributors if the Token sale does not reach its funding goal.

The constructor \verb|TokenSale| initiates the token sale with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateSale|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed.

The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$. Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time as described in section \ref{TokenPrice}.

The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.

The function \verb|refund| can be called by any contributor to recieve their wei back if the token sale failed to meet its funding goal.

The function \verb|divisor| is used to calculate the price of the token during the sale in the function \verb|buyTokenProxy|.

The events \verb|FundingToDate|, \verb|SoldToken| and \verb|Refund| are used to inform lightweight clients of the status of the token sale.
\end{multicols}

\subsection{DAO} \label{DAO}
\begin{verbatim}
contract DAOInterface {
    Proposal[] public proposals;
    uint minQuorumDivisor;
    uint lastTimeMinQuorumMet;
    uint public rewards;
    address[] public allowedRecipients;
    mapping (address => uint) public rewardToken;
    uint public totalRewardToken;
    ManagedAccount public rewardAccount;
    mapping (address => uint) public paidOut;
    mapping (address => uint) public blocked;
    uint public proposalDeposit;
    DAO_Creator public daoCreator;

    struct Proposal {
        address recipient;
        uint amount;
        string description;
        uint votingDeadline;
        bool open;
        bool proposalPassed;
        bytes32 proposalHash;
        uint proposalDeposit;
        bool newServiceProvider;
        SplitData[] splitData;
        uint yea;
        uint nay;
        mapping (address => bool) votedYes;
        mapping (address => bool) votedNo;
        address creator;
    }

    struct SplitData {
        uint splitBalance;
        uint totalSupply;
        uint rewardToken;
        DAO newDAO;
    }

    modifier onlyTokenholders {}

    function DAO(
        address _defaultServiceProvider,
        DAO_Creator _daoCreator,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    )
    function () returns (bool success);
    function payDAO() returns(bool);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool _newServiceProvider
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function addAllowedAddress(address _recipient) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function isBlocked(address _account) returns (bool);

    event ProposalAdded(
        uint indexed proposalID,
        address recipient,
        uint amount,
        bool newServiceProvider,
        string description
    );
    event Voted(uint indexed proposalID, bool position, address indexed voter);
    event ProposalTallied(uint indexed proposalID, bool result, uint quorum);
    event NewServiceProvider(address indexed _newServiceProvider);
    event AllowedRecipientAdded(address indexed _recipient);
}

\end{verbatim}
\begin{multicols}{2}
The original contract used as a starting point for ‘’DAO’’ was: \url{http://chriseth.github.io/browser-solidity/?gist=192371538cf5e43e6dab} as described in 
\url{https://blog.ethereum.org/2015/12/04}. The main feature added is the splitting mechanism and all that comes with it.
Now we will define the member variables and functions one at a time.

The array \verb|proposals| holds all the proposals ever made.

The integer \verb|minQuorumDivisor| is used to calculate the quorum needed for a proposal to pass. It is set to $5$, but will double in the case a quorum has not been reached for over a year.

The integer \verb|lastTimeMinQuorumMet| keeps track of the last time the quorum was reached.

The integer \verb|rewards| counts all the rewards which have been sent to the DAO. It gets set to zero when paid out to the \verb|rewardAccount|.

The address \verb|serviceProvider| is set at the creation of the DAO and defines the service provider.

The list \verb|allowedRecipients| is commonly referred to as ‘’the whitelist.’’ The DAO can only send transactions to itself, the \verb|serviceProvider|, \verb|rewardAccount|, \verb|extraBalance| and addresses in the whitelist. Only the \verb|serviceProvider| can add addresses to the whitelist.

The map \verb|rewardToken| tracks the addresses that are owed rewards generated by the products of the DAO. Those addresses can only be DAOs.

The integer \verb|totalRewardToken| tracks the amount of reward tokens in existence.

The variable \verb|rewardAccount| is of the type \verb|ManagedAccount| , which will be discussed in \ref{app:ManagedAccount}. It is used to manage the rewards which are to be distributed to the DAO Token Holders and reward token holders.

The map \verb|paidOut| is used to keep track how much wei a single token holder has already retrieved from \verb|rewardAccount|.

The map \verb|blocked| stores the addresses of the DAO Tokens that have voted and therefore are not allowed to be transferred until the vote has concluded.. The address points to the proposal ID.

The integer \verb|proposalDeposit| specifies the minimum deposit to be paid in wei for any proposal that does not include a change in service providers.

The contract \verb|daoCreator| is used to create a new DAO with the same code as this DAO, used in the case of a split.

A single proposal has the parameters:
\begin{description}
 \item[recipient] The address where the \verb|amount| of wei will go to if the proposal is accepted.
 \item[amount] The amount of wei to transfer to \verb|recipient| if the proposal is accepted.
 \item[description] A plain text description of the proposal.
 \item[votingDeadline] A unix timestamp, denoting the end of the voting period.
 \item[open] A boolean which is false if the votes have already been counted, true otherwise.
 \item[proposalPassed] A boolean which is true if a quorum has been achieved with the majority approving the proposal.
 \item[proposalHash] A hash to check validity of a proposal. Equal to \verb|sha3(_recipient, _amount, _transactionData)|.
 \item[proposalDeposit] The minimum deposit (in wei) the creator of a proposal is required to send to submit a proposal. It is taken from the \verb|msg.value| of a \verb|newProposal| call; its purpose is to prevent spam. It is set to $20$ ether by default but the creator of the proposal can send any amount above this for the deposit.For Slock.it’s purposes, the proposals will be sorted by the proposal deposit in the GUI, so in the case that a proposal is considered important, the creator of the proposal can deposit extra ether to “advertise” their proposal. The creator of the proposal will be refunded the entire deposit if quorum is reached, if it is not reached the deposit remains with the DAO. 
 \item[newServiceProvider] A boolean which is true if this proposal assigns a new service provider.
 \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new service provider.
 \item[yea] Number of tokens in favor of the proposal.
 \item[nay] Number of tokens in opposed to the proposal.
 \item[votedYes] Simple mapping to check if a token holder has voted for it.
 \item[votedNo] Simple mapping to check if a token holder has voted against it.
 \item[creator] The address of the token holder that created the proposal.
\end{description}

The split data structure is used to split the DAO. It contains:
\begin{description}
 \item[splitBalance] The balance of the current DAO minus the proposal deposit at the time of split.
 \item[totalSupply] The total amount of DAO tokens in existence at the time of the split.
 \item[rewardToken] The amount of reward tokens owned by the original DAO at the time of split.
 \item[newDAO] The address of the new DAO contract ($0$ if not created yet).
\end{description}

Those are all the member variables which are stored in this smart contract on the blockchain. This information can at any time be read from the blockchain using an Ethereum client.

We will now discuss the functions of the DAO contract in detail. Many of the member variables that are used in this contract are defined in one of the other three contracts.

There is a special function which is called the constructor. It has the same name as the contract ``DAO''. This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|serviceProvider|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount| 
 \item \verb|minValue|
 \item \verb|closingTime|
 \item \verb|privateSale|
\end{itemize}

In order to interact with the smart contract the following functions are used:

\subsubsection*{fallback function}
The fallback function is a function without a specific name. It is called when the contract receives a transaction without data (a pure value transfer). There are no direct arguments for this function.
The fallback function will call \verb|buyTokenProxy| passing the address of the sender as an argument during the token sale. This will trigger the immediate purchase of tokens. In order to protect users, this function will send the ether received after the end of the sale back to the sender for a time period of $40$ days. After which this function is repurposed to receive ether as simple deposit to the DAO using the function \verb|receiveEther|.

\subsubsection*{payDAO}
This function is used to receive and track the rewards generated by the products funded by the DAO and returns true when ether has been added to \verb|rewards|. In the context of Slock.it, these will be the rewards generated when Slocks are deployed or used.

\subsubsection*{receiveEther}
A simple function used to receive ether. It does nothing but return true when the DAO receives ether.

\subsubsection*{newProposal}
This function is used to create a new proposal. The arguments of the function are:
\begin{description}
 \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current service provider or an address on the whitelist \verb|allowedRecipients|).
 \item[amount] The amount of wei to be sent in the proposed transaction.
 \item[description] A string describing the proposal.
 \item[transactionData] The data of the proposed transaction.
 \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 10 days for a new service provider proposal.
 \item[newServiceProvider] A boolean defining whether this proposal is for a new service provider or not.
\end{description}
After checking the sanity of the proposal (see code), this function creates a proposal which is open for voting for a certain amount of time. The function will return a proposal ID which is used to vote.

\subsubsection*{checkProposalCode}
This function is used to check that a certain proposal ID matches a certain transaction.
The arguments of the function are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[recipient] The address of the recipient of the proposed transaction.
 \item[amount] The amount of wei to be sent with the proposed transaction.
 \item[transactionData] The data of the proposed transaction.
\end{description}
If the \verb|recipient|,  the \verb|amount| and the \verb|transactionData| match the proposal ID, the function will return \verb|true| , otherwise it will return \verb|false|. This will be used to verify that the proposal ID matches what the DAO token holder thinks they are voting on.

\subsubsection*{vote}
This function is used to vote on a proposal. The arguments of the function are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[supportsProposal]  A boolean Yes/No does the DAO token holder support the proposal
\end{description}
The function simply checks whether the sender has yet to vote and whether the proposal is still open for voting. If both requirements are met, it records the vote in the storage of the contract. The tokens used to vote will be blocked, meaning they can not be transferred until the proposal is closed.This is to avoid voting several times with different sender addresses.

\subsubsection*{executeProposal}
This function can be called by anyone. It counts the votes, in order to check whether the quorum is met, and executes the proposal if it passed, unless it is a proposal for a new service provider, than it does nothing.
The arguments of the function are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[transactionData] The data of the proposed transaction
\end{description}
The function checks whether the voting deadline has passed and that the \verb|transactionData| matches the proposal ID. Then it checks whether the quorum has been met (see Eq. \ref{minQuorum}) and if the proposal had a majority of support. If this is the case, it executes the proposal and refunds the 
proposal deposit. If the quorum has been achieved, but the proposal was declined by the majority of the voters, the proposal deposit is refunded and the proposal closes.

\subsubsection*{splitDAO}
After a new service provider has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new service provider. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newServiceProvider] The address of the new service provider of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively buy tokens of the newly created DAO and fund the new DAO just as the original DAO was funded.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|getMyReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed.

\subsubsection*{transfer and transferFrom}
These functions overload the functions defined in the \verb|Token| contract. They do call \verb|transfer / transferFrom| function in the \verb|Token| contract, but they additionally transfer information about the already paid out rewards attached to the tokens being transferred using the \verb|transferPaidOut| function.

\subsubsection*{transferPaidOut}
This function is called to when making any transfer of DAO tokens using \verb|transfer| or \verb|transferFrom| and it updates the array \verb|paidOut| to track the amount of rewards which has been paid out already, $P$, and is calculated as follows:
\begin{equation}
 P = P_{\text{from}} \cdot T_{\text{amount}} / T_{\text{from}}
\end{equation}
Here $P_{\text{from}}$ is the total amount of ether which has been paid out to the \verb|from| address (the sender), $T_{\text{amount}}$ is the amount of tokens to be transferred and $T_{\text{from}}$ the amount of tokens owned by the \verb|from| address.

\subsubsection*{transferWithoutReward and transferFromWithoutReward}
The same as \verb|transfer| and \verb|transferFrom|, but it calls \verb|getMyReward| prior to that.

\subsubsection*{getMyReward}
Calls \verb|withdrawRewardFor| with the sender as the parameter. This is used to withdraw the portion of the rewards which belong to the sender from the \verb|rewardAccount|.

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
Their portion $S$ is calculated as follows:
\begin{equation}
 S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender. $R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut}}[\text{sender}]
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut}}[\text{sender}]$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.
\subsubsection*{addAllowedAddress}
This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.

\subsubsection*{halveMinQuorum}
When called, halves the minimum quorum in the case it has not been met for over 52 weeks, by doubling \verb|minQuorumDivisor|.

\subsubsection*{numberOfProposals}
Returns the total number of proposals ever created.

\subsubsection*{isBlocked}
This function returns true when the address given as parameter is currently blocked to transfer tokens due to an ongoing vote it has participated in, otherwise it returns false.

\subsubsection*{changeProposalDeposit}
This function changes the parameter \verb|proposalDeposit|. It can only be called by the DAO through a transaction which was proposed and voted for by a majority of the token holders.

\end{multicols}

\subsection{Managed Account}
\begin{verbatim}
 contract ManagedAccountInterface {
    address public owner;
    uint public accumulatedInput;

    function payOut(address _recipient, uint _amount) returns (bool);

    event PayOut(address _recipient, uint _amount);
}
\end{verbatim}
\begin{multicols}{2}
This contract is used to manage the rewards and the \verb|extraBalance| (as explained in section \ref{TokenPrice}). It has two member variables:

The address \verb|owner|, is the only address with permission to withdraw from that account (in our case the DAO) and send ether to another address using the \verb|payOut| function.

The integer, \verb|accumulatedInput|, represents the total sum of ether (in wei) which has been sent to this contract so far.

The fallback function is called when the contract receives a transaction without data (a pure value transfer). There are no direct arguments for this function. When it is called it counts the amount of ether it receives and stores it in \verb|accumulatedInput|.

The function \verb|payOut| can only be executed by the \verb|owner| (in our case the DAO). It has two arguments: \verb|recipient| and \verb|amount|. It is used to send \verb|amount| wei to a \verb|recipient| and is called by \verb|getMyReward| in the DAO contract.

\section{Reward Tokens} \label{RewardToken}

In this section we give a description of how reward tokens are implemented in this contract. Much of the information has already been explained, but it is restated here for clarity.

Reward tokens are used to divide the ether sent to \verb|rewardAccount| amongst the various DAOs that own reward tokens. Reward tokens are only transferred in the event of a DAO split, they can never be owned by anything other than the original DAO or a “fork” of the original DAO that generated the reward tokens.

Reward tokens are generated when the DAO makes any transaction spending ether (with the exception of sending ether to the \verb|rewardAccount|). When the DAO’s products send ether back to the DAO (for example when a Slock sends $1\%$ of a transaction to the DAO), the ether is held with the rest of the ether that the DAO has, but \verb|rewards| counts all the ether which has been received as rewards. The DAO can use these rewards to fund new proposals or to equally distribute the rewards to the reward token holders (using a proposal which gets voted on by the DAO token holders). Then the token holders of the DAOs that hold reward tokens will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token. To do this the DAO will send the accumulated rewards to the \verb|rewardAccount| which is held in the \verb|ManagedAccount| contract. Then and only then will the token holders of the DAOs that hold reward tokens be able to call the \verb|getMyReward| function and receive their ether. These payouts are tracked by the map \verb|paidOut| which keeps track of which DAOs hold reward tokens and whether they have claimed their portion of the rewards, and which of the original DAO token holders have claimed their fair portion of the rewards.This process guarantees that any DAO token holder whose ether was spent building a product will receive the rewards promised to them from that product even if they decide to split from the DAO.

\section{Split} \label{split}

In this section we want to formally describe some parameters and their behavior during a split.

The total amount of DAO tokens \verb|totalSupply| is defined as follows:
\begin{equation}
T_{\text{total}} = \sum_{i=0}^{2^{256}-1} T_i
\end{equation}
Where $T_i$ is the amount of DAO tokens owned by an address $i$ (\verb|balances[i]|). Note that  $2^{256}$ is the total number of possible addresses in Ethereum.
Similarly, the amount of reward tokens $R_{\text{total}}$ is defined as follows:
\begin{equation}
 R_{\text{total}} = \sum_{i=0}^{2^{256}-1} R_i = \sum_{p=0; p.proposalPassed = true}^{numProposals} p.amount
\end{equation}
For every passed proposal that sends ether out of the DAO, an amount of reward tokens equal to the amount being spent (in wei) is created.

Let’s assume that during the split, a fraction of DAO tokens, $X$, changes service providers and leaves the DAO. The new DAO created receives $X \cdot \Xi_{\text{DAO pre}}$, a portion of the remaining ether from the original DAO.
\begin{equation}
 \Xi_{\text{DAO post}} = (1 - X) \cdot \Xi_{\text{DAO pre}}
\end{equation}
Here $\Xi_{\text{DAO pre}}$ is the ether balance of the original DAO before the split and $\Xi_{\text{DAO post}}$ is the ether balance of the original DAO after the split.

A portion of the reward tokens is transferred to the new DAO in a very similar manner:
\begin{equation}
 R_{\text{DAO post}} = (1 - X) \cdot R_{\text{DAO pre}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO (prior to the first split $100\%$ of all rewards tokens ever created are owned by the DAO).
\begin{equation}
 R_{\text{newDAO}} = (X) \cdot R_{\text{DAO pre}}
\end{equation}
The number of reward tokens owned by the new DAO are denoted by $R_{\text{newDAO}}$.
The total amount of reward tokens $R_{\text{total}}$ stays constant during the split, no reward tokens are ever destroyed.

The original DAO tokens of the accounts that confirmed the new service provider are destroyed.
Hence:
\begin{equation}
 T_{\text{total post}}= (1 - X) \cdot T_{\text{total pre}}
\end{equation}

This process allows DAO token holders to retrieve their ether from the DAO at any time without losing out on any of the future rewards they are entitled to receive even if they choose to leave the DAO.

\section{Updates}
Although the code of the contract specified at a certain address in the Ethereum blockchain can not be changed, there might still be a need for a single member or the DAO as a whole to change the contracts.
Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to send all the ether in the old DAO to this contract.
If accepted, the complete DAO moves to the new contract. In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens. In the new contract this right should only be usable in restricted functions which are only callable by the owner of the tokens. This process allows for the DAO to maintain static immutable code on the Ethereum blockchain, while still being able to be updated if the need arises.

\section{Acknowledgements}
I want to thank Stephan Tual and Simon Jentzsch for fruitful discussions and corrections, as well as Gavin Wood and Christian Reitwiessner for a review of the contracts and the development of Solidity, the programing language used to write the contracts.

Special thanks goes to Yoichi Hirai and Lefteris Karapetsas for reviewing the smart contracts and making significant improvements.

I also want to thank Griff Green for reviewing and editing the paper.

Last but not least I want to thank our community which has given feedback, corrections and encouragement.

\end{multicols}

\bibliography{Biblio}
\bibliographystyle{plainnat}
\begin{appendix}

\section{Contracts}
\subsection{Token}\label{app:Token}
\begin{verbatim}
contract TokenInterface {
    mapping (address => uint256) balances;
    mapping (address => mapping (address => uint256)) allowed;

    /// @return Total amount of tokens
    uint256 public totalSupply;

    /// @param _owner The address from which the balance will be retrieved
    /// @return The balance
    function balanceOf(address _owner) constant returns (uint256 balance);

    /// @notice Send `_amount` tokens to `_to` from `msg.sender`
    /// @param _to The address of the recipient
    /// @param _amount The amount of tokens to be transferred
    /// @return Whether the transfer was successful or not
    function transfer(address _to, uint256 _amount) returns (bool success);

    /// @notice Send `_amount` tokens to `_to` from `_from` on the condition it 
    /// is approved by `_from`
    /// @param _from The address of the sender
    /// @param _to The address of the recipient
    /// @param _amount The amount of tokens to be transferred
    /// @return Whether the transfer was successful or not
    function transferFrom(address _from, address _to, uint256 _amount) 
        returns (bool success);

    /// @notice `msg.sender` approves `_spender` to spend `_amount` tokens on 
    /// its behalf
    /// @param _spender The address of the account able to transfer the tokens
    /// @param _amount The amount of tokens to be approved for transfer
    /// @return Whether the approval was successful or not
    function approve(address _spender, uint256 _amount) returns (bool success);

    /// @param _owner The address of the account owning tokens
    /// @param _spender The address of the account able to transfer the tokens
    /// @return Amount of remaining tokens of _owner that _spender is allowed 
    /// to spend
    function allowance(address _owner, address _spender) 
        constant 
        returns (uint256 remaining);

    event Transfer(address indexed _from, address indexed _to, uint256 _amount);
    event Approval(
        address indexed _owner, 
        address indexed _spender, 
        uint256 _amount
    );
}

contract Token is TokenInterface {
    // Protects users by preventing the execution of method calls that 
    // inadvertently also transferred ether
    modifier noEther() {if (msg.value > 0) throw; _}

    function balanceOf(address _owner) constant returns (uint256 balance) {
        return balances[_owner];
    }

    function transfer(address _to, uint256 _amount) 
        noEther 
        returns (bool success) 
    {
        if (balances[msg.sender] >= _amount && _amount > 0) {
            balances[msg.sender] -= _amount;
            balances[_to] += _amount;
            Transfer(msg.sender, _to, _amount);
            return true;
        }
        else
           return false;
    }

    function transferFrom(address _from, address _to, uint256 _amount) 
        noEther 
        returns (bool success) 
    {
        if (balances[_from] >= _amount 
            && allowed[_from][msg.sender] >= _amount 
            && _amount > 0
        ) {
            balances[_to] += _amount;
            balances[_from] -= _amount;
            allowed[_from][msg.sender] -= _amount;
            Transfer(_from, _to, _amount);
            return true;
        }
        else
            return false;
    }

    function approve(address _spender, uint256 _amount) returns (bool success) {
        allowed[msg.sender][_spender] = _amount;
        Approval(msg.sender, _spender, _amount);
        return true;
    }

    function allowance(address _owner, address _spender) 
        constant 
        returns (uint256 remaining) 
    {
        return allowed[_owner][_spender];
    }
}
\end{verbatim}

\subsection{TokenSale}\label{app:TokenSale}
\begin{verbatim}
contract TokenSaleInterface {

    // End of token sale, in Unix time
    uint public closingTime;   
    // Minimum funding goal of the token sale, denominated in tokens
    uint public minValue;  
    // True if the DAO reached its minimum funding goal, false otherwise
    bool public isFunded;   
    // For DAO splits - if privateSale is 0, then it is a public sale, otherwise
    // only the address stored in privateSale is allowed to purchase tokens
    address public privateSale;
    // hold extra ether which has been paid after the DAO token price has increased
    ManagedAccount extraBalance;
    // tracks the amount of wei given from each contributor (used for refund)
    mapping (address => uint256) weiGiven;

    /// @dev Constructor setting the minimum funding goal and the 
    /// end of the Token Sale
    /// @param _minValue Token Sale minimum funding goal
    /// @param _closingTime Date (in Unix time) of the end of the Token Sale
    // This is the constructor: it can not be overloaded so it is commented out
    //  function TokenSale(uint _minValue, uint _closingTime);

    /// @notice Buy Token with `_tokenHolder` as the initial owner of the Token
    /// @param _tokenHolder The address of the Tokens's recipient 
    function buyTokenProxy(address _tokenHolder) returns (bool success);

    /// @notice Refund `msg.sender` in the case the Token Sale didn't reach its 
    /// minimum funding goal
    function refund();

    /// @return the divisor used to calculate the token price during the sale
    function divisor() returns (uint divisor);

    event FundingToDate(uint value);
    event SoldToken(address indexed to, uint amount);
    event Refund(address indexed to, uint value);
}

contract TokenSale is TokenSaleInterface, Token {
    function TokenSale(uint _minValue, uint _closingTime, address _privateSale) {
        closingTime = _closingTime;
        minValue = _minValue;
        privateSale = _privateSale;
        extraBalance = new ManagedAccount(address(this));
    }

    function buyTokenProxy(address _tokenHolder) returns (bool success) {
        if (now < closingTime && msg.value > 0 
        && (privateSale == 0 || privateSale == msg.sender)) {
            uint token = (msg.value * 20) / divisor();
            extraBalance.call.value(msg.value - token)();
            balances[_tokenHolder] += token;
            totalSupply += token;
            weiGiven[msg.sender] += msg.value;
            SoldToken(_tokenHolder, token);
            if (totalSupply >= minValue && !isFunded) {
                isFunded = true;
                FundingToDate(totalSupply);
            }
            return true;
        }
        throw;
    }

    function refund() noEther {
        if (now > closingTime && !isFunded) {
            // get extraBalance - will only succeed when called for the first time
            extraBalance.payOut(address(this), extraBalance.accumulatedInput());

            // execute refund
            if (msg.sender.call.value(weiGiven[msg.sender])()) {
                Refund(msg.sender, weiGiven[msg.sender]);
                totalSupply -= balances[msg.sender];
                balances[msg.sender] = 0;
                weiGiven[msg.sender] = 0;
            }
        }
    }

    function divisor() returns (uint divisor){
        // the number of (base unit) tokens per wei is calculated
        // as `msg.value` * 20 / `divisor`
        // the funding period starts with a 1:1 ratio
        if (closingTime - 2 weeks > now) return 20;
        // followed by 10 days with a daily price increase of 5%
        else if (closingTime - 4 days > now)
            return (20 + (now - (closingTime - 2 weeks)) / (1 days));
        // the last 4 days there is a constant price ratio of 1:1,5
        else return 30;
    }
}
\end{verbatim}
\subsection{DAO}\label{app:DAO}
\begin{verbatim}
contract DAOInterface {

    // Proposals to spend the DAO's ether or to choose a new service provider
    Proposal[] public proposals;
    // The quorum needed for each proposal is partially calculated by
    // totalSupply / minQuorumDivisor
    uint minQuorumDivisor;
    // The unix time of the last time quorum was reached on a proposal
    uint lastTimeMinQuorumMet;
    // The total amount of wei received as reward that has not been sent to
    // the rewardAccount
    uint public rewards;
    // Address of the service provider
    address public serviceProvider;
    // The whitelist: List of addresses the DAO is allowed to send money to
    address[] public allowedRecipients;

    // Tracks the addresses that own Reward Tokens. Those addresses can only be
    // DAOs that have split from the original DAO. Conceptually, Reward Tokens
    // represent the proportion of the rewards that the DAO has the right to
    // receive. These Reward Tokens are generated when the DAO spends ether.
    mapping (address => uint) public rewardToken;
    // Total supply of rewardToken
    uint public totalRewardToken;

    // The account used to manage the rewards which are to be distributed to the
    // DAO Token Holders of any DAO that holds Reward Tokens
    ManagedAccount public rewardAccount;
    // Amount of rewards (in wei) already paid out to a certain address
    mapping (address => uint) public paidOut;
    // Map of addresses blocked during a vote (not allowed to transfer DAO
    // tokens). The address points to the proposal ID.
    mapping (address => uint) public blocked;

    // The minimum deposit (in wei) required to submit any proposal that is not
    // requesting a new service provider (no deposit is required for splits)
    uint public proposalDeposit;

    // Contract that is able to create a new DAO (with the same code as
    // this one), used for splits
    DAO_Creator public daoCreator;

    // A proposal with `newServiceProvider == false` represents a transaction
    // to be issued by this DAO
    // A proposal with `newServiceProvider == true` represents a DAO split
    struct Proposal {
        // The address where the `amount` will go to if the proposal is accepted
        // or if `newServiceProvider` is true, the proposed service provider of
        //the new DAO).
        address recipient;
        // The amount to transfer to `recipient` if the proposal is accepted.
        uint amount;
        // A plain text description of the proposal
        string description;
        // A unix timestamp, denoting the end of the voting period
        uint votingDeadline;
        // True if the proposal's votes have yet to be counted, otherwise False
        bool open;
        // True if quorum has been reached, the votes have been counted, and
        // the majority said yes
        bool proposalPassed;
        // A hash to check validity of a proposal
        bytes32 proposalHash;
        // Deposit in wei the creator added when submitting their proposal. It
        // is taken from the msg.value of a newProposal call.
        uint proposalDeposit;
        // True if this proposal is to assign a new service provider
        bool newServiceProvider;
        // Data needed for splitting the DAO
        SplitData[] splitData;
        // Number of tokens in favour of the proposal
        uint yea;
        // Number of tokens opposed to the proposal
        uint nay;
        // Simple mapping to check if a shareholder has voted for it
        mapping (address => bool) votedYes;
        // Simple mapping to check if a shareholder has voted against it
        mapping (address => bool) votedNo;
        // Address of the shareholder who created the proposal
        address creator;
    }

    // Used only in the case of a newServiceProvider porposal.
    struct SplitData {
        // The balance of the current DAO minus the deposit at the time of split
        uint splitBalance;
        // The total amount of DAO Tokens in existence at the time of split.
        uint totalSupply;
        // Amount of Reward Tokens owned by the DAO at the time of split.
        uint rewardToken;
        // The new DAO contract created at the time of split.
        DAO newDAO;
    }
    // Used to restrict acces to certain functions to only DAO Token Holders
    modifier onlyTokenholders {}

    /// @dev Constructor setting the default service provider and the address
    /// for the contract able to create another DAO as well as the parameters
    /// for the DAO Token Sale
    /// @param _defaultServiceProvider The default service provider
    /// @param _daoCreator The contract able to (re)create this DAO
    /// @param _minValue Minimal value for a successful DAO Token Sale
    /// @param _closingTime Date (in unix time) of the end of the DAO Token Sale
    /// @param _privateSale If zero the DAO Token Sale is open to public, a
    /// non-zero address means that the DAO Token Sale is only for the address
    // This is the constructor: it can not be overloaded so it is commented out
    //  function DAO(
        //  address _defaultServiceProvider,
        //  DAO_Creator _daoCreator,
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateSale
    //  )

    /// @notice Buy Token with `msg.sender` as the beneficiary
    function () returns (bool success);

    /// @dev Function used by the products of the DAO (e.g. Slocks) to send
    /// rewards to the DAO
    /// @return Whether the call to this function was successful or not
    function payDAO() returns(bool);

    /// @dev This function is used by the service provider to send money back
    /// to the DAO, it can also be used to receive payments that should not be
    /// counted as rewards (donations, grants, etc.)
    /// @return Whether the DAO received the ether successfully
    function receiveEther() returns(bool);

    /// @notice `msg.sender` creates a proposal to send `_amount` Wei to
    ///  `_recipient` with the transaction data `_transactionData`. If
    /// `_newServiceProvider` is true, then this is a proposal that splits the
    /// DAO and sets `_recipient` as the new DAO's new service provider.
    /// @param _recipient Address of the recipient of the proposed transaction
    /// @param _amount Amount of wei to be sent with the proposed transaction
    /// @param _description String describing the proposal
    /// @param _transactionData Data of the proposed transaction
    /// @param _debatingPeriod Time used for debating a proposal, at least 2
    /// weeks for a regular proposal, 10 days for new service provider proposal
    /// @param _newServiceProvider Bool defining whether this proposal is about
    /// a new service provider or not
    /// @return The proposal ID. Needed for voting on the proposal
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool _newServiceProvider
    ) onlyTokenholders returns (uint _proposalID);

    /// @notice Check that the proposal with the ID `_proposalID` matches the
    /// transaction which sends `_amount` with data `_transactionData`
    /// to `_recipient`
    /// @param _proposalID The proposal ID
    /// @param _recipient The recipient of the proposed transaction
    /// @param _amount The amount of wei to be sent in the proposed transaction
    /// @param _transactionData The data of the proposed transaction
    /// @return Whether the proposal ID matches the transaction data or not
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);

    /// @notice Vote on proposal `_proposalID` with `_supportsProposal`
    /// @param _proposalID The proposal ID
    /// @param _supportsProposal Yes/No - support of the proposal
    /// @return The vote ID.
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);

    /// @notice Checks whether proposal `_proposalID` with transaction data
    /// `_transactionData` has been voted for or rejected, and executes the
    /// transaction in the case it has been voted for.
    /// @param _proposalID The proposal ID
    /// @param _transactionData The data of the proposed transaction
    /// @return Whether the proposed transaction has been executed or not
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);

    /// @notice ATTENTION! I confirm to move my remaining funds to a new DAO
    /// with `_newServiceProvider` as the new service provider, as has been
    /// proposed in proposal `_proposalID`. This will burn my tokens. This can
    /// not be undone and will split the DAO into two DAO's, with two
    /// different underlying tokens.
    /// @param _proposalID The proposal ID
    /// @param _newServiceProvider The new service provider of the new DAO
    /// @dev This function, when called for the first time for this proposal,
    /// will create a new DAO and send the sender's portion of the remaining
    /// ether and Reward Tokens to the new DAO. It will also burn the DAO Tokens
    /// of the sender. (TODO: document rewardTokens - done??)
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);

    /// @notice Add a new possible recipient `_recipient` to the whitelist so
    /// that the DAO can send transactions to them (using proposals)
    /// @param _recipient New recipient address
    /// @dev Can only be called by the current service provider
    function addAllowedAddress(address _recipient) external returns (bool _success);

    /// @notice Change the minimum deposit required to submit a proposal
    /// @param _proposalDeposit The new proposal deposit
    /// @dev Can only be called by this DAO (through proposals with the
    /// recipient being this DAO itself)
    function changeProposalDeposit(uint _proposalDeposit) external;

    /// @notice Get my portion of the reward that was sent to `rewardAccount`
    /// @return Whether the call was successful
    function getMyReward() returns(bool _success);

    /// @notice Withdraw `account`'s portion of the reward from `rewardAccount`,
    /// to `account`'s balance
    /// @return Whether the call was successful
    function withdrawRewardFor(address _account) returns(bool _success);

    /// @notice Send `_amount` tokens to `_to` from `msg.sender`. Prior to this
    /// getMyReward() is called.
    /// @param _to The address of the recipient
    /// @param _amount The amount of tokens to be transfered
    /// @return Whether the transfer was successful or not
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);

    /// @notice Send `_amount` tokens to `_to` from `_from` on the condition it
    /// is approved by `_from`. Prior to this getMyReward() is called.
    /// @param _from The address of the sender
    /// @param _to The address of the recipient
    /// @param _amount The amount of tokens to be transfered
    /// @return Whether the transfer was successful or not
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);

    /// @notice Doubles the 'minQuorumDivisor' in the case quorum has not been
    /// achieved in 52 weeks
    /// @return Whether the change was successful or not
    function halveMinQuorum() returns (bool _success);

    /// @return total number of proposals ever created
    function numberOfProposals() constant returns (uint _numberOfProposals);

    /// @param _account The address of the account which is checked.
    /// @return Whether the account is blocked (not allowed to transfer tokens) or not.
    function isBlocked(address _account) returns (bool);

    event ProposalAdded(
        uint indexed proposalID,
        address recipient,
        uint amount,
        bool newServiceProvider,
        string description
    );
    event Voted(uint indexed proposalID, bool position, address indexed voter);
    event ProposalTallied(uint indexed proposalID, bool result, uint quorum);
    event NewServiceProvider(address indexed _newServiceProvider);
    event AllowedRecipientAdded(address indexed _recipient);
}

// The DAO contract itself
contract DAO is DAOInterface, Token, TokenSale {

    // Modifier that allows only shareholders to vote and create new proposals
    modifier onlyTokenholders {
        if (balanceOf(msg.sender) == 0) throw;
            _
    }

    function DAO(
        address _defaultServiceProvider,
        DAO_Creator _daoCreator,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    ) TokenSale(_minValue, _closingTime, _privateSale) {

        serviceProvider = _defaultServiceProvider;
        daoCreator = _daoCreator;
        proposalDeposit = 20 ether;
        rewardAccount = new ManagedAccount(address(this));
        lastTimeMinQuorumMet = now;
        minQuorumDivisor = 5; // sets the minimal quorum to 20%
        proposals.length++; // avoids a proposal with ID 0 because it is used
        if (address(rewardAccount) == 0)
            throw;
    }

    function () returns (bool success) {
        if (now < closingTime + 40 days)
            return buyTokenProxy(msg.sender);
        else
            return receiveEther();
    }

    function payDAO() returns (bool) {
        rewards += msg.value;
        return true;
    }

    function receiveEther() returns (bool) {
        return true;
    }

    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool _newServiceProvider
    ) onlyTokenholders returns (uint _proposalID) {

        // Sanity check
        if (_newServiceProvider && (
            _amount != 0
            || _transactionData.length != 0
            || _recipient == serviceProvider
            || msg.value > 0
            || _debatingPeriod < 1 weeks)) {
            throw;
        } else if(
            !_newServiceProvider
            && (!isRecipientAllowed(_recipient) || (_debatingPeriod < 2 weeks))
        ) {
            throw;
        }

        if (!isFunded
            || now < closingTime
            || (msg.value < proposalDeposit && !_newServiceProvider)) {

            throw;
        }

        if (_recipient == address(rewardAccount) && _amount > rewards)
            throw;

        if (now + _debatingPeriod < now) // prevents overflow
            throw;

        _proposalID = proposals.length++;
        Proposal p = proposals[_proposalID];
        p.recipient = _recipient;
        p.amount = _amount;
        p.description = _description;
        p.proposalHash = sha3(_recipient, _amount, _transactionData);
        p.votingDeadline = now + _debatingPeriod;
        p.open = true;
        //p.proposalPassed = False; // that's default
        p.newServiceProvider = _newServiceProvider;
        if (_newServiceProvider)
            p.splitData.length++;
        p.creator = msg.sender;
        p.proposalDeposit = msg.value;
        ProposalAdded(
            _proposalID,
            _recipient,
            _amount,
            _newServiceProvider,
            _description
        );
    }

    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) noEther constant returns (bool _codeChecksOut) {
        Proposal p = proposals[_proposalID];
        return p.proposalHash == sha3(_recipient, _amount, _transactionData);
    }

    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders noEther returns (uint _voteID) {

        Proposal p = proposals[_proposalID];
        if (p.votedYes[msg.sender]
            || p.votedNo[msg.sender]
            || now >= p.votingDeadline) {

            throw;
        }

        if (_supportsProposal) {
            p.yea += balances[msg.sender];
            p.votedYes[msg.sender] = true;
        } else {
            p.nay += balances[msg.sender];
            p.votedNo[msg.sender] = true;
        }

        if (blocked[msg.sender] == 0) {
            blocked[msg.sender] = _proposalID;
        } else if (p.votingDeadline > proposals[blocked[msg.sender]].votingDeadline) {
            // this proposal's voting deadline is further into the future than
            // the proposal that blocks the sender so make it the blocker
            blocked[msg.sender] = _proposalID;
        }

        Voted(_proposalID, _supportsProposal, msg.sender);
    }

    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) noEther returns (bool _success) {

        Proposal p = proposals[_proposalID];
        // Check if the proposal can be executed
        if (now < p.votingDeadline  // has the voting deadline arrived?
            // Have the votes been counted?
            || !p.open
            // Does the transaction code match the proposal?
            || p.proposalHash != sha3(p.recipient, p.amount, _transactionData)) {

            throw;
        }

        if (p.newServiceProvider) {
            p.open = false;
            return;
        }

        uint quorum = p.yea + p.nay;

        // Execute result
        if (quorum >= minQuorum(p.amount) && p.yea > p.nay) {
            if (!p.creator.send(p.proposalDeposit))
                throw;
            // Without this throw, the creator of the proposal can repeat this,
            // and get so much ether
            if (!p.recipient.call.value(p.amount)(_transactionData))
                throw;
            p.proposalPassed = true;
            _success = true;
            lastTimeMinQuorumMet = now;
            if (p.recipient == address(rewardAccount)) {
                // This happens when multiple similar proposals are created and
                // both are passed at the same time.
                if (rewards < p.amount)
                    throw;
                rewards -= p.amount;
            } else {
                rewardToken[address(this)] += p.amount;
                totalRewardToken += p.amount;
            }
        } else if (quorum >= minQuorum(p.amount) && p.nay >= p.yea) {
            if (!p.creator.send(p.proposalDeposit))
                throw;
            lastTimeMinQuorumMet = now;
        }

        // Since the voting deadline is over, close the proposal
        p.open = false;

        // Initiate event
        ProposalTallied(_proposalID, _success, quorum);
    }

    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) noEther onlyTokenholders returns (bool _success) {

        Proposal p = proposals[_proposalID];

        // Sanity check

        if (now < p.votingDeadline  // has the voting deadline arrived?
            //The request for a split expires 41 days after the voting deadline
            || now > p.votingDeadline + 41 days
            // Does the new service provider address match?
            || p.recipient != _newServiceProvider
            // Is it a new service provider proposal?
            || !p.newServiceProvider
            // Have you voted for this split?
            || !p.votedYes[msg.sender]
            // Did you already vote on another proposal?
            || blocked[msg.sender] != _proposalID) {

            throw;
        }

        // If the new DAO doesn't exist yet, create the new DAO and store the
        // current split data
        if (address(p.splitData[0].newDAO) == 0) {
            p.splitData[0].newDAO = createNewDAO(_newServiceProvider);
            // Call depth limit reached, etc.
            if (address(p.splitData[0].newDAO) == 0)
                throw;
            // p.proposalDeposit should be zero here
            if (this.balance < p.proposalDeposit)
                throw;
            p.splitData[0].splitBalance = this.balance - p.proposalDeposit;
            p.splitData[0].rewardToken = rewardToken[address(this)];
            p.splitData[0].totalSupply = totalSupply;
            p.proposalPassed = true;
        }

        // Move funds and assign new Tokens
        uint fundsToBeMoved =
            (balances[msg.sender] * p.splitData[0].splitBalance) /
            p.splitData[0].totalSupply;
        if (p.splitData[0].newDAO.buyTokenProxy.value(fundsToBeMoved)(msg.sender) == false)
            throw;

        // Assign reward rights to new DAO
        uint rewardTokenToBeMoved =
            (balances[msg.sender] * p.splitData[0].rewardToken) /
            p.splitData[0].totalSupply;
        rewardToken[address(p.splitData[0].newDAO)] += rewardTokenToBeMoved;
        if (rewardToken[address(this)] < rewardTokenToBeMoved)
            throw;
        rewardToken[address(this)] -= rewardTokenToBeMoved;

        // Burn DAO Tokens
        Transfer(msg.sender, 0, balances[msg.sender]);
        totalSupply -= balances[msg.sender];
        balances[msg.sender] = 0;
        paidOut[address(p.splitData[0].newDAO)] += paidOut[msg.sender];
        paidOut[msg.sender] = 0;

        return true;
    }

    function getMyReward() noEther returns (bool _success) {
        return withdrawRewardFor(msg.sender);
    }

    function withdrawRewardFor(address _account) noEther returns (bool _success) {
        // The account's portion of Reward Tokens of this DAO
        uint portionOfTheReward =
            (balanceOf(_account) * rewardToken[address(this)]) /
            totalSupply + rewardToken[_account];
        uint reward =
            (portionOfTheReward * rewardAccount.accumulatedInput()) /
            totalRewardToken - paidOut[_account];
        if (!rewardAccount.payOut(_account, reward))
            throw;
        paidOut[_account] += reward;
        return true;
    }

    function transfer(address _to, uint256 _value) returns (bool success) {
        if (isFunded
            && now > closingTime
            && !isBlocked(msg.sender)
            && transferPaidOut(msg.sender, _to, _value)
            && super.transfer(_to, _value)) {

            return true;
        } else {
            throw;
        }
    }

    function transferWithoutReward(address _to, uint256 _value) returns (bool success) {
        if (!getMyReward())
            throw;
        return transfer(_to, _value);
    }

    function transferFrom(address _from, address _to, uint256 _value) returns (bool success) {
        if (isFunded
            && now > closingTime
            && !isBlocked(_from)
            && transferPaidOut(_from, _to, _value)
            && super.transferFrom(_from, _to, _value)) {

            return true;
        } else {
            throw;
        }
    }

    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _value
    ) returns (bool success) {

        if (!withdrawRewardFor(_from))
            throw;
        return transferFrom(_from, _to, _value);
    }

    function transferPaidOut(
        address _from,
        address _to,
        uint256 _value
    ) internal returns (bool success) {

        uint transferPaidOut = paidOut[_from] * _value / balanceOf(_from);
        if (transferPaidOut > paidOut[_from])
            throw;
        paidOut[_from] -= transferPaidOut;
        paidOut[_to] += transferPaidOut;
        return true;
    }

    function changeProposalDeposit(uint _proposalDeposit) noEther external {
        if (msg.sender != address(this) || _proposalDeposit > this.balance / 10)
            throw;
        proposalDeposit = _proposalDeposit;
    }

    function addAllowedAddress(address _recipient) noEther external returns (bool _success) {
        if (msg.sender != serviceProvider)
            throw;
        allowedRecipients.push(_recipient);
        return true;
    }

    function isRecipientAllowed(address _recipient) internal returns (bool _isAllowed) {
        if (_recipient == serviceProvider
            || _recipient == address(rewardAccount)
            || _recipient == address(this)
            || (_recipient == address(extraBalance)
                // only allowed when at least the amount held in the
                // extraBalance account has been spent from the DAO
                && totalRewardToken > extraBalance.accumulatedInput()))
            return true;

        for (uint i = 0; i < allowedRecipients.length; ++i) {
            if (_recipient == allowedRecipients[i])
                return true;
        }
        return false;
    }

    function minQuorum(uint _value) internal returns (uint _minQuorum) {
        // minimum of 20% and maximum of 53.33%
        return totalSupply / minQuorumDivisor + _value / 3;
    }

    function halveMinQuorum() returns (bool _success) {
        if (lastTimeMinQuorumMet < (now - 52 weeks)) {
            lastTimeMinQuorumMet = now;
            minQuorumDivisor *= 2;
            return true;
        } else {
            return false;
        }
    }

    function createNewDAO(address _newServiceProvider) internal returns (DAO _newDAO) {
        NewServiceProvider(_newServiceProvider);
        return daoCreator.createDAO(_newServiceProvider, 0, now + 42 days);
    }

    function numberOfProposals() constant returns (uint _numberOfProposals) {
        // Don't count index 0. It's used by isBlocked() and exists from start
        return proposals.length - 1;
    }

    function isBlocked(address _account) returns (bool) {
        if (blocked[_account] == 0)
            return false;
        Proposal p = proposals[blocked[_account]];
        if (!p.open) {
            blocked[_account] = 0;
            return false;
        } else {
            return true;
        }
    }
}

contract DAO_Creator {
    function createDAO(
        address _defaultServiceProvider,
        uint _minValue,
        uint _closingTime
    ) returns (DAO _newDAO) {

        return new DAO(
            _defaultServiceProvider,
            DAO_Creator(this),
            _minValue,
            _closingTime,
            msg.sender
        );
    }
}
\end{verbatim}

\subsection{Sample Offer}\label{app:SampleOffer}
\begin{verbatim}
contract SampleOffer {

    uint totalCosts;
    uint oneTimeCosts;
    uint dailyCosts;

    address serviceProvider;
    bytes32 hashOfTheContract;
    uint minDailyCosts;
    uint paidOut;

    uint dateOfSignature;
    DAO client; // address of DAO

    bool public promiseValid;
    uint public rewardDivisor;
    uint public deploymentReward;

    modifier callingRestriction {
        if (promiseValid) {
            if (msg.sender != address(client))
                throw;
        } else if (msg.sender != serviceProvider) {
                throw;
        }
        _
    }

    modifier onlyClient {
        if (msg.sender != address(client))
            throw;
        _
    }

    function SampleOffer(
        address _serviceProvider,
        bytes32 _hashOfTheContract,
        uint _totalCosts,
        uint _oneTimeCosts,
        uint _minDailyCosts,
        uint _rewardDivisor,
        uint _deploymentReward
    ) {
        serviceProvider = _serviceProvider;
        hashOfTheContract = _hashOfTheContract;
        totalCosts = _totalCosts;
        oneTimeCosts = _oneTimeCosts;
        minDailyCosts = _minDailyCosts;
        dailyCosts = _minDailyCosts;
        rewardDivisor = _rewardDivisor;
        deploymentReward = _deploymentReward;
    }

    function sign() {
        if (msg.value < totalCosts && dateOfSignature != 0)
            throw;
        if (!serviceProvider.send(oneTimeCosts))
            throw;
        client = DAO(msg.sender);
        dateOfSignature = now;
        promiseValid = true;
    }

    function setDailyCosts(uint _dailyCosts) onlyClient {
        dailyCosts = _dailyCosts;
        if (dailyCosts < minDailyCosts)
            promiseValid = false;
    }

    function returnRemainingMoney() onlyClient {
        if (client.receiveEther.value(this.balance)())
            promiseValid = false;
    }

    function getDailyPayment() {
        if (msg.sender != serviceProvider)
            throw;
        uint amount = (now - dateOfSignature) / (1 days) * dailyCosts - paidOut;
        if (serviceProvider.send(amount))
            paidOut += amount;
    }

    function setRewardDivisor(uint _rewardDivisor) callingRestriction {
        if (_rewardDivisor < 50 && msg.sender != address(client))
            throw; // 2% is the default max reward
        rewardDivisor = _rewardDivisor;
    }

    function setDeploymentFee(uint _deploymentReward) callingRestriction {
        if (deploymentReward > 10 ether && msg.sender != address(client))
            throw; // TODO, set a max defined by service provider, or ideally oracle (set in euro)
        deploymentReward = _deploymentReward;
    }

    // interface for Slocks
    function payOneTimeReward() returns(bool) {
        if (msg.value < deploymentReward)
            throw;
        if (promiseValid) {
            if (client.payDAO.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (serviceProvider.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }

    // pay reward
    function payReward() returns(bool) {
        if (promiseValid) {
            if (client.payDAO.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (serviceProvider.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }
}
\end{verbatim}

\subsection{Managed Account}\label{app:ManagedAccount}
\begin{verbatim}
contract ManagedAccountInterface {
    address public owner;
    uint public accumulatedInput;

    function payOut(address _recipient, uint _amount) returns (bool);

    event PayOut(address indexed _recipient, uint _amount);
}

contract ManagedAccount is ManagedAccountInterface{
    function ManagedAccount(address _owner){
        owner = _owner;
    }

    function(){
        accumulatedInput += msg.value;
    }

    function payOut(address _recipient, uint _amount) returns (bool){
        if (msg.sender != owner || msg.value > 0) throw;
        if (_recipient.call.value(_amount)()){
            PayOut(_recipient, _amount);
            return true;
        }
        else
            return false;
    }
}
\end{verbatim}
\end{appendix}
\end{document}

### 2016-03-16 tests/scenarios/deploy/deploy.template.js
Each DAO scenario is now in its own directory

@@ -1,0 +1,66 @@
+var _defaultServiceProvider = web3.eth.accounts[0];
+var daoContract = web3.eth.contract($dao_abi);
+console.log("Creating DAOCreator Contract");
+var creatorContract = web3.eth.contract($creator_abi);
+var _daoCreatorContract = creatorContract.new(
+    {
+	from: web3.eth.accounts[0],
+	data: '$creator_bin',
+	gas: 3000000
+    }, function (e, contract){
+	if (e) {
+            console.log(e+" at DAOCreator creation!");
+	} else if (typeof contract.address != 'undefined') {
+        addToTest('dao_creator_address', contract.address);
+        checkWork();
+        var dao = daoContract.new(
+		    _defaultServiceProvider,
+		    contract.address,
+		    $min_value,
+		    $closing_time,
+            0,
+		    {
+		        from: web3.eth.accounts[0],
+		        data: '$dao_bin',
+		        gas: 4000000
+		    }, function (e, contract) {
+		        // funny thing, without this geth hangs
+		        console.log("At DAO creation callback");
+		        if (typeof contract.address != 'undefined') {
+                    addToTest('dao_address', contract.address);
+		        }
+		    });
+        checkWork();
+	}
+    });
+checkWork();
+var offerContract = web3.eth.contract($offer_abi);
+var offer = offerContract.new(
+    _defaultServiceProvider, //service provider
+    '0x0',  // This is a hash of the paper contract. Does not matter for testing
+    web3.toWei($offer_total, "ether"), //total costs
+    web3.toWei($offer_onetime, "ether"), //one time costs
+    web3.toWei(1, "ether"), //min daily costs
+    web3.toWei(1, "ether"), //reward divison
+    web3.toWei(1, "ether"), //deployment rewards
+    {
+	    from: web3.eth.accounts[0],
+	    data: '$offer_bin',
+	    gas: 3000000
+    }, function (e, contract) {
+	    if (e) {
+            console.log(e + " at Offer Contract creation!");
+	    } else if (typeof contract.address != 'undefined') {
+            addToTest('offer_address', contract.address);
+        }
+    }
+);
+checkWork();
+console.log("mining contract, please wait");
+miner.start(1);
+setTimeout(function() {
+    miner.stop(0);
+    testResults();
+}, 3000);
+
+

### 2016-03-16 tests/scenarios/fund/fund.template.js

@@ -1,0 +1,40 @@
+var amounts = $amounts;
+
+var dao = web3.eth.contract($dao_abi).at('$dao_address');
+console.log("Buying DAO tokens");
+for (i = 0; i < eth.accounts.length; i++) {
+    web3.eth.sendTransaction({
+        from:eth.accounts[i],
+        to: dao.address,
+        gas:200000,
+        value:web3.toWei(amounts[i], "ether")
+    });
+}
+
+checkWork();
+
+setTimeout(function() {
+    miner.stop(0);
+    addToTest('dao_funded', dao.isFunded());
+    addToTest('total_supply', parseInt(web3.fromWei(dao.totalSupply())));
+    var balances = [];
+    for (i = 0; i < eth.accounts.length; i++) {
+        balances.push(parseInt(web3.fromWei(dao.balanceOf(eth.accounts[i]))));
+    }
+    addToTest('balances', balances);
+
+    // now also try to purchase some extra tokens after the sale ended
+    web3.eth.sendTransaction({
+        from:eth.accounts[0],
+        to: dao.address,
+        gas:200000,
+        value:web3.toWei(20, "ether")
+    });
+    // and confirm balance is still the same
+    checkWork();
+    addToTest('user0_after', parseInt(web3.fromWei(dao.balanceOf(eth.accounts[0]))));
+
+    testResults();
+}, $wait_ms);
+console.log("Wait for end of sale");
+miner.start(1);

### 2016-03-16 tests/scenarios/fund/run.py

@@ -44,7 +44,12 @@ def run(framework):
         "Notice: Funding period is {} seconds so the test will wait "
         "as much".format(sale_secs)
     )
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     framework.execute('fund', {
+=======
+    output = framework.run_script('fund.js')
+    eval_test('fund', output, {
+>>>>>>> Each DAO scenario is now in its own directory
         "dao_funded": True,
         "total_supply": framework.total_supply,
         "balances": framework.token_amounts,

### 2016-03-16 tests/scenarios/proposal/proposal.template.js

@@ -1,0 +1,86 @@
+var dao = web3.eth.contract($dao_abi).at('$dao_address');
+var offer = web3.eth.contract($offer_abi).at('$offer_address');
+
+console.log("Add offer contract as allowed recipient");
+dao.addAllowedAddress.sendTransaction('$offer_address', {from: serviceProvider, gas: 1000000});
+checkWork();
+
+addToTest('creator_balance_before', web3.fromWei(eth.getBalance(proposalCreator)));
+console.log("Creating a new proposal for $offer_amount ether.");
+var tx_hash = null;
+dao.newProposal.sendTransaction(
+    '$offer_address',
+    web3.toWei($offer_amount, "ether"),
+    '$offer_desc',
+    '$transaction_bytecode',
+    $debating_period,
+    false,
+    {
+        from: proposalCreator,
+        value: web3.toWei($proposal_deposit, "ether"),
+        gas: 1000000
+    }
+    , function (e, res) {
+        if (e) {
+            console.log(e + "at newProposal()!");
+        } else {
+            tx_hash = res;
+            console.log("newProposal tx hash is: " + tx_hash);
+        }
+    }
+);
+checkWork();
+
+addToTest('creator_balance_after_proposal', web3.fromWei(eth.getBalance(proposalCreator)));
+addToTest(
+    'calculated_deposit',
+    bigDiffRound(testMap['creator_balance_before'], testMap['creator_balance_after_proposal'])
+);
+addToTest('dao_proposals_number', dao.numberOfProposals());
+
+var votes = $votes;
+var prop_id = 1;
+
+console.log("Deadline is: " + dao.proposals(prop_id)[3] + " Voting ... ");
+for (i = 0; i < votes.length; i++) {
+    console.log("User " + i +" is voting ["+ votes[i] +"]. His token balance is: " + web3.fromWei(dao.balanceOf(eth.accounts[i])) + " ether and NOW is: " + Math.floor(Date.now() / 1000));
+    dao.vote.sendTransaction(
+        prop_id,
+        votes[i],
+        {
+            from: eth.accounts[i],
+            gas: 1000000
+        }
+    );
+}
+checkWork();
+addToTest('proposal_yay', parseInt(web3.fromWei(dao.proposals(prop_id)[9])));
+addToTest('proposal_nay', parseInt(web3.fromWei(dao.proposals(prop_id)[10])));
+addToTest('provider_balance_before', web3.fromWei(eth.getBalance(serviceProvider)));
+
+setTimeout(function() {
[…]

### 2016-03-16 tests/scenarios/proposal/run.py

@@ -53,7 +53,12 @@ def run(framework):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     framework.execute('proposal', {
+=======
+    output = framework.run_script('proposal.js')
+    eval_test('proposal', output, {
+>>>>>>> Each DAO scenario is now in its own directory
         "dao_proposals_number": "1",
         "proposal_passed": True,
         "proposal_yay": yay,

### 2016-03-16 tests/scenarios/rewards/rewards.template.js

@@ -1,0 +1,75 @@
+var dao = web3.eth.contract($dao_abi).at('$dao_address');
+
+// some kind soul makes a donation to the DAO, so rewards get populated
+console.log("Donating to DAO...");
+dao.payDAO.sendTransaction({
+    from: eth.accounts[1],
+    value: web3.toWei($total_rewards, "ether"),
+    gas: 100000
+});
+checkWork();
+
+// create a new proposal for sending this whole donation to the rewardAccount
+console.log("Creating proposal to send to rewardAccount...");
+var tx_hash = null;
+dao.newProposal.sendTransaction(
+    dao.rewardAccount(),
+    web3.toWei($total_rewards, "ether"),
+    'Send money to the reward account',
+    '$transaction_bytecode', // bytecode, not needed here, calling the fallback function
+    $debating_period,
+    false,
+    {
+        from: proposalCreator,
+        value: web3.toWei($proposal_deposit, "ether"),
+        gas: 1000000
+    }
+    , function (e, res) {
+        if (e) {
+            console.log(e + "at newProposal()!");
+        } else {
+            tx_hash = res;
+            console.log("newProposal tx hash is: " + tx_hash);
+        }
+    }
+);
+checkWork();
+
+
+var prop_id = $prop_id;
+console.log("Voting for proposal '" + prop_id + "' ...");
+// in this scenario let's just say everyone votes 100% in favour
+for (i = 0; i < eth.accounts.length; i++) {
+    dao.vote.sendTransaction(
+        prop_id,
+        true,
+        {
+            from: eth.accounts[i],
+            gas: 1000000
+        }
+    );
+}
+checkWork();
+
+setTimeout(function() {
+    miner.stop(0);
+    console.log("Executing the proposal...");
+    // now execute the proposal
+    dao.executeProposal.sendTransaction(prop_id, '$transaction_bytecode', {from:serviceProvider, gas:1000000});
+    checkWork();
+    addToTest('provider_balance_before_claim', eth.getBalance(serviceProvider));
+    console.log("Claiming the reward...");
+    dao.getMyReward.sendTransaction({from: serviceProvider, gas: 1000000});
+    checkWork();
+    addToTest('provider_balance_after_claim', eth.getBalance(serviceProvider));
+    addToTest(
+        'provider_reward_portion',
+        parseFloat(web3.fromWei(bigDiff(
[…]

### 2016-03-16 tests/scenarios/rewards/run.py

@@ -35,7 +35,12 @@ def run(framework):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     results = framework.execute('rewards', {
+=======
+    output = framework.run_script('rewards.js')
+    results = eval_test('rewards', output, {
+>>>>>>> Each DAO scenario is now in its own directory
         "provider_reward_portion": calculate_reward(
             framework.token_amounts[0],
             framework.total_supply,

### 2016-03-16 tests/scenarios/split/run.py

@@ -91,7 +91,12 @@ def prepare_test_split(framework, split_gas):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     return votes
+=======
+    output = framework.run_script('split.js')
+    return votes, output
+>>>>>>> Each DAO scenario is now in its own directory
 
 
 def run(framework):
@@ -101,14 +106,22 @@ def run(framework):
     # This should happen with the latest homestead changes:
     # https://github.com/ethereum/EIPs/blob/master/EIPS/eip-2.mediawiki#specification
     split_gas = 4000000
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     votes = prepare_test_split(framework, split_gas)
+=======
+    votes, output = prepare_test_split(framework, split_gas)
+>>>>>>> Each DAO scenario is now in its own directory
     oldBalance, newBalance, oldDAORewards, newDAORewards = tokens_after_split(
         votes,
         framework.token_amounts,
         framework.dao_balance_after_rewards,
         framework.dao_rewardToken_after_rewards
     )
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     framework.execute('split', {
+=======
+    eval_test('split', output, {
+>>>>>>> Each DAO scenario is now in its own directory
         # default deposit,a simple way to test new DAO contract got created
         "newDAOProposalDeposit": 20,
         "oldDAOBalance": oldBalance,

### 2016-03-16 tests/scenarios/split/split.template.js

@@ -1,0 +1,82 @@
+var dao = web3.eth.contract($dao_abi).at('$dao_address');
+var newServiceProvider = eth.accounts[1];
+
+// create a new proposal for sending this whole donation to the rewardAccount
+console.log("Creating proposal to change SP...");
+var tx_hash = null;
+dao.newProposal.sendTransaction(
+    newServiceProvider, // new SP
+    0,
+    'Changing SP to eth.accounts[1]',
+    '',
+    $debating_period,
+    true,
+    {
+        from: proposalCreator,
+        gas: 1000000
+    }
+    , function (e, res) {
+        if (e) {
+            console.log(e + "at newProposal()!");
+        } else {
+            tx_hash = res;
+            console.log("newProposal tx hash is: " + tx_hash);
+        }
+    }
+);
+checkWork();
+
+var votes = $votes;
+var prop_id = $prop_id;
+console.log("Voting for split proposal '" + prop_id + "' ...");
+for (i = 0; i < votes.length; i++) {
+    dao.vote.sendTransaction(
+        prop_id,
+        votes[i],
+        {
+            from: eth.accounts[i],
+            gas: 1000000
+        }
+    );
+}
+checkWork();
+addToTest('proposal_yay', parseInt(web3.fromWei(dao.proposals(prop_id)[9])));
+addToTest('proposal_nay', parseInt(web3.fromWei(dao.proposals(prop_id)[10])));
+
+setTimeout(function() {
+    miner.stop(0);
+    console.log("Executing the split proposal...");
+    // now each user who voted for the split should call splitDAO to execute the proposal
+    for (i = 0; i < votes.length; i++) {
+        if (votes[i]) {
+            dao.splitDAO.sendTransaction(
+                prop_id,
+                newServiceProvider,
+                {from:eth.accounts[i], gas: $split_gas}
+            );
+        }
+    }
+    checkWork();
+    console.log("After split execution");
+    addToTest('proposal_passed', dao.proposals(prop_id)[5]);
+    addToTest('proposal_newdao', dao.splitProposalNewAddress(prop_id, 0));
+
+    var newdao = web3.eth.contract($dao_abi).at(testMap['proposal_newdao']);
+    // check token balance of each user in both DAOs
+    oldDAOBalance = [];
+    newDAOBalance = [];
[…]

### 2016-03-16 tests/test.py

@@ -11,8 +11,12 @@ import sys
 import importlib
 from string import Template
 from utils import (
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     rm_file, determine_binary, write_js,
     create_genesis, edit_dao_source, eval_test
+=======
+    rm_file, determine_binary, write_js, create_genesis, edit_dao_source
+>>>>>>> Each DAO scenario is now in its own directory
 )
 from args import test_args
 
@@ -186,7 +190,11 @@ class TestContext():
         print("Creating {}.js".format(name))
         scenario_dir = os.path.join(self.tests_dir, "scenarios", name)
         with open(
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
                 os.path.join(scenario_dir, 'template.js'),
+=======
+                os.path.join(scenario_dir, '{}.template.js'.format(name)),
+>>>>>>> Each DAO scenario is now in its own directory
                 'r'
         ) as f:
             data = f.read()
@@ -196,10 +204,13 @@ class TestContext():
         s = tmpl.substitute(substitutions)
         write_js("{}.js".format(name), s, len(self.accounts))
 
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     def execute(self, name, expected):
         output = self.run_script('{}.js'.format(name))
         return eval_test(name, output, expected)
 
+=======
+>>>>>>> Each DAO scenario is now in its own directory
     def run_scenario(self, name):
         if name == 'None':
             print("Asked to run no scenario. Quitting ...")

### 2016-03-16 tests/utils.py

@@ -208,7 +208,10 @@ def count_token_votes(amounts, votes):
             nay += amount
     return yay, nay
 
+<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
 
+=======
+>>>>>>> Each DAO scenario is now in its own directory
 def edit_dao_source(contracts_dir, keep_limits):
     with open(os.path.join(contracts_dir, 'DAO.sol'), 'r') as f:
         contents = f.read()

### 2016-03-16 tests/scenarios/deploy/run.py
Each DAO scenario is now in its own directory

@@ -1,0 +1,58 @@
+import inspect
+import os
+import sys
+import json
+currentdir = os.path.dirname(
+    os.path.abspath(inspect.getfile(inspect.currentframe()))
+)
+parentdir = os.path.dirname(os.path.dirname(currentdir))
+os.sys.path.insert(0, parentdir)
+from utils import extract_test_dict, seconds_in_future
+
+
+def calculate_closing_time(obj, script_name, substitutions):
+    obj.closing_time = seconds_in_future(obj.args.closing_time)
+    substitutions['closing_time'] = obj.closing_time
+    return substitutions
+
+
+def run(framework):
+    print("Running the Deploy Test Scenario")
+    framework.create_js_file(
+        'deploy',
+        {
+            "dao_abi": framework.dao_abi,
+            "dao_bin": framework.dao_bin,
+            "creator_abi": framework.creator_abi,
+            "creator_bin": framework.creator_bin,
+            "offer_abi": framework.offer_abi,
+            "offer_bin": framework.offer_bin,
+            "offer_onetime": framework.args.offer_onetime_costs,
+            "offer_total": framework.args.offer_total_costs,
+            "min_value": framework.min_value,
+        },
+        calculate_closing_time
+    )
+    output = framework.run_script('deploy.js')
+    results = extract_test_dict('deploy', output)
+
+    try:
+        framework.dao_creator_addr = results['dao_creator_address']
+        framework.dao_addr = results['dao_address']
+        framework.offer_addr = results['offer_address']
+    except:
+        print(
+            "ERROR: Could not find expected results in the deploy scenario"
+            ". The output was:\n{}".format(output)
+        )
+        sys.exit(1)
+    print("DAO Creator address is: {}".format(framework.dao_creator_addr))
+    print("DAO address is: {}".format(framework.dao_addr))
+    print("SampleOffer address is: {}".format(framework.offer_addr))
+    with open(framework.save_file, "w") as f:
+        f.write(json.dumps({
+            "dao_creator_addr": framework.dao_creator_addr,
+            "dao_addr": framework.dao_addr,
+            "offer_addr": framework.offer_addr,
+            "closing_time": framework.closing_time
+        }))

### 2016-03-16 tests/scenarios/fund/run.py

@@ -1,0 +1,53 @@
+import inspect
+import os
+import random
+from datetime import datetime
+currentdir = os.path.dirname(
+    os.path.abspath(inspect.getfile(inspect.currentframe()))
+)
+parentdir = os.path.dirname(os.path.dirname(currentdir))
+os.sys.path.insert(0, parentdir)
+from utils import eval_test, constrained_sum_sample_pos, arr_str, ts_now
+
+
+def run(framework):
+    # if deployment did not already happen do it now
+    if not framework.dao_addr:
+        framework.run_scenario('deploy')
+    else:
+        print(
+            "WARNING: Running the funding scenario with a pre-deployed "
+            "DAO contract. Closing time is {} which is approximately {} "
+            "seconds from now.".format(
+                datetime.fromtimestamp(framework.closing_time).strftime(
+                    '%Y-%m-%d %H:%M:%S'
+                ),
+                framework.closing_time - ts_now()
+            )
+        )
+
+    sale_secs = framework.closing_time - ts_now()
+    framework.total_supply = framework.min_value + random.randint(1, 100)
+    framework.token_amounts = constrained_sum_sample_pos(
+        len(framework.accounts), framework.total_supply
+    )
+    framework.create_js_file(
+        'fund',
+        {
+            "dao_abi": framework.dao_abi,
+            "dao_address": framework.dao_addr,
+            "wait_ms": (sale_secs-3)*1000,
+            "amounts": arr_str(framework.token_amounts)
+        }
+    )
+    print(
+        "Notice: Funding period is {} seconds so the test will wait "
+        "as much".format(sale_secs)
+    )
+    output = framework.run_script('fund.js')
+    eval_test('fund', output, {
+        "dao_funded": True,
+        "total_supply": framework.total_supply,
+        "balances": framework.token_amounts,
+        "user0_after": framework.token_amounts[0],
+    })

### 2016-03-16 tests/scenarios/proposal/run.py

@@ -1,0 +1,67 @@
+import inspect
+import os
+import random
+currentdir = os.path.dirname(
+    os.path.abspath(inspect.getfile(inspect.currentframe()))
+)
+parentdir = os.path.dirname(os.path.dirname(currentdir))
+os.sys.path.insert(0, parentdir)
+from utils import eval_test, arr_str, create_votes_array
+
+
+def count_token_votes(amounts, votes):
+    """Returns how many tokens votes yay and how many voted nay"""
+    yay = 0
+    nay = 0
+    for idx, amount in enumerate(amounts):
+        if votes[idx]:
+            yay += amount
+        else:
+            nay += amount
+    return yay, nay
+
+
+def run(framework):
+    if not framework.token_amounts:
+        # run the funding scenario first
+        framework.run_scenario('fund')
+
+    debate_secs = 20
+    minamount = 2  # is determined by the total costs + one time costs
+    amount = random.randint(minamount, sum(framework.token_amounts))
+    votes = create_votes_array(
+        framework.token_amounts,
+        not framework.args.proposal_fail
+    )
+    yay, nay = count_token_votes(framework.token_amounts, votes)
+    framework.create_js_file(
+        'proposal',
+        {
+            "dao_abi": framework.dao_abi,
+            "dao_address": framework.dao_addr,
+            "offer_abi": framework.offer_abi,
+            "offer_address": framework.offer_addr,
+            "offer_amount": amount,
+            "offer_desc": 'Test Proposal',
+            "proposal_deposit": framework.args.proposal_deposit,
+            "transaction_bytecode": '0x2ca15122',  # solc --hashes SampleOffer.sol
+            "debating_period": debate_secs,
+            "votes": arr_str(votes)
+        }
+    )
+    print(
+        "Notice: Debate period is {} seconds so the test will wait "
+        "as much".format(debate_secs)
+    )
+    output = framework.run_script('proposal.js')
+    eval_test('proposal', output, {
+        "dao_proposals_number": "1",
+        "proposal_passed": True,
+        "proposal_yay": yay,
+        "proposal_nay": nay,
+        "calculated_deposit": framework.args.proposal_deposit,
+        "onetime_costs": framework.args.offer_onetime_costs,
+        "deposit_returned": True,
+        "offer_promise_valid": True
+    })
+    framework.prop_id = 1

### 2016-03-16 tests/scenarios/rewards/run.py

@@ -1,0 +1,46 @@
+import inspect
+import os
+currentdir = os.path.dirname(
+    os.path.abspath(inspect.getfile(inspect.currentframe()))
+)
+parentdir = os.path.dirname(os.path.dirname(currentdir))
+os.sys.path.insert(0, parentdir)
+from utils import eval_test, arr_str, create_votes_array
+
+
+def calculate_reward(tokens, total_tokens, total_rewards):
+    result = (tokens * float(total_rewards)) / float(total_tokens)
+    return result
+
+
+def run(framework):
+    if not framework.prop_id:
+        # run the proposal scenario first
+        framework.run_scenario('proposal')
+
+    debate_secs = 15
+    framework.create_js_file(
+        'rewards',
+        {
+            "dao_abi": framework.dao_abi,
+            "dao_address": framework.dao_addr,
+            "total_rewards": framework.args.total_rewards,
+            "proposal_deposit": framework.args.proposal_deposit,
+            "transaction_bytecode": '0x0',  # fallback function
+            "debating_period": debate_secs,
+            "prop_id": framework.next_proposal_id()
+        }
+    )
+    print(
+        "Notice: Debate period is {} seconds so the test will wait "
+        "as much".format(debate_secs)
+    )
+    output = framework.run_script('rewards.js')
+    results = eval_test('rewards', output, {
+        "provider_reward_portion": calculate_reward(
+            framework.token_amounts[0],
+            framework.total_supply,
+            framework.args.total_rewards)
+    })
+    framework.dao_balance_after_rewards = results['DAO_balance']
+    framework.dao_rewardToken_after_rewards = results['DAO_rewardToken']

### 2016-03-16 tests/scenarios/split/run.py

@@ -1,0 +1,125 @@
+import inspect
+import os
+import random
+from datetime import datetime
+currentdir = os.path.dirname(
+    os.path.abspath(inspect.getfile(inspect.currentframe()))
+)
+parentdir = os.path.dirname(os.path.dirname(currentdir))
+os.sys.path.insert(0, parentdir)
+from utils import eval_test, arr_str, create_votes_array
+
+
+def tokens_after_split(votes, original_balance, dao_balance, reward_tokens):
+    """
+    Create expected token and reward token results after the split scenario
+        Parameters
+        ----------
+        votes : array of booleans
+        The votes array of what each user voted
+
+        original_balance : array of ints
+        The original amount of tokens each user had before the split
+
+        dao_balance : int
+        The balance of ether left in the DAO before the scenario started
+
+        reward_tokens : float
+        Amount of reward tokens generated in the DAO before the scenario.
+
+        Returns
+        ----------
+        old_dao_balance : array of ints
+        The balance of tokens left in the old dao.
+
+        new_dao_balance : array of ints
+        The balance of tokens left in the new dao.
+
+        old_reward_tokens : float
+        The amount of reward tokens left in the old dao.
+
+        new_reward_tokens : float
+        The amount of reward tokens left in the new dao.
+    """
+
+    old_dao_balance = []
+    new_dao_balance = []
+    totalSupply = sum(original_balance)
+    old_reward_tokens = reward_tokens
+    new_reward_tokens = 0
+
+    for vote, orig in zip(votes, original_balance):
+        if vote:
+            new_dao_balance.append(orig * dao_balance / totalSupply)
+            old_dao_balance.append(0)
+            rewardToMove = float(orig) * reward_tokens / float(totalSupply)
+            old_reward_tokens -= float(rewardToMove)
+            new_reward_tokens += float(rewardToMove)
+        else:
+            old_dao_balance.append(orig)
+            new_dao_balance.append(0)
+    return (
+        old_dao_balance,
+        new_dao_balance,
+        old_reward_tokens,
+        new_reward_tokens
+    )
+
+
+def prepare_test_split(framework, split_gas):
+    if framework.prop_id != 2:
+        # run the rewards scenario first
+        framework.run_scenario('rewards')
+
+    debate_secs = 15
+    votes = create_votes_array(
+        framework.token_amounts,
+        not framework.args.proposal_fail
+    )
[…]

### 2016-03-16 tests/test.py

@@ -8,14 +8,10 @@ import json
 import subprocess
 import shutil
 import sys
-from datetime import datetime
+import importlib
 from string import Template
-import random
 from utils import (
-    constrained_sum_sample_pos, rm_file, determine_binary, ts_now,
-    create_votes_array, arr_str, eval_test, write_js,
-    count_token_votes, create_genesis, calculate_reward, tokens_after_split,
-    calculate_closing_time, extract_test_dict, edit_dao_source
+    rm_file, determine_binary, write_js, create_genesis, edit_dao_source
 )
 from args import test_args
 
@@ -36,16 +32,6 @@ class TestContext():
         self.geth = determine_binary(args.geth, 'geth')
 
         self.min_value = args.min_value
-        self.test_scenarios = {
-            'none': self.run_test_none,
-            'deploy': self.run_test_deploy,
-            'fund': self.run_test_fund,
-            'proposal': self.run_test_proposal,
-            'rewards': self.run_test_rewards,
-            'split': self.run_test_split,
-            'split-insufficient-gas': self.run_test_split_insufficient_gas,
-        }
-
         # keep this at end since any data loaded should override constructor
         if args.clean_chain:
             self.clean_blockchain()
@@ -197,8 +183,9 @@ class TestContext():
         and it returns the edited substitutions map
         """
         print("Creating {}.js".format(name))
+        scenario_dir = os.path.join(self.tests_dir, "scenarios", name)
         with open(
-                os.path.join(self.templates_dir, '{}.template.js'.format(name)),
+                os.path.join(scenario_dir, '{}.template.js'.format(name)),
                 'r'
         ) as f:
             data = f.read()
@@ -208,236 +195,12 @@ class TestContext():
         s = tmpl.substitute(substitutions)
         write_js("{}.js".format(name), s, len(self.accounts))
 
-    def run_test_deploy(self):
-        print("Running the Deploy Test Scenario")
-        self.create_js_file(
-            'deploy',
-            {
-                "dao_abi": self.dao_abi,
-                "dao_bin": self.dao_bin,
-                "creator_abi": self.creator_abi,
-                "creator_bin": self.creator_bin,
-                "offer_abi": self.offer_abi,
-                "offer_bin": self.offer_bin,
-                "offer_onetime": self.args.offer_onetime_costs,
-                "offer_total": self.args.offer_total_costs,
-                "min_value": self.min_value,
-            },
-            calculate_closing_time
-        )
-        output = self.run_script('deploy.js')
-        results = extract_test_dict('deploy', output)
[…]

### 2016-03-16 tests/utils.py

@@ -208,18 +208,6 @@ def count_token_votes(amounts, votes):
             nay += amount
     return yay, nay
 
-
-def calculate_reward(tokens, total_tokens, total_rewards):
-    result = (tokens * float(total_rewards)) / float(total_tokens)
-    return result
-
-
-def calculate_closing_time(obj, script_name, substitutions):
-    obj.closing_time = seconds_in_future(obj.args.closing_time)
-    substitutions['closing_time'] = obj.closing_time
-    return substitutions
-
-
 def edit_dao_source(contracts_dir, keep_limits):
     with open(os.path.join(contracts_dir, 'DAO.sol'), 'r') as f:
         contents = f.read()
@@ -283,59 +271,3 @@ def edit_dao_source(contracts_dir, keep_limits):
         f.write(contents)
 
     return new_path
-
-
-def tokens_after_split(votes, original_balance, dao_balance, reward_tokens):
-    """
-    Create expected token and reward token results after the split scenario
-        Parameters
-        ----------
-        votes : array of booleans
-        The votes array of what each user voted
-
-        original_balance : array of ints
-        The original amount of tokens each user had before the split
-
-        dao_balance : int
-        The balance of ether left in the DAO before the scenario started
-
-        reward_tokens : float
-        Amount of reward tokens generated in the DAO before the scenario.
-
-        Returns
-        ----------
-        old_dao_balance : array of ints
-        The balance of tokens left in the old dao.
-
-        new_dao_balance : array of ints
-        The balance of tokens left in the new dao.
-
-        old_reward_tokens : float
-        The amount of reward tokens left in the old dao.
-
-        new_reward_tokens : float
-        The amount of reward tokens left in the new dao.
-    """
-
-    old_dao_balance = []
-    new_dao_balance = []
-    totalSupply = sum(original_balance)
-    old_reward_tokens = reward_tokens
-    new_reward_tokens = 0
-
-    for vote, orig in zip(votes, original_balance):
-        if vote:
-            new_dao_balance.append(orig * dao_balance / totalSupply)
-            old_dao_balance.append(0)
-            rewardToMove = float(orig) * reward_tokens / float(totalSupply)
-            old_reward_tokens -= float(rewardToMove)
-            new_reward_tokens += float(rewardToMove)
-        else:
-            old_dao_balance.append(orig)
-            new_dao_balance.append(0)
-    return (
-        old_dao_balance,
-        new_dao_balance,
-        old_reward_tokens,
-        new_reward_tokens
-    )

### 2016-03-16 tests/scenarios/fund/run.py
Combine run_script and eval_test into one

@@ -44,8 +44,7 @@ def run(framework):
         "Notice: Funding period is {} seconds so the test will wait "
         "as much".format(sale_secs)
     )
-    output = framework.run_script('fund.js')
-    eval_test('fund', output, {
+    framework.execute('fund', {
         "dao_funded": True,
         "total_supply": framework.total_supply,
         "balances": framework.token_amounts,

### 2016-03-16 tests/scenarios/proposal/run.py

@@ -53,8 +53,7 @@ def run(framework):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
-    output = framework.run_script('proposal.js')
-    eval_test('proposal', output, {
+    framework.execute('proposal', {
         "dao_proposals_number": "1",
         "proposal_passed": True,
         "proposal_yay": yay,

### 2016-03-16 tests/scenarios/rewards/run.py

@@ -35,8 +35,7 @@ def run(framework):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
-    output = framework.run_script('rewards.js')
-    results = eval_test('rewards', output, {
+    results = framework.execute('rewards', {
         "provider_reward_portion": calculate_reward(
             framework.token_amounts[0],
             framework.total_supply,

### 2016-03-16 tests/scenarios/split/run.py

@@ -91,8 +91,7 @@ def prepare_test_split(framework, split_gas):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
-    output = framework.run_script('split.js')
-    return votes, output
+    return votes
 
 
 def run(framework):
@@ -102,14 +101,14 @@ def run(framework):
     # This should happen with the latest homestead changes:
     # https://github.com/ethereum/EIPs/blob/master/EIPS/eip-2.mediawiki#specification
     split_gas = 4000000
-    votes, output = prepare_test_split(framework, split_gas)
+    votes = prepare_test_split(framework, split_gas)
     oldBalance, newBalance, oldDAORewards, newDAORewards = tokens_after_split(
         votes,
         framework.token_amounts,
         framework.dao_balance_after_rewards,
         framework.dao_rewardToken_after_rewards
     )
-    eval_test('split', output, {
+    framework.execute('split', {
         # default deposit,a simple way to test new DAO contract got created
         "newDAOProposalDeposit": 20,
         "oldDAOBalance": oldBalance,

### 2016-03-16 tests/test.py

@@ -11,7 +11,8 @@ import sys
 import importlib
 from string import Template
 from utils import (
-    rm_file, determine_binary, write_js, create_genesis, edit_dao_source
+    rm_file, determine_binary, write_js,
+    create_genesis, edit_dao_source, eval_test
 )
 from args import test_args
 
@@ -194,6 +195,10 @@ class TestContext():
             substitutions = cb_before_creation(self, name, substitutions)
         s = tmpl.substitute(substitutions)
         write_js("{}.js".format(name), s, len(self.accounts))
+
+    def execute(self, name, expected):
+        output = self.run_script('{}.js'.format(name))
+        return eval_test(name, output, expected)
 
     def run_scenario(self, name):
         if name == 'None':

### 2016-03-16 tests/utils.py

@@ -208,6 +208,7 @@ def count_token_votes(amounts, votes):
             nay += amount
     return yay, nay
 
+
 def edit_dao_source(contracts_dir, keep_limits):
     with open(os.path.join(contracts_dir, 'DAO.sol'), 'r') as f:
         contents = f.read()

### 2016-03-16 tests/test.py
Templates don't need to have a name anymore

@@ -186,7 +186,7 @@ class TestContext():
         print("Creating {}.js".format(name))
         scenario_dir = os.path.join(self.tests_dir, "scenarios", name)
         with open(
-                os.path.join(scenario_dir, '{}.template.js'.format(name)),
+                os.path.join(scenario_dir, 'template.js'),
                 'r'
         ) as f:
             data = f.read()

### 2016-03-16 tests/scenarios/fund_fail/run.py
Introduce fund_fail scenario and simplify tests

@@ -16,7 +16,7 @@ def run(framework):
         framework.run_scenario('deploy')
     else:
         print(
-            "WARNING: Running the funding scenario with a pre-deployed "
+            "WARNING: Running the failed funding scenario with a pre-deployed "
             "DAO contract. Closing time is {} which is approximately {} "
             "seconds from now.".format(
                 datetime.fromtimestamp(framework.closing_time).strftime(
@@ -26,13 +26,14 @@ def run(framework):
             )
         )
 
+    accounts_num = len(framework.accounts)
     sale_secs = framework.closing_time - ts_now()
-    framework.total_supply = framework.min_value + random.randint(1, 100)
+    framework.total_supply = random.randint(5, framework.min_value - 2)
     framework.token_amounts = constrained_sum_sample_pos(
-        len(framework.accounts), framework.total_supply
+        accounts_num, framework.total_supply
     )
     framework.create_js_file(
-        'fund',
+        'fund_fail',
         {
             "dao_abi": framework.dao_abi,
             "dao_address": framework.dao_addr,
@@ -44,10 +45,9 @@ def run(framework):
         "Notice: Funding period is {} seconds so the test will wait "
         "as much".format(sale_secs)
     )
-
-    framework.execute('fund', {
-        "dao_funded": True,
+    framework.execute('fund_fail', {
+        "dao_funded": False,
         "total_supply": framework.total_supply,
-        "balances": framework.token_amounts,
-        "user0_after": framework.token_amounts[0],
+        "balances": [0] * accounts_num,
+        "refund": framework.token_amounts[0:1]
     })

### 2016-03-16 tests/scenarios/fund_fail/template.js

@@ -1,0 +1,66 @@
+var amounts = $amounts;
+
+var dao = web3.eth.contract($dao_abi).at('$dao_address');
+console.log("Buying DAO tokens");
+for (i = 0; i < eth.accounts.length; i++) {
+    web3.eth.sendTransaction({
+        from:eth.accounts[i],
+        to: dao.address,
+        gas:200000,
+        value:web3.toWei(amounts[i], "ether")
+    });
+}
+
+checkWork();
+
+setTimeout(function() {
+    miner.stop(0);
+    addToTest('dao_funded', dao.isFunded());
+    addToTest('total_supply', parseInt(web3.fromWei(dao.totalSupply())));
+    var balances = [];
+    for (i = 0; i < eth.accounts.length; i++) {
+        balances.push(parseInt(web3.fromWei(dao.balanceOf(eth.accounts[i]))));
+    }
+    addToTest('balances', balances);
+
+    // since funding failed let's get a refund (only first 2 users for now)
+    var eth_balance_before_refund = [];
+    for (i = 0; i < 2; i++) {
+        eth_balance_before_refund.push(parseInt(web3.fromWei(eth.getBalance(eth.accounts[i]))));
+    }
+    addToTest('eth_balance_before_refund', eth_balance_before_refund);
+    
+    for (i = 0; i < eth.accounts.length; i++) {
+        dao.refund.sendTransaction({
+            from:eth.accounts[i],
+            gas:200000
+        }); 
+    }
+    checkWork();
+    // try to ask for a refund again and see if we get more (we shouldn't)
+    for (i = 0; i < eth.accounts.length; i++) {
+        dao.refund.sendTransaction({
+            from:eth.accounts[i],
+            gas:200000
+        }); 
+    }
+    checkWork();
+    var eth_balance_after_refund = [];
+    for (i = 0; i < 2; i++) {
+        eth_balance_after_refund.push(parseInt(web3.fromWei(eth.getBalance(eth.accounts[i]))));
+    }
+    addToTest('eth_balance_after_refund', eth_balance_after_refund);
+
+    var refund = [];
+    for (i = 0; i < 2; i++) {
+        refund.push(bigDiffRound(
+            testMap['eth_balance_after_refund'][i],
+            testMap['eth_balance_before_refund'][i]
+        ));
+    }
+    addToTest('refund', refund);
+
+    testResults();
+}, $wait_ms);
+console.log("Wait for end of sale");
+miner.start(1);

### 2016-03-16 tests/scenarios/proposal/run.py

@@ -53,12 +53,8 @@ def run(framework):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
+
     framework.execute('proposal', {
-=======
-    output = framework.run_script('proposal.js')
-    eval_test('proposal', output, {
->>>>>>> Each DAO scenario is now in its own directory
         "dao_proposals_number": "1",
         "proposal_passed": True,
         "proposal_yay": yay,

### 2016-03-16 tests/scenarios/rewards/run.py

@@ -35,12 +35,8 @@ def run(framework):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
+
     results = framework.execute('rewards', {
-=======
-    output = framework.run_script('rewards.js')
-    results = eval_test('rewards', output, {
->>>>>>> Each DAO scenario is now in its own directory
         "provider_reward_portion": calculate_reward(
             framework.token_amounts[0],
             framework.total_supply,

### 2016-03-16 tests/scenarios/split/run.py

@@ -91,12 +91,7 @@ def prepare_test_split(framework, split_gas):
         "Notice: Debate period is {} seconds so the test will wait "
         "as much".format(debate_secs)
     )
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     return votes
-=======
-    output = framework.run_script('split.js')
-    return votes, output
->>>>>>> Each DAO scenario is now in its own directory
 
 
 def run(framework):
@@ -106,22 +101,16 @@ def run(framework):
     # This should happen with the latest homestead changes:
     # https://github.com/ethereum/EIPs/blob/master/EIPS/eip-2.mediawiki#specification
     split_gas = 4000000
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
+
     votes = prepare_test_split(framework, split_gas)
-=======
-    votes, output = prepare_test_split(framework, split_gas)
->>>>>>> Each DAO scenario is now in its own directory
     oldBalance, newBalance, oldDAORewards, newDAORewards = tokens_after_split(
         votes,
         framework.token_amounts,
         framework.dao_balance_after_rewards,
         framework.dao_rewardToken_after_rewards
     )
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
+
     framework.execute('split', {
-=======
-    eval_test('split', output, {
->>>>>>> Each DAO scenario is now in its own directory
         # default deposit,a simple way to test new DAO contract got created
         "newDAOProposalDeposit": 20,
         "oldDAOBalance": oldBalance,

### 2016-03-16 tests/test.py

@@ -11,12 +11,9 @@ import sys
 import importlib
 from string import Template
 from utils import (
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     rm_file, determine_binary, write_js,
-    create_genesis, edit_dao_source, eval_test
-=======
+    create_genesis, edit_dao_source, eval_test,
     rm_file, determine_binary, write_js, create_genesis, edit_dao_source
->>>>>>> Each DAO scenario is now in its own directory
 )
 from args import test_args
 
@@ -190,11 +187,7 @@ class TestContext():
         print("Creating {}.js".format(name))
         scenario_dir = os.path.join(self.tests_dir, "scenarios", name)
         with open(
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
                 os.path.join(scenario_dir, 'template.js'),
-=======
-                os.path.join(scenario_dir, '{}.template.js'.format(name)),
->>>>>>> Each DAO scenario is now in its own directory
                 'r'
         ) as f:
             data = f.read()
@@ -204,13 +197,10 @@ class TestContext():
         s = tmpl.substitute(substitutions)
         write_js("{}.js".format(name), s, len(self.accounts))
 
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
     def execute(self, name, expected):
         output = self.run_script('{}.js'.format(name))
         return eval_test(name, output, expected)
 
-=======
->>>>>>> Each DAO scenario is now in its own directory
     def run_scenario(self, name):
         if name == 'None':
             print("Asked to run no scenario. Quitting ...")

### 2016-03-16 tests/utils.py

@@ -208,10 +208,7 @@ def count_token_votes(amounts, votes):
             nay += amount
     return yay, nay
 
-<<<<<<< 613f71c70f5341865f226f5d970820c0ed9f4325
 
-=======
->>>>>>> Each DAO scenario is now in its own directory
 def edit_dao_source(contracts_dir, keep_limits):
     with open(os.path.join(contracts_dir, 'DAO.sol'), 'r') as f:
         contents = f.read()

### 2016-03-17 paper/Paper.tex

@@
 The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent.
-The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$.
-Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time as described in section \ref{TokenPrice}.
+The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time as described in section \ref{TokenPrice}.
 
@@
 \begin{equation}
-\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut}}[\text{sender}]
+\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut[sender]}}
 \end{equation}
-Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut}}[\text{sender}]$ is the total amount of wei which has already been paid out to the DAO token holder calling the function.
+Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function.
 The reward tokens are further elaborated in section \ref{split}.
@@
     /// ether and Reward Tokens to the new DAO. It will also burn the DAO Tokens
-    /// of the sender. (TODO: document rewardTokens - done??)
+    /// of the sender. 
     function splitDAO(
@@
         if (deploymentReward > 10 ether && msg.sender != address(client))
-            throw; // TODO, set a max defined by service provider, or ideally oracle (set in euro)
+            throw; 
         deploymentReward = _deploymentReward;

### 2016-03-17 tests/scenarios/deploy/deploy.template.js
Remove extra files causing problems after rebase

@@ -1,66 +1,0 @@
-var _defaultServiceProvider = web3.eth.accounts[0];
-var daoContract = web3.eth.contract($dao_abi);
-console.log("Creating DAOCreator Contract");
-var creatorContract = web3.eth.contract($creator_abi);
-var _daoCreatorContract = creatorContract.new(
-    {
-	from: web3.eth.accounts[0],
-	data: '$creator_bin',
-	gas: 3000000
-    }, function (e, contract){
-	if (e) {
-            console.log(e+" at DAOCreator creation!");
-	} else if (typeof contract.address != 'undefined') {
-        addToTest('dao_creator_address', contract.address);
-        checkWork();
-        var dao = daoContract.new(
-		    _defaultServiceProvider,
-		    contract.address,
-		    $min_value,
-		    $closing_time,
-            0,
-		    {
-		        from: web3.eth.accounts[0],
-		        data: '$dao_bin',
-		        gas: 4000000
-		    }, function (e, contract) {
-		        // funny thing, without this geth hangs
-		        console.log("At DAO creation callback");
-		        if (typeof contract.address != 'undefined') {
-                    addToTest('dao_address', contract.address);
-		        }
-		    });
-        checkWork();
-	}
-    });
-checkWork();
-var offerContract = web3.eth.contract($offer_abi);
-var offer = offerContract.new(
-    _defaultServiceProvider, //service provider
-    '0x0',  // This is a hash of the paper contract. Does not matter for testing
-    web3.toWei($offer_total, "ether"), //total costs
-    web3.toWei($offer_onetime, "ether"), //one time costs
-    web3.toWei(1, "ether"), //min daily costs
-    web3.toWei(1, "ether"), //reward divison
-    web3.toWei(1, "ether"), //deployment rewards
-    {
-	    from: web3.eth.accounts[0],
-	    data: '$offer_bin',
-	    gas: 3000000
-    }, function (e, contract) {
-	    if (e) {
-            console.log(e + " at Offer Contract creation!");
-	    } else if (typeof contract.address != 'undefined') {
-            addToTest('offer_address', contract.address);
-        }
-    }
-);
-checkWork();
-console.log("mining contract, please wait");
-miner.start(1);
-setTimeout(function() {
-    miner.stop(0);
-    testResults();
-}, 3000);
-
-

### 2016-03-17 tests/scenarios/fund/fund.template.js

@@ -1,40 +1,0 @@
-var amounts = $amounts;
-
-var dao = web3.eth.contract($dao_abi).at('$dao_address');
-console.log("Buying DAO tokens");
-for (i = 0; i < eth.accounts.length; i++) {
-    web3.eth.sendTransaction({
-        from:eth.accounts[i],
-        to: dao.address,
-        gas:200000,
-        value:web3.toWei(amounts[i], "ether")
-    });
-}
-
-checkWork();
-
-setTimeout(function() {
-    miner.stop(0);
-    addToTest('dao_funded', dao.isFunded());
-    addToTest('total_supply', parseInt(web3.fromWei(dao.totalSupply())));
-    var balances = [];
-    for (i = 0; i < eth.accounts.length; i++) {
-        balances.push(parseInt(web3.fromWei(dao.balanceOf(eth.accounts[i]))));
-    }
-    addToTest('balances', balances);
-
-    // now also try to purchase some extra tokens after the sale ended
-    web3.eth.sendTransaction({
-        from:eth.accounts[0],
-        to: dao.address,
-        gas:200000,
-        value:web3.toWei(20, "ether")
-    });
-    // and confirm balance is still the same
-    checkWork();
-    addToTest('user0_after', parseInt(web3.fromWei(dao.balanceOf(eth.accounts[0]))));
-
-    testResults();
-}, $wait_ms);
-console.log("Wait for end of sale");
-miner.start(1);

### 2016-03-17 tests/scenarios/proposal/proposal.template.js

@@ -1,86 +1,0 @@
-var dao = web3.eth.contract($dao_abi).at('$dao_address');
-var offer = web3.eth.contract($offer_abi).at('$offer_address');
-
-console.log("Add offer contract as allowed recipient");
-dao.addAllowedAddress.sendTransaction('$offer_address', {from: serviceProvider, gas: 1000000});
-checkWork();
-
-addToTest('creator_balance_before', web3.fromWei(eth.getBalance(proposalCreator)));
-console.log("Creating a new proposal for $offer_amount ether.");
-var tx_hash = null;
-dao.newProposal.sendTransaction(
-    '$offer_address',
-    web3.toWei($offer_amount, "ether"),
-    '$offer_desc',
-    '$transaction_bytecode',
-    $debating_period,
-    false,
-    {
-        from: proposalCreator,
-        value: web3.toWei($proposal_deposit, "ether"),
-        gas: 1000000
-    }
-    , function (e, res) {
-        if (e) {
-            console.log(e + "at newProposal()!");
-        } else {
-            tx_hash = res;
-            console.log("newProposal tx hash is: " + tx_hash);
-        }
-    }
-);
-checkWork();
-
-addToTest('creator_balance_after_proposal', web3.fromWei(eth.getBalance(proposalCreator)));
-addToTest(
-    'calculated_deposit',
-    bigDiffRound(testMap['creator_balance_before'], testMap['creator_balance_after_proposal'])
-);
-addToTest('dao_proposals_number', dao.numberOfProposals());
-
-var votes = $votes;
-var prop_id = 1;
-
-console.log("Deadline is: " + dao.proposals(prop_id)[3] + " Voting ... ");
-for (i = 0; i < votes.length; i++) {
-    console.log("User " + i +" is voting ["+ votes[i] +"]. His token balance is: " + web3.fromWei(dao.balanceOf(eth.accounts[i])) + " ether and NOW is: " + Math.floor(Date.now() / 1000));
-    dao.vote.sendTransaction(
-        prop_id,
-        votes[i],
-        {
-            from: eth.accounts[i],
-            gas: 1000000
-        }
-    );
-}
-checkWork();
-addToTest('proposal_yay', parseInt(web3.fromWei(dao.proposals(prop_id)[9])));
-addToTest('proposal_nay', parseInt(web3.fromWei(dao.proposals(prop_id)[10])));
-addToTest('provider_balance_before', web3.fromWei(eth.getBalance(serviceProvider)));
-
-setTimeout(function() {
[…]

### 2016-03-17 tests/scenarios/rewards/rewards.template.js

@@ -1,75 +1,0 @@
-var dao = web3.eth.contract($dao_abi).at('$dao_address');
-
-// some kind soul makes a donation to the DAO, so rewards get populated
-console.log("Donating to DAO...");
-dao.payDAO.sendTransaction({
-    from: eth.accounts[1],
-    value: web3.toWei($total_rewards, "ether"),
-    gas: 100000
-});
-checkWork();
-
-// create a new proposal for sending this whole donation to the rewardAccount
-console.log("Creating proposal to send to rewardAccount...");
-var tx_hash = null;
-dao.newProposal.sendTransaction(
-    dao.rewardAccount(),
-    web3.toWei($total_rewards, "ether"),
-    'Send money to the reward account',
-    '$transaction_bytecode', // bytecode, not needed here, calling the fallback function
-    $debating_period,
-    false,
-    {
-        from: proposalCreator,
-        value: web3.toWei($proposal_deposit, "ether"),
-        gas: 1000000
-    }
-    , function (e, res) {
-        if (e) {
-            console.log(e + "at newProposal()!");
-        } else {
-            tx_hash = res;
-            console.log("newProposal tx hash is: " + tx_hash);
-        }
-    }
-);
-checkWork();
-
-
-var prop_id = $prop_id;
-console.log("Voting for proposal '" + prop_id + "' ...");
-// in this scenario let's just say everyone votes 100% in favour
-for (i = 0; i < eth.accounts.length; i++) {
-    dao.vote.sendTransaction(
-        prop_id,
-        true,
-        {
-            from: eth.accounts[i],
-            gas: 1000000
-        }
-    );
-}
-checkWork();
-
-setTimeout(function() {
-    miner.stop(0);
-    console.log("Executing the proposal...");
-    // now execute the proposal
-    dao.executeProposal.sendTransaction(prop_id, '$transaction_bytecode', {from:serviceProvider, gas:1000000});
-    checkWork();
-    addToTest('provider_balance_before_claim', eth.getBalance(serviceProvider));
-    console.log("Claiming the reward...");
-    dao.getMyReward.sendTransaction({from: serviceProvider, gas: 1000000});
-    checkWork();
-    addToTest('provider_balance_after_claim', eth.getBalance(serviceProvider));
-    addToTest(
-        'provider_reward_portion',
-        parseFloat(web3.fromWei(bigDiff(
[…]

### 2016-03-17 tests/scenarios/split/split.template.js

@@ -1,82 +1,0 @@
-var dao = web3.eth.contract($dao_abi).at('$dao_address');
-var newServiceProvider = eth.accounts[1];
-
-// create a new proposal for sending this whole donation to the rewardAccount
-console.log("Creating proposal to change SP...");
-var tx_hash = null;
-dao.newProposal.sendTransaction(
-    newServiceProvider, // new SP
-    0,
-    'Changing SP to eth.accounts[1]',
-    '',
-    $debating_period,
-    true,
-    {
-        from: proposalCreator,
-        gas: 1000000
-    }
-    , function (e, res) {
-        if (e) {
-            console.log(e + "at newProposal()!");
-        } else {
-            tx_hash = res;
-            console.log("newProposal tx hash is: " + tx_hash);
-        }
-    }
-);
-checkWork();
-
-var votes = $votes;
-var prop_id = $prop_id;
-console.log("Voting for split proposal '" + prop_id + "' ...");
-for (i = 0; i < votes.length; i++) {
-    dao.vote.sendTransaction(
-        prop_id,
-        votes[i],
-        {
-            from: eth.accounts[i],
-            gas: 1000000
-        }
-    );
-}
-checkWork();
-addToTest('proposal_yay', parseInt(web3.fromWei(dao.proposals(prop_id)[9])));
-addToTest('proposal_nay', parseInt(web3.fromWei(dao.proposals(prop_id)[10])));
-
-setTimeout(function() {
-    miner.stop(0);
-    console.log("Executing the split proposal...");
-    // now each user who voted for the split should call splitDAO to execute the proposal
-    for (i = 0; i < votes.length; i++) {
-        if (votes[i]) {
-            dao.splitDAO.sendTransaction(
-                prop_id,
-                newServiceProvider,
-                {from:eth.accounts[i], gas: $split_gas}
-            );
-        }
-    }
-    checkWork();
-    console.log("After split execution");
-    addToTest('proposal_passed', dao.proposals(prop_id)[5]);
-    addToTest('proposal_newdao', dao.splitProposalNewAddress(prop_id, 0));
-
-    var newdao = web3.eth.contract($dao_abi).at(testMap['proposal_newdao']);
-    // check token balance of each user in both DAOs
-    oldDAOBalance = [];
-    newDAOBalance = [];
[…]

### 2016-03-17 tests/scenarios/fund_fail/run.py
Working verison of the fund_fail scenario
- Also fixed the depoyed DAO's minValue. Should be in Wei not Ether :)

@@ -28,7 +28,7 @@ def run(framework):
 
     accounts_num = len(framework.accounts)
     sale_secs = framework.closing_time - ts_now()
-    framework.total_supply = random.randint(5, framework.min_value - 2)
+    framework.total_supply = random.randint(5, framework.min_value - 4)
     framework.token_amounts = constrained_sum_sample_pos(
         accounts_num, framework.total_supply
     )
@@ -48,6 +48,5 @@ def run(framework):
     framework.execute('fund_fail', {
         "dao_funded": False,
         "total_supply": framework.total_supply,
-        "balances": [0] * accounts_num,
-        "refund": framework.token_amounts[0:1]
+        "refund": framework.token_amounts[0:2]
     })

### 2016-03-17 tests/scenarios/fund_fail/template.js

@@ -15,18 +15,14 @@ checkWork();
 
 setTimeout(function() {
     miner.stop(0);
+    addToTest('dao_minValue', dao.minValue());
     addToTest('dao_funded', dao.isFunded());
     addToTest('total_supply', parseInt(web3.fromWei(dao.totalSupply())));
-    var balances = [];
-    for (i = 0; i < eth.accounts.length; i++) {
-        balances.push(parseInt(web3.fromWei(dao.balanceOf(eth.accounts[i]))));
-    }
-    addToTest('balances', balances);
 
     // since funding failed let's get a refund (only first 2 users for now)
     var eth_balance_before_refund = [];
     for (i = 0; i < 2; i++) {
-        eth_balance_before_refund.push(parseInt(web3.fromWei(eth.getBalance(eth.accounts[i]))));
+        eth_balance_before_refund.push(web3.fromWei(eth.getBalance(eth.accounts[i])));
     }
     addToTest('eth_balance_before_refund', eth_balance_before_refund);
     
@@ -47,16 +43,16 @@ setTimeout(function() {
     checkWork();
     var eth_balance_after_refund = [];
     for (i = 0; i < 2; i++) {
-        eth_balance_after_refund.push(parseInt(web3.fromWei(eth.getBalance(eth.accounts[i]))));
+        eth_balance_after_refund.push(web3.fromWei(eth.getBalance(eth.accounts[i])));
     }
     addToTest('eth_balance_after_refund', eth_balance_after_refund);
 
     var refund = [];
     for (i = 0; i < 2; i++) {
-        refund.push(bigDiffRound(
+        refund.push((bigDiffRound(
             testMap['eth_balance_after_refund'][i],
             testMap['eth_balance_before_refund'][i]
-        ));
+        )));
     }
     addToTest('refund', refund);
 

### 2016-04-05 deploy/deploy.js
Rename compile.py/js to prepare.py/js

@@ -1,5 +1,6 @@
-//first run code.js to import the compiled source code
-//before you do that run compile.py to compile the latest version of the software in DAO
+// first run prepare.js to import the compiled source code and some other helper variables
+// before you do that run prepare.py to compile the latest version of the software in DAO
+// and populate the helper variables
 
 personal.unlockAccount(eth.accounts[0]);
 var _defaultServiceProvider = web3.eth.accounts[0];

### 2016-04-05 deploy/deploy.js
Fix error in deploy/deploy.js

@@ -13,7 +13,7 @@ console.log("Creating DAOCreator Contract");
 var _daoCreatorContract = creatorContract.new(
     {
 	    from: web3.eth.accounts[0],
-	    data: dao_bin,
+	    data: creator_bin,
 	    gas: 4000000
     }, function (e, contract){
 	    if (e) {

### 2016-04-05 deploy/deploy.js
Deployment script: Make SP parameterizable

@@ -3,7 +3,6 @@
 // and populate the helper variables
 
 personal.unlockAccount(eth.accounts[0]);
-var _defaultServiceProvider = web3.eth.accounts[0];
 var daoContract = web3.eth.contract(dao_abi);
 var min_value = 1;
 var closing_time = new Date().getTime() + seconds_from_now;
@@ -21,7 +20,7 @@ var _daoCreatorContract = creatorContract.new(
 	    } else if (typeof contract.address != 'undefined') {
             console.log("Reached actual DAO creation");
             var dao = daoContract.new(
-	            _defaultServiceProvider,
+	            service_provider,
 	            contract.address,
 	            web3.toWei(min_value, "ether"),
                 closing_time,

### 2016-04-05 deploy/prepare.py

@@ -38,11 +38,16 @@ if __name__ == "__main__":
         default=60,
         help='Deployed DAO sale duration in minutes'
     )
+    p.add_argument(
+        '--service-provider',
+        default="0x08144824954c65b12f68b75072488e634ac4e67a",  # Griff testnet
+        help='Account to set as service provider'
+    )
     args = p.parse_args()
     solc = determine_binary(args.solc, 'solc')
     comp = compile_contract(solc, "../DAO.sol")
 
-    with open("code.js", "w") as f:
+    with open("prepare.js", "w") as f:
         f.write("dao_abi = {};\n".format(comp['contracts']['DAO']['abi']))
         f.write("dao_bin = '{}';\n".format(comp['contracts']['DAO']['bin']))
         f.write("creator_abi = {};\n".format(
@@ -54,3 +59,4 @@ if __name__ == "__main__":
         f.write("seconds_from_now = {};\n".format(
           args.sale_duration_mins * 60)
         )
+        f.write("service_provider = {};\n".format(args.service_provider))

### 2016-04-05 paper/Paper.tex
fix price function in paper
clearify text
Corrections to WP

@@
 \end{equation}
-Where $d$ is the \verb|minQuorumDivisor|. This parameter’s default value is $5$, but it will double in the case the quorum has not been met for over a year.
+Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
 $\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward token as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}).
@@
 
-A problem this simple fix doesn’t address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely.
+A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely.
 An attacker could use this to their advantage.
@@
 There is no quorum requirement, so that every token holder has the ability to split into their own DAO.
-The debating period is used to discuss the new service provider and conduct an informal vote.
-The result of the vote has no actual consequence, it is purely instructional.
-After this first voting round, token holders can cast a second vote to confirm the result.
+The debating period is used to discuss (on or off-chain) the new service provider and conduct a first vote that's non-binding.
+After this first vote, token holders can cast a second one to confirm its results.
 In the case a majority opts to  keep the original service provider, the minority can either change their vote to keep the original service provider in order to avoid a split, or inversely they can confirm their vote for a new service provider and move their portion of the funds to a new DAO.
@@
 \section{Token Price} \label{TokenPrice}
-In order to reward contributors who purchase tokens early during the funding period, since they had less information, and hence a greater risk, than contributors who joined later, they will pay less than contributors who joined later.
+DAO Token price increases over time.
+This reflects an assumption that early purchasers have greater risk, as they may have less information about the potential success of the DAO and do not know whether follow-on contribution will lead to full funding of the DAO.
 For the DAO described here, we have chosen the following price schedule:
@@
 0.01 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
-0.01 + 0.005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
+0.01 + 0.0005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
 0.015 & \text{otherwise}
@@
 This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
-Their portion $S$ is calculated as follows:
+Their portion of the reward tokens $S$ is calculated as follows:
 \begin{equation}

### 2016-04-05 paper/Paper.tex
clarification on minQuorumDivisor
Hiro Mant [7:01 AM] 
I don't get this sentence from the whitepaper:

Hiro Mant [7:06 AM] 
> The sum ΞDAO + Rtotal is equal to the amount of ether raised plus the rewards received.
(p.2) (edited)

[7:08] 
If the DAO already spent some Ether to earlier proposals, E_DAO will be smaller than E_raised.
Where am I wrong here?

Hiro Mant [10:32 AM] 
@griff: But two lines above the cited phrase, it says:

[10:32] 
>  ΞDAO is the amount of ether owned by the DAO

[10:33] 
So EDAO is not the total recived  (sale+rewards

[10:33] 
but income - spent

[10:33] 
?

@@
 Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
-$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward token as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}).
-The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received.
+$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward tokens ever generated as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}).
+The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received or said another way, the total amount of ether the DAO has ever received.
 

### 2016-04-05 paper/Paper.tex
second round of changes

--- 2016-04-05 paper/Paper.tex
@@
 
-\title{Decentralized autonomous organization to manage a trust\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}}
+\title{Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}}
 \author{
@@
 \begin{abstract}
-This document describes the first implementation of a Decentralized Autonomous Organization (DAO) decentralizing the management of a trust.
-This concept, as well as the majority robbing the minority attack vector are discussed, and a solution is proposed.
-Furthermore, a practical implementation of this type of DAO using smart contracts written in Solidity on the Ethereum blockchain is presented and described in detail.
+This paper describes the first implementation of Decentralized Autonomous Organization (DAO) code to automate organizational governance and decision-making.
+The code can be used by individuals working together collaboratively outside of a traditional corporate form.
+It can also be used by a registered corporate entity to automate formal governance rules contained in corporate bylaws or imposed by law.
+We first discuss the DAO Concept.
+We then discuss minority rights, and propose a solution to a ``robbing the minority'' attack vector.
+Finally, we provide a practical implementation of a first generation DAO entity using smart contracts written in Solidity on the Ethereum blockchain.
 \end{abstract}
@@
 
-Historically, the management of trusts has always been centralized.
-A group of individuals (trustees) would write a contract and combine their resources into one trust, which was then managed by a single person or company, with the trustees losing the power to directly control their money.
-The rise of crowdfunding (\cite{2015CFReport}), has lowered the barrier of entry to fund projects and has allowed for small contributors to participate in large projects.
-The money raised still carries the risk of being mismanaged by the company receiving the funding which all too often fails to follow through on its promises or outright disappears without a trace (\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}).
-Thanks to the development of Ethereum (\cite{buterin2013ethereum,Wood2014ethereum}), a blockchain technology which integrates a Turing complete programming language and the ability to process smart contracts, it is now possible to create an organization allowing the “trustees” to maintain direct control of their funds while still bundling many smaller contributions together to achieve a larger goal.
-We have written smart contracts (\cite{szabo1997formalizing, miller1997future}) that form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain.
-In this paper we detail the concept of a DAO managing a trust using a concrete example.
-
-After explaining the concept of the DAO, we will cover the ``Majority Robbing the Minority Attack'' and propose a solution, the ``DAO split''.
-Finally, we will explore the smart contracts and conclude with a more detailed specification of the ``DAO split''.
+Corporate entities of all kinds are governed by rules that describe permitted and proscribed conduct.
+These rules may exist as private contracts (like bylaws or shareholder agreements) between corporate owners.
+They may also be imposed by law in addition to or in the absence of a written agreement between participants.
+
+Historically, corporations have only been able to act through people (or through corporate entities that were themselves ultimately controlled by people).
+This presents two simple and fundamental problems.
+Whatever a private contract or public law require:  (1) people do not always follow the rules and (2) people do not always agree what the rules actually require.
+Collaboration without a corporate form does not solve these problems, necessarily, and it may introduce others.
+In the absence of a coporate form, an explicit written agreement is substituted for unclear informal ``understandings'' and legal protections provided by a corporate form will not be available.
+
+Rule-breaking within an organization not always obvious, and motives may not matter to stakeholders once their money has been lost.
+While bad behavior may make a corporation or its management civilly or criminally liable, punishment can come as little comfort to an investor who has already lost their money.
+
+Crowdfunding (\cite{2015CFReport}) amplifies the problem.
+On the one hand, it has made it easier for small contributors to invest in large projects.
+It has also made it possible for entrepeneurs to receive financial support that might not have been easily available in the past.
+On the other hand, small investors remain vulnerable to financial mismanagement or outright fraud.
+Because they have small stakes in a venture, they may lack power to identify problems, participate in governance decisions, or to easily recover their investment.
+(\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}).
+At the same time, corporate leadership and managment may be accused of malfeasance or mismanagement when they believe that they have acted in good faith, based on their understanding of their obligations and interpretation of applicable rules.
+
+We present a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality.
+We illustrate a method that for the first time allows the creation of organizations in which (1) ?participants?
+maintain direct real-time control of contributed funds and (2) where governance rules are formalized and automated using software.
+Specifically, we have written generic smart contract code (\cite{szabo1997formalizing, miller1997future}) that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain.
+In this paper we explain how the DAO code works.
+We do so by focusing on some basic formation and governance features, including formation, funding and voting rights.
+
+We first describe the DAO's formation and basic functionality.
+We then discuss minority owner rights and propose a solution to the ``Majority Robbing the Minority Attack'' problem, the ``DAO split''.
+We then explore the smart contract code in detail, and conclude with an explanation and detailed specification of the ``DAO split''.
 
@@
 
-\section{Concept}
-This section will cover the underlying concept of the DAO and what it is able to do.
-
-After the DAO is deployed on the Ethereum blockchain, anyone is able to fund it by sending ether (the digital fuel powering the Ethereum network) to the address of the DAO’s smart contract during a period of time set aside for the initial funding.
-In exchange, tokens are created which represent membership as well as ownership of a portion of the DAO; these tokens are assigned to the account that sent the ether.
-The amount of tokens created is proportional to the amount of ether transferred.
-The price per token varies over time (see section \ref{TokenPrice}).
-The ownership of these tokens can be transferred to other accounts using transactions on the Ethereum blockchain, as soon as the funding period is over.
-When deploying the contract, a minimum DAO funding goal and the period of time allowed for the initial funding are chosen.
-In the event the minimum funding amount is not reached at the end of the funding period, every contributor is refunded their ether.
+A word of caution, at the outset:  the legal status of DAOs remains the subject of active and vigorous debate and discussion.
+Not everyone shares the same definition.
+Some have said that they are autonomous code and can operate independently of legal systems; others have said that they must be owned or operate by humans or human created entities.
+There will be many uses cases, and the DAO code will develop over time.
+Ultimately, how a DAO functions and its legal status will depend on many factors, including how DAO code is used, where it is used, and who uses it.
+We do not speculate about the legal status of DAOs worldwide.
+This paper is not intended to offer legal advice or conclusions.
+Anyone who uses DAO code will do so at their own risk.
+
+\section{Dao Concept | Dao Practice}
+
+DAO code is written in the ``Solidity'' programming language.  A DAO is activated by deployment on the Ethereum blockchain.
+
+Once deployed, the DAO code requires ``ether'' to engage in transactions on Ethereum.
+(Ether is the digital fuel that powers the Ethereum network).
+Without ether, a DAO can not do very much and a DAO's first order of business is to receive ether.
+After the DAO code is deployed, ether may be sent to the DAO?s smart contract address during an initial funding period which is defined in the DAO code.
+
+In exchange for ether, the DAO code creates tokens that are then assigned to the account of the person who sent the ether.
+A token grants its holder voting and ownership rights.
+The number of tokens created is proportional to the amount of ether transferred.
+Token price varies over time (see section \ref{TokenPrice}).
+Token ownership is freely transferable on the Ethereum blockchain, when the funding period is over.
+
+A minimum DAO funding goal and funding time-period are set as parameters in the DAO code prior to deployment.
+If the minimum funding amount is not reached at the close of the funding period, all ether is returned.
 After the funding period has ended, we denote the total ether raised by $\Xi_{\text{raised}}$ and the total amount of tokens created by $T_{\text{total}}$.
-This DAO purely manages funds.
-In itself, it does not have the capabilities to build a product, write code or develop hardware.
-It requires a service provider to accomplish these and other goals, which it hires by signing off on a proposal.
-Every member of the DAO is allowed to submit proposals to spend a portion of the total ether raised, denoted by $\Xi_{\text{transfer}}$, on funding projects.
-If the proposal is approved, the ether is sent to another smart contract representing the proposed project.
+
+The DAO stores ether and transmits it based on the DAO code.
+It does not do much else.
+It cannot build a product, write code or develop hardware.
+It requires what we have called a "Service Provider'' to accomplish these and other goals.
+The DAO engages a Service Provider by accepting a Service Provider proposal.
+
+DAO token holders may also submit proposals to use the DAO's ether, denoted by $\Xi_{\text{transfer}}$, for a variety of purposes.
+If a proposal is approved, the DAO tranmits ether to a smart contract representing the proposed project.
 Such smart contracts can be parameterized and enable the DAO to interact with and influence the project being funded.
@@
 
-This means, initially a quorum of  $20\%$ of all tokens is required for any proposal to pass.
+This means, initially, a quorum of  $20\%$ of all tokens is required for any proposal to pass.
 In the event $\Xi_{\text{transfer}}$ equals the amount of ether raised during the funding period plus the rewards received, then a quorum of $53.33\%$ is required.
 
-In order to prevent proposal spam, a minimal deposit is required to be paid when creating a proposal, which gets refunded if quorum is achieved, if quorum is not achieved, the proposal deposit stays with the DAO.
+In order to prevent ``proposal spam'', a minimal deposit is required to be paid when creating a proposal, which gets refunded if quorum is achieved.
+If quorum is not achieved, the DAO keeps the proposal deposit.
 The value of the proposal deposit can be changed from the default value by the DAO through another proposal.
@@
 \section{Notation}
-Throughout this paper, $\Xi$ always represents an amount of ether in its base unit wei. Which is defined as $1 \: \text{Wei} = 10^{-18} \: \text{Ether}$ (\cite{Wood2014ethereum}).
-Similarly, DAO tokens are denoted with $T$ and always represent the amount of DAO tokens in its base unit. Which we define as $10^{-16}$ DAO token.
+Throughout this paper, $\Xi$ always represents an amount of ether in its base unit wei. This is defined as $1 \: \text{Wei} = 10^{-18} \: \text{Ether}$ (\cite{Wood2014ethereum}).
+Similarly, DAO tokens are denoted with $T$ and always represent the amount of DAO tokens in its base unit. We define this as $10^{-16}$ DAO token.
 \section{Majority robs minority attack}
-A problem every DAO has to mitigate is the ability for the majority to rob the minority.
-An attacker with $51\%$ of the tokens, acquired either during the funding period or purchased afterwards, could make a proposal to send all the funds to themselves.
+Minority owner rights can be a problem in any corporate form.
+Minority rights may be protected or addressed by provisions in corporate governance documents or by statute or judge-made law.
+But many of these solutions fail because minority owners may lack voting rights or the ability to ``vote with their feet" and easily retrieve their capital.
+We present a solution to this problem in the DAO code.
+
+A problem every that DAO has to mitigate is the ability for the majority to rob the minority by changing governance and ownership rules after DAO formation.
+For example, an attacker with $51\%$ of the tokens, acquired either during the funding period or purchased afterwards, could make a proposal to send all the funds to themselves.
 Since they would hold the majority of the tokens, they would always be able to pass their proposals.
 
-To prevent this, the minority always needs the option to retrieve their portion of the funds.
-This is done by splitting the DAO into two.
-In the case an individual, or a group of token holders, strongly disagree with a proposal and want to retrieve their portion of the funds before the proposal gets executed, they can submit a special type of proposal to form a new DAO.
+To prevent this, the minority must always have the ability to retrieve their portion of the funds.
+Our solution is to allow the DAO to split into two.
+If an individual, or a group of token holders, disagree with a proposal and want to retrieve their portion of the funds before the proposal gets executed, they can submit a special type of proposal to form a new DAO.
 The minority can then vote to move their funds to this new DAO, leaving the majority alone only able to spend their own money.
@@
 An attacker could use this to their advantage.
-Even though the minority has the chance to retrieve their funds and split the DAO, some of them could be unaware of the situation and won't do this.
-For the DAO to be considered safe, it is required that inactive token holders will not lose their funds.
+Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act.
+For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their tokens.
 Our proposed solution is implemented by limiting each individual DAO to a single service provider.
@@
 The process of choosing a new service provider is as follows:
-Any token holder can start a proposal to vote for a new service provider.
-For this proposal there is no proposal deposit to be paid, otherwise the attacker could vote for an extremely high deposit, preventing any splits.
+Any token holder can submit a proposal for a new service provider.
+In this case, no proposal deposit is required, because an attacker could vote for an extremely high deposit, preventing any splits.
 The debating period for this proposal is $10$ days.

### 2016-04-05 paper/Paper.tex
third round of WP changes

@@
 
-This price increase leads to a situation where a single contributor, who has bought tokens during the initial price, can split the DAO right after the end of the sale and would get more ether out than they put in due to other contributors paying a higher price (\cite{GriffDiscussion}).
+Price increases during the initial funding period could lead to a situation where a single contributor, having bought tokens during the initial price, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors paying a higher price (\cite{GriffDiscussion}).
 In order to avoid that possibility, all ether that is payed above the initial price of the token, will be sent to an extra account.

### 2016-04-07 tests/scenarios/deposit/run.py
Adapt the rewards test to using DAORewardAccount
- Moved the calculate_bytecode() function to utils.py and made it a bit
  more generic

- Totally changed the rewards test and made sure that it passes after
  the addition of the DAORewardaccount

@@ -1,22 +1,15 @@
+from utils import calculate_bytecode
+
 scenario_description = (
     "Make a proposal to change the default proposal deposit, vote for it and "
     "then assure that the DAO's proposal deposit did indeed change"
 )
 
 
-def calculate_bytecode(new_deposit):
-    """
-    Create the bytecode for calling dao.changeProposalDeposit() as defined
-    here:
-    https://github.com/ethereum/wiki/wiki/Ethereum-Contract-ABI#examples
-    """
-    return "{0}{1:0{2}x}".format('0xe33734fd', new_deposit, 64)
-
-
 def run(ctx):
     ctx.assert_scenario_ran('fund')
 
-    bytecode = calculate_bytecode(ctx.args.deposit_new_value)
+    bytecode = calculate_bytecode('0xe33734fd', ctx.args.deposit_new_value)
     ctx.create_js_file(substitutions={
             "dao_abi": ctx.dao_abi,
             "dao_address": ctx.dao_addr,

### 2016-04-07 paper/Paper.tex
update debating period

@@
 Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act.
-For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their tokens.
+For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their ether.
 Our proposed solution is implemented by limiting each individual DAO to a single service provider.
@@
 In this case, no proposal deposit is required, because an attacker could vote for an extremely high deposit, preventing any splits.
-The debating period for this proposal is $10$ days.
-This is $4$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through.
+The debating period for this proposal is $7$ days.
+This is $7$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through.
 There is no quorum requirement, so that every token holder has the ability to split into their own DAO.

### 2016-04-07 paper/Paper.tex
update contracts

@@
     uint lastTimeMinQuorumMet;
-    uint public rewards;
+    address public serviceProvider;
     address[] public allowedRecipients;
@@
     ManagedAccount public rewardAccount;
+    ManagedAccount public DAOrewardAccount;
     mapping (address => uint) public paidOut;
+    mapping (address => uint) public DAOpaidOut;
     mapping (address => uint) public blocked;
@@
         DAO_Creator _daoCreator,
+        uint _proposalDeposit,
         uint _minValue,
@@
     function () returns (bool success);
-    function payDAO() returns(bool);
     function receiveEther() returns(bool);
@@
     ) returns (bool _success);
+    function newContract(address _newContract);
     function addAllowedAddress(address _recipient) external returns (bool _success);
     function changeProposalDeposit(uint _proposalDeposit) external;
+    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
     function getMyReward() returns(bool _success);
@@
     uint lastTimeMinQuorumMet;
-    // The total amount of wei received as reward that has not been sent to
-    // the rewardAccount
-    uint public rewards;
+
     // Address of the service provider
@@
     // The whitelist: List of addresses the DAO is allowed to send money to
-    address[] public allowedRecipients;
+    mapping (address => bool) public allowedRecipients;
 
@@
     // The account used to manage the rewards which are to be distributed to the
-    // DAO Token Holders of any DAO that holds Reward Tokens
+    // DAO Token Holders of this DAO
     ManagedAccount public rewardAccount;
+
+    // The account used to manage the rewards which are to be distributed to
+    // any DAO that holds Reward Tokens
+    ManagedAccount public DAOrewardAccount;
+
+    // Amount of rewards (in wei) already paid out to a certain DAO
+    mapping (address => uint) public DAOpaidOut;
+
     // Amount of rewards (in wei) already paid out to a certain address
@@
         // or if `newServiceProvider` is true, the proposed service provider of
-        //the new DAO).
+        // the new DAO).
         address recipient;
@@
         SplitData[] splitData;
-        // Number of tokens in favour of the proposal
+        // Number of Tokens in favour of the proposal
         uint yea;
-        // Number of tokens opposed to the proposal
+        // Number of Tokens opposed to the proposal
         uint nay;
@@
     }
-    // Used to restrict acces to certain functions to only DAO Token Holders
+
+    // Used to restrict access to certain functions to only DAO Token Holders
     modifier onlyTokenholders {}
@@
     /// @param _daoCreator The contract able to (re)create this DAO
+    /// @param _proposalDeposit The deposit to be paid for a regular proposal
     /// @param _minValue Minimal value for a successful DAO Token Sale
@@
         //  DAO_Creator _daoCreator,
+        //  uint _proposalDeposit,
         //  uint _minValue,
@@
         //  address _privateSale
-    //  )
+    //  );
 
     /// @notice Buy Token with `msg.sender` as the beneficiary
+    /// @return Whether the purchase was successful
     function () returns (bool success);
-
-    /// @dev Function used by the products of the DAO (e.g. Slocks) to send
-    /// rewards to the DAO
-    /// @return Whether the call to this function was successful or not
-    function payDAO() returns(bool);
 
@@
     /// `_newServiceProvider` is true, then this is a proposal that splits the
-    /// DAO and sets `_recipient` as the new DAO's new service provider.
+    /// DAO and sets `_recipient` as the new DAO's service provider.
     /// @param _recipient Address of the recipient of the proposed transaction
@@
     /// ether and Reward Tokens to the new DAO. It will also burn the DAO Tokens
-    /// of the sender. 
+    /// of the sender. (TODO: document rewardTokens - done??)
     function splitDAO(
@@
     ) returns (bool _success);
+
+    /// @dev can only be called by the DAO itself through a proposal
+    /// updates the contract of the DAO by sending all funds and rewardTokens
+    /// to the new DAO. The new DAO needs to be approved by the service provider
+    /// @param _newContract the address of the new contract
+    function newContract(address _newContract);
 
@@
 
+    /// @notice Move rewards from the DAORewards managed account
+    /// @param _toMembers If true rewards are move to the actual reward account
+    ///                   for the DAO. If not then it's moved to the DAO itself
+    /// @return Whether the call was successful
+    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
+
     /// @notice Get my portion of the reward that was sent to `rewardAccount`
@@
 
-    /// @notice Withdraw `account`'s portion of the reward from `rewardAccount`,
-    /// to `account`'s balance
+    /// @notice Withdraw `_account`'s portion of the reward from `rewardAccount`
+    /// to `_account`'s balance
     /// @return Whether the call was successful
-    function withdrawRewardFor(address _account) returns(bool _success);
+    function withdrawRewardFor(address _account) internal returns (bool _success);
 
@@
         daoCreator = _daoCreator;
-        proposalDeposit = 20 ether;
+        proposalDeposit = _proposalDeposit;
         rewardAccount = new ManagedAccount(address(this));
+        DAOrewardAccount = new ManagedAccount(address(this));
+        if (address(rewardAccount) == 0)
+            throw;
+        if (address(DAOrewardAccount) == 0)
+            throw;
         lastTimeMinQuorumMet = now;
@@
         proposals.length++; // avoids a proposal with ID 0 because it is used
-        if (address(rewardAccount) == 0)
-            throw;
+
+        allowedRecipients[address(this)] = true;
+        allowedRecipients[serviceProvider] = true;
     }
@@
             return receiveEther();
-    }
-
-    function payDAO() returns (bool) {
-        rewards += msg.value;
-        return true;
     }
@@
         }
-
-        if (_recipient == address(rewardAccount) && _amount > rewards)
-            throw;
 
@@
             lastTimeMinQuorumMet = now;
-            if (p.recipient == address(rewardAccount)) {
-                // This happens when multiple similar proposals are created and
-                // both are passed at the same time.
-                if (rewards < p.amount)
-                    throw;
-                rewards -= p.amount;
-            } else {
             rewardToken[address(this)] += p.amount;
             totalRewardToken += p.amount;
-            }
         } else if (quorum >= minQuorum(p.amount) && p.nay >= p.yea) {
@@
         Transfer(msg.sender, 0, balances[msg.sender]);
+        withdrawRewardFor(msg.sender); // be nice, and get his rewards
         totalSupply -= balances[msg.sender];
@@
 
+    function newContract(address _newContract){
+        if (msg.sender != address(this) || !allowedRecipients[_newContract]) return;
+        // move all funds
+        _newContract.call.value(address(this).balance)();
+
+        //move all reward tokens
+        rewardToken[_newContract] += rewardToken[address(this)];
+        rewardToken[address(this)] = 0;
+    }
+
+    function retrieveDAOReward(bool _toMembers) external noEther returns (bool _success) {
+        DAO dao = DAO(msg.sender);
+        uint reward =
+            (rewardToken[msg.sender] * DAOrewardAccount.accumulatedInput()) /
+            totalRewardToken - DAOpaidOut[msg.sender];
+        if(_toMembers) {
+            if (!DAOrewardAccount.payOut(dao.rewardAccount(), reward))
+                throw;
+            }
+        else {
+            if (!DAOrewardAccount.payOut(dao, reward))
+                throw;
+        }
+        DAOpaidOut[msg.sender] += reward;
+        return true;
+    }
+
     function getMyReward() noEther returns (bool _success) {
@@
 
-    function withdrawRewardFor(address _account) noEther returns (bool _success) {
-        // The account's portion of Reward Tokens of this DAO
-        uint portionOfTheReward =
-            (balanceOf(_account) * rewardToken[address(this)]) /
-            totalSupply + rewardToken[_account];
+    function withdrawRewardFor(address _account) noEther internal returns (bool _success) {
         uint reward =
-            (portionOfTheReward * rewardAccount.accumulatedInput()) /
-            totalRewardToken - paidOut[_account];
+            (balanceOf(_account) * rewardAccount.accumulatedInput()) / totalSupply - paidOut[_account];
         if (!rewardAccount.payOut(_account, reward))
@@
             throw;
-        allowedRecipients.push(_recipient);
+        allowedRecipients[_recipient] = true;
         return true;
@@
     function isRecipientAllowed(address _recipient) internal returns (bool _isAllowed) {
-        if (_recipient == serviceProvider
-            || _recipient == address(rewardAccount)
-            || _recipient == address(this)
+        if (allowedRecipients[_recipient]
             || (_recipient == address(extraBalance)
@@
             return true;
-
-        for (uint i = 0; i < allowedRecipients.length; ++i) {
-            if (_recipient == allowedRecipients[i])
-                return true;
-        }
+        else
             return false;
@@
 
-    function minQuorum(uint _value) internal returns (uint _minQuorum) {
+    function minQuorum(uint _value) internal constant returns (uint _minQuorum) {
         // minimum of 20% and maximum of 53.33%
-        return totalSupply / minQuorumDivisor + _value / 3;
+        return totalSupply / minQuorumDivisor +
+            (_value * totalSupply) / (3 * (this.balance + totalRewardToken));
     }
@@
         NewServiceProvider(_newServiceProvider);
-        return daoCreator.createDAO(_newServiceProvider, 0, now + 42 days);
+        return daoCreator.createDAO(_newServiceProvider, 0, 0, now + 42 days);
     }
@@
         address _defaultServiceProvider,
+        uint _proposalDeposit,
         uint _minValue,
@@
             DAO_Creator(this),
+            _proposalDeposit,
             _minValue,
@@
     function setRewardDivisor(uint _rewardDivisor) callingRestriction {
-        if (_rewardDivisor < 50 && msg.sender != address(client))
+        if (_rewardDivisor < 50)
             throw; // 2% is the default max reward
@@
     function setDeploymentFee(uint _deploymentReward) callingRestriction {
-        if (deploymentReward > 10 ether && msg.sender != address(client))
-            throw; 
+        if (deploymentReward > 10 ether)
+            throw; // TODO, set a max defined by service provider, or ideally oracle (set in euro)
         deploymentReward = _deploymentReward;
@@
         if (promiseValid) {
-            if (client.payDAO.value(msg.value)()) {
+            if (client.DAOrewardAccount().call.value(msg.value)()) {
                 return true;

### 2016-04-07 paper/Paper.tex
update contracts

@@
         rewardToken[address(this)] = 0;
+        DAOpaidOut[_newContract] += DAOpaidOut[address(this)];
+        DAOpaidOut[address(this)] = 0;
     }

### 2016-04-07 deploy/deploy.js
Adjust tests after proposal deposit as argument

@@ -22,6 +22,7 @@ var _daoCreatorContract = creatorContract.new(
             var dao = daoContract.new(
 	            service_provider,
 	            contract.address,
+                default_proposal_deposit,
 	            web3.toWei(min_value, "ether"),
                 closing_time,
                 0,

### 2016-04-07 deploy/prepare.py

@@ -74,6 +74,12 @@ if __name__ == "__main__":
         default="0x08144824954c65b12f68b75072488e634ac4e67a",  # Griff testnet
         help='Account to set as service provider'
     )
+    p.add_argument(
+        '--default-proposal-deposit',
+        type=int,
+        default=10,
+        help='The default proposal deposit for every proposal of the DAO'
+    )
     args = p.parse_args()
     ctx = TestDeployContext(args)
     comp = ctx.compile_contract("DAO.sol")
@@ -91,5 +97,8 @@ if __name__ == "__main__":
           args.sale_duration_mins * 60)
         )
         f.write("service_provider = \"{}\";\n".format(args.service_provider))
+        f.write("default_proposal_deposit = {};\n".format(
+            args.default_proposal_deposit)
+        )
 
     ctx.cleanup()

### 2016-04-07 tests/scenarios/deploy/template.js

@@ -14,10 +14,11 @@ var _daoCreatorContract = creatorContract.new(
         addToTest('dao_creator_address', contract.address);
         checkWork();
         var dao = daoContract.new(
-	    _defaultServiceProvider,
-	    contract.address,
-	    web3.toWei($min_value, "ether"),
-	    $closing_time,
+	        _defaultServiceProvider,
+	        contract.address,
+            $default_proposal_deposit,
+	        web3.toWei($min_value, "ether"),
+	        $closing_time,
             0,
 		    {
 		        from: web3.eth.accounts[0],

### 2016-04-07 deploy/deploy.js
prepare scripts: default proposal is in ether

@@ -22,7 +22,7 @@ var _daoCreatorContract = creatorContract.new(
             var dao = daoContract.new(
 	            service_provider,
 	            contract.address,
-                default_proposal_deposit,
+                web3.toWei(default_proposal_deposit, "ether"),
 	            web3.toWei(min_value, "ether"),
                 closing_time,
                 0,

### 2016-04-07 deploy/prepare.py

@@ -78,7 +78,7 @@ if __name__ == "__main__":
         '--default-proposal-deposit',
         type=int,
         default=10,
-        help='The default proposal deposit for every proposal of the DAO'
+        help='The proposal deposit (in ether) for every proposal of the DAO'
     )
     args = p.parse_args()
     ctx = TestDeployContext(args)

### 2016-04-08 paper/Paper.tex
style

@@
 On the other hand, small investors remain vulnerable to financial mismanagement or outright fraud.
-Because they have small stakes in a venture, they may lack power to identify problems, participate in governance decisions, or to easily recover their investment.
-(\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}).
+Because they have small stakes in a venture, they may lack power to identify problems, participate in governance decisions, or to easily recover their investment (\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}).
 At the same time, corporate leadership and managment may be accused of malfeasance or mismanagement when they believe that they have acted in good faith, based on their understanding of their obligations and interpretation of applicable rules.
@@
 We present a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality.
-We illustrate a method that for the first time allows the creation of organizations in which (1) ?participants?
-maintain direct real-time control of contributed funds and (2) where governance rules are formalized and automated using software.
+We illustrate a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2) where governance rules are formalized and automated using software.
 Specifically, we have written generic smart contract code (\cite{szabo1997formalizing, miller1997future}) that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain.
@@
 
-\section{Dao Concept | Dao Practice}
+\section{Dao Concept}
 
@@
 Once deployed, the DAO code requires ``ether'' to engage in transactions on Ethereum.
-(Ether is the digital fuel that powers the Ethereum network).
+Ether is the digital fuel that powers the Ethereum network.
 Without ether, a DAO can not do very much and a DAO's first order of business is to receive ether.
@@
 It cannot build a product, write code or develop hardware.
-It requires what we have called a "Service Provider'' to accomplish these and other goals.
+It requires what we have called a ``Service Provider'' to accomplish these and other goals.
 The DAO engages a Service Provider by accepting a Service Provider proposal.
@@
 
-The integer \verb|rewards| counts all the rewards which have been sent to the DAO. It gets set to zero when paid out to the \verb|rewardAccount|.
-
 The address \verb|serviceProvider| is set at the creation of the DAO and defines the service provider.
@@
 The variable \verb|rewardAccount| is of the type \verb|ManagedAccount| , which will be discussed in \ref{app:ManagedAccount}.
-It is used to manage the rewards which are to be distributed to the DAO Token Holders and reward token holders.
+It is used to manage the rewards which are to be distributed to the DAO Token Holders.
+
+Similar, \verb|DAOrewardAccount| is also of the type \verb|ManagedAccount|.
+This account is used to receive all rewards from projects funded by the DAO.
+It will then redistribute them amongst all splitted DAOs as well as itself using \verb|retrieveDAOReward|.
 
 The map \verb|paidOut| is used to keep track how much wei a single token holder has already retrieved from \verb|rewardAccount|.
+
+Similar, the map \verb|DAOpaidOut| is used to keep track how much a single DAO has already received from \verb|DAOrewardAccount|.
 
@@
 After which this function is repurposed to receive ether as simple deposit to the DAO using the function \verb|receiveEther|.
-
-\subsubsection*{payDAO}
-This function is used to receive and track the rewards generated by the products funded by the DAO and returns true when ether has been added to \verb|rewards|.
-In the context of Slock.it, these will be the rewards generated when Slocks are deployed or used.
 
@@
 
+\subsubsection*{newContract}
+This function can only be called by the DAO itself (through a proposal and a vote) and is used to move all remaining ether, as well as all rewardTokens to a new address.
+This is used to update the contract.
+The new address needs to be approved by the service provider.
+
 \subsubsection*{transfer and transferFrom}
@@
 The reward tokens are further elaborated in section \ref{split}.
+
+\subsubsection*{retrieveDAOReward}
+This function, when called by a DAO, sends the rewards which belong to this DAO from \verb|DAOrewardAccount| to either the DAO itself, or to the \verb|rewardAccount| of the respective DAO in order to be distributed among its token holders, depending on the parameter \verb|_toMembers|.
+
 \subsubsection*{addAllowedAddress}
@@
 
-Reward tokens are used to divide the ether sent to \verb|rewardAccount| amongst the various DAOs that own reward tokens.
-Reward tokens are only transferred in the event of a DAO split, they can never be owned by anything other than the original DAO or a “fork” of the original DAO that generated the reward tokens.
-
-Reward tokens are generated when the DAO makes any transaction spending ether (with the exception of sending ether to the \verb|rewardAccount|).
-When the DAO’s products send ether back to the DAO (for example when a Slock sends $1\%$ of a transaction to the DAO), the ether is held with the rest of the ether that the DAO has, but \verb|rewards| counts all the ether which has been received as rewards.
+Reward tokens are used to divide the ether sent to \verb|DAOrewardAccount| amongst the various DAOs that own reward tokens.
+Reward tokens are only transferred in the event of a DAO split or an update of the contract, they can never be owned by anything other than the original DAO or a “fork” of the original DAO that generated the reward tokens.
+
+Reward tokens are generated when the DAO makes any transaction spending ether.
+When the DAO’s products send ether back to the DAO (for example when a Slock sends $1\%$ of a transaction to the DAO), the ether is held within \verb|DAOrewardAccount|.
 The DAO can use these rewards to fund new proposals or to equally distribute the rewards to the reward token holders (using a proposal which gets voted on by the DAO token holders).
-Then the token holders of the DAOs that hold reward tokens will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token.
-To do this the DAO will send the accumulated rewards to the \verb|rewardAccount| which is held in the \verb|ManagedAccount| contract.
-Then and only then will the token holders of the DAOs that hold reward tokens be able to call the \verb|getMyReward| function and receive their ether.
-These payouts are tracked by the map \verb|paidOut| which keeps track of which DAOs hold reward tokens and whether they have claimed their portion of the rewards, and which of the original DAO token holders have claimed their fair portion of the rewards.This process guarantees that any DAO token holder whose ether was spent building a product will receive the rewards promised to them from that product even if they decide to split from the DAO.
+
+Then the token holders of the DAOs will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token.
+To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount|b(a \verb|ManagedAccount| contract].
+Then and only then will the token holders of the DAOs be able to call the \verb|getMyReward| function and receive their ether.
+
+These payouts are tracked by the map \verb|paidOut| which keeps track of which token holders have claimed their fair portion of the rewards.
+This process guarantees that any DAO token holder whose ether was spent building a product will receive the rewards promised to them from that product even if they decide to split from the DAO.
 
@@
 Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
-But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to send all the ether in the old DAO to this contract.
+But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the
 If accepted, the complete DAO moves to the new contract.
@@
     /// ether and Reward Tokens to the new DAO. It will also burn the DAO Tokens
-    /// of the sender. (TODO: document rewardTokens - done??)
+    /// of the sender.
     function splitDAO(

### 2016-04-11 paper/Paper.tex

@@
 Without ether, a DAO can not do very much and a DAO's first order of business is to receive ether.
-After the DAO code is deployed, ether may be sent to the DAO?s smart contract address during an initial funding period which is defined in the DAO code.
+After the DAO code is deployed, ether may be sent to the DAO's smart contract address during an initial funding period which is defined in the DAO code.
 
@@
 DAO token holders may also submit proposals to use the DAO's ether, denoted by $\Xi_{\text{transfer}}$, for a variety of purposes.
-If a proposal is approved, the DAO tranmits ether to a smart contract representing the proposed project.
+If a proposal is approved, the DAO transmits ether to a smart contract representing the proposed project.
 Such smart contracts can be parameterized and enable the DAO to interact with and influence the project being funded.
@@
 
-A problem every that DAO has to mitigate is the ability for the majority to rob the minority by changing governance and ownership rules after DAO formation.
+A problem every DAO has to mitigate is the ability for the majority to rob the minority by changing governance and ownership rules after DAO formation.
 For example, an attacker with $51\%$ of the tokens, acquired either during the funding period or purchased afterwards, could make a proposal to send all the funds to themselves.
@@
 This results in a constant price in the beginning, until $2$ weeks before the end of the token sale.
-At this time the price increased daily by $0.005 \: \Xi_c$ per base unit of DAO token.
+At this time the price increased daily by $0.0005 \: \Xi_c$ per base unit of DAO token.
 Until $4$ days before the closing time when there will be a constant price of $0.015 \: \Xi_c$ per base unit of DAO token.
@@
 The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent.
-The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time as described in section \ref{TokenPrice}.
+The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $P(t) \cdot 200$ , as described in section \ref{TokenPrice}.
 

### 2016-04-13 paper/Paper.tex
update contract interfaces

@@
 \begin{equation}
- q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{total}})}
+ q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{DAO}})}
  \label{minQuorum}
@@
 Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
-$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward tokens ever generated as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}).
-The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received or said another way, the total amount of ether the DAO has ever received.
+$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{DAO}}$ is the amount of reward tokens owned by this DAO, as explained in section \ref{RewardToken} (also see \verb|rewardToken| in \ref{app:DAO}).
+The sum $\Xi_{DAO} + R_{\text{DAO}}$ is equal to the amount of ether raised plus the rewards received or said another way, the total amount of ether the DAO has ever received.
 
@@
     uint public minValue;  
-    bool public isFunded;   
+    bool public isFueled;
     address public privateSale;
@@
 
-The boolean \verb|isFunded| is true if DAO has reached its minimum funding goal, false otherwise.
+The boolean \verb|isFueled| is true if DAO has reached its minimum fueling goal, false otherwise.
 
@@
     uint lastTimeMinQuorumMet;
-    address public serviceProvider;
+    address public curator;
     address[] public allowedRecipients;
@@
     uint public proposalDeposit;
+    uint sumOfProposalDeposits;
     DAO_Creator public daoCreator;
@@
         uint proposalDeposit;
-        bool newServiceProvider;
+        bool newCurator;
         SplitData[] splitData;
@@
     function DAO(
-        address _defaultServiceProvider,
+        address _curator,
         DAO_Creator _daoCreator,
@@
         uint _debatingPeriod,
-        bool _newServiceProvider
+        bool __newCurator
     ) onlyTokenholders returns (uint _proposalID);
@@
     ) returns (bool _success);
+    function emergenyCloseProposal(uint _proposalID) external;
     function splitDAO(
@@
     function newContract(address _newContract);
-    function addAllowedAddress(address _recipient) external returns (bool _success);
+    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
     function changeProposalDeposit(uint _proposalDeposit) external;
@@
     function numberOfProposals() constant returns (uint _numberOfProposals);
+    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
     function isBlocked(address _account) returns (bool);
@@
 
-The address \verb|serviceProvider| is set at the creation of the DAO and defines the service provider.
-
-The list \verb|allowedRecipients| is commonly referred to as ‘’the whitelist.’’ The DAO can only send transactions to itself, the \verb|serviceProvider|, \verb|rewardAccount|, \verb|extraBalance| and addresses in the whitelist.
-Only the \verb|serviceProvider| can add addresses to the whitelist.
+The address \verb|curator| is set at the creation of the DAO and defines the curator.
+
+The list \verb|allowedRecipients| is commonly referred to as ‘’the whitelist.’’ The DAO can only send transactions to itself, the \verb|curator|, \verb|extraBalance| and addresses in the whitelist.
+Only the \verb|curator| can add addresses to the whitelist.
 
@@
 This account is used to receive all rewards from projects funded by the DAO.
-It will then redistribute them amongst all splitted DAOs as well as itself using \verb|retrieveDAOReward|.
+It will then redistribute them amongst all splitted DAOs as well as itself using the function \verb|retrieveDAOReward|.
 
@@
 
-The map \verb|blocked| stores the addresses of the DAO Tokens that have voted and therefore are not allowed to be transferred until the vote has concluded.. The address points to the proposal ID.
+The map \verb|blocked| stores the addresses of the DAO Tokens that have voted and therefore are not allowed to be transferred until the vote has concluded. The address points to the proposal ID.
 
 The integer \verb|proposalDeposit| specifies the minimum deposit to be paid in wei for any proposal that does not include a change in service providers.
+
+The integer \verb|sumOfProposalDeposits| is the sum of all proposal deposits of open proposals.
 
@@
  \item[proposalHash] A hash to check validity of a proposal. Equal to \verb|sha3(_recipient, _amount, _transactionData)|.
- \item[proposalDeposit] The minimum deposit (in wei) the creator of a proposal is required to send to submit a proposal.
+ \item[proposalDeposit] The deposit (in wei) the creator of a proposal has send to submit a proposal.
 It is taken from the \verb|msg.value| of a \verb|newProposal| call; its purpose is to prevent spam.
-It is set to $20$ ether by default but the creator of the proposal can send any amount above this for the deposit.For Slock.it’s purposes, the proposals will be sorted by the proposal deposit in the GUI, so in the case that a proposal is considered important, the creator of the proposal can deposit extra ether to “advertise” their proposal.
+Its minimal value is set when the contract is deploayed as constructor parameter.
+But the creator of the proposal can send any amount above this for the deposit.
+The proposals will be sorted by the proposal deposit in the GUI, so in the case that a proposal is considered important, the creator of the proposal can deposit extra ether to “advertise” their proposal.
 The creator of the proposal will be refunded the entire deposit if quorum is reached, if it is not reached the deposit remains with the DAO.
@@
 \begin{itemize}
- \item \verb|serviceProvider|
+ \item \verb|curator|
  \item \verb|daoCreator|
@@
  \item \verb|rewardAccount|
+ \item \verb|DAOrewardAccount|
  \item \verb|minValue|
@@
  \item \verb|privateSale|
+ \item \verb|lastTimeMinQuorumMet|
+ \item \verb|minQuorumDivisor|
+ \item \verb|allowedRecipients|
 \end{itemize}
@@
  \item[transactionData] The data of the proposed transaction.
- \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 10 days for a new service provider proposal.
+ \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 1 week for a new service provider proposal.
  \item[newServiceProvider] A boolean defining whether this proposal is for a new service provider or not.
@@
 If both requirements are met, it records the vote in the storage of the contract.
-The tokens used to vote will be blocked, meaning they can not be transferred until the proposal is closed.This is to avoid voting several times with different sender addresses.
+The tokens used to vote will be blocked, meaning they can not be transferred until the proposal is closed.
+This is to avoid voting several times with different sender addresses.
 
@@
 
+\subsubsection*{emergenyCloseProposal}
+This is used in the case `executeProposal` fails because it throws (e.g.
+when returuning the deposit, because the fallback function of this address throws, or when executing the proposed transaction).
+It can be called $5$ days after the voting deadline of the proposal passed.
+It will close the proposal.
 \subsubsection*{splitDAO}
@@
 Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split.
-These tokens allow the new DAO to retrieve their portion of the reward using the \verb|getMyReward| function of the original DAO.
+These tokens allow the new DAO to retrieve their portion of the reward using the \verb|retrieveDAOReward| function of the original DAO.
 At the end of this process all original DAO tokens of the sender account are destroyed.
+It is important to notice that in all integer division descirbed above, ther may be remainders which stay with the DAO.
 
@@
 This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
-Their portion of the reward tokens $S$ is calculated as follows:
-\begin{equation}
- S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
-\end{equation}
-Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender.
-$R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
 The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
 \begin{equation}
-\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut[sender]}}
+\Xi_{\text{reward}} = T_{\text{sender}} \cdot \Xi_{\text{rewardAccount}} / T_{\text{total}} - \Xi_{\text{paidOut[sender]}}
 \end{equation}
-Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function.
+Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount| and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function.
 The reward tokens are further elaborated in section \ref{split}.
@@
 
-\subsubsection*{addAllowedAddress}
-This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.
+\subsubsection*{changeAllowedRecipients}
+This function can add/remove an address to/from the whitelist, \verb|allowedRecipients|. It can only be executed by the curator.
 
@@
 Returns the total number of proposals ever created.
+
+\subsubsection*{getNewDAOAdress}
+This is just a helper function to read the address of a newly created `split DAO`. It gets the proposal ID which was used for the split as input parameter and return the address of the new DAO.
 
@@
 Reward tokens are generated when the DAO makes any transaction spending ether.
-When the DAO’s products send ether back to the DAO (for example when a Slock sends $1\%$ of a transaction to the DAO), the ether is held within \verb|DAOrewardAccount|.
-The DAO can use these rewards to fund new proposals or to equally distribute the rewards to the reward token holders (using a proposal which gets voted on by the DAO token holders).
+When the DAO’s products send ether back to the DAO, the ether is held within \verb|DAOrewardAccount|.
+The DAO can use these rewards to fund new proposals or to fairly distribute the rewards to the reward token holders (using a proposal which gets voted on by the DAO token holders).
 
 Then the token holders of the DAOs will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token.
-To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount|b(a \verb|ManagedAccount| contract].
+To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount| (a \verb|ManagedAccount| contract).
 Then and only then will the token holders of the DAOs be able to call the \verb|getMyReward| function and receive their ether.
@@
 Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
-But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the
-If accepted, the complete DAO moves to the new contract.
+But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the address of the new contract as parameter.
+If accepted, the complete DAO moves to the new contract, meaining, all ether and reward tokens are transferred to the new contract.
 In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens.
 In the new contract this right should only be usable in restricted functions which are only callable by the owner of the tokens.
+Another option is to create new tokens in the new contract based on the token distribution in the old contract.
+This can also be achieved by a proof that the old tokens are destroyed (sending to the $0$ address).
 This process allows for the DAO to maintain static immutable code on the Ethereum blockchain, while still being able to be updated if the need arises.
@@
     // Address of the service provider
-    address public serviceProvider;
+    address public curator;
     // The whitelist: List of addresses the DAO is allowed to send money to
@@
 
-        serviceProvider = _defaultServiceProvider;
+        curator = _defaultServiceProvider;
         daoCreator = _daoCreator;
@@
         allowedRecipients[address(this)] = true;
-        allowedRecipients[serviceProvider] = true;
+        allowedRecipients[curator] = true;
     }
@@
             || _transactionData.length != 0
-            || _recipient == serviceProvider
+            || _recipient == curator
             || msg.value > 0
@@
     function addAllowedAddress(address _recipient) noEther external returns (bool _success) {
-        if (msg.sender != serviceProvider)
+        if (msg.sender != curator)
             throw;
@@
 
-    address serviceProvider;
+    address curator;
     bytes32 hashOfTheContract;
@@
                 throw;
-        } else if (msg.sender != serviceProvider) {
+        } else if (msg.sender != curator) {
                 throw;
@@
     function SampleOffer(
-        address _serviceProvider,
+        address _curator,
         bytes32 _hashOfTheContract,
@@
     ) {
-        serviceProvider = _serviceProvider;
+        curator = _curator;
         hashOfTheContract = _hashOfTheContract;
@@
             throw;
-        if (!serviceProvider.send(oneTimeCosts))
+        if (!curator.send(oneTimeCosts))
             throw;
@@
     function getDailyPayment() {
-        if (msg.sender != serviceProvider)
+        if (msg.sender != curator)
             throw;
         uint amount = (now - dateOfSignature) / (1 days) * dailyCosts - paidOut;
-        if (serviceProvider.send(amount))
+        if (curator.send(amount))
             paidOut += amount;
@@
         } else {
-            if (serviceProvider.send(msg.value)) {
+            if (curator.send(msg.value)) {
                 return true;

### 2016-04-13 paper/Paper.tex
replace service provider with Curator and update contracts

@@
 
-A minimum DAO funding goal and funding time-period are set as parameters in the DAO code prior to deployment.
+A minimum DAO funding goal and funding time-period are set as parameters in the DAO code during to deployment.
 If the minimum funding amount is not reached at the close of the funding period, all ether is returned.
@@
 A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely.
-An attacker could use this to their advantage.
-Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act.
+An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act.
 For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their ether.
-Our proposed solution is implemented by limiting each individual DAO to a single service provider.
-This service provider controls the only account that can receive ether from the DAO, across all proposals.
-In addition, the service provider can build a “whitelist” of addresses that the DAO is allowed to send funds to.
-This gives the service provider of the DAO considerable power.
-To prevent the abuse of this power, it is possible for the DAO to vote for a new service provider, which may result in a split of the DAO as described above.
-
-Any token holder can make a proposal to vote for a new service provider.
+Our proposed solution is implemented by limiting each individual DAO to a single curator.
+This curator controls the list of addresses that can receive ether from the DAO, across all proposals.
+This gives the curator of the DAO considerable power.
+To prevent the abuse of this power, it is possible for the DAO to vote for a new curator, which may result in a split of the DAO as described above.
+
+Any token holder can make a proposal to vote for a new curator.
 In effect, even a single token holder is able to both retrieve their remaining portion of ether and maintain their right to any future rewards associated to their previous contribution, as these will be sent to the new DAO automatically.
@@
 
-The process of choosing a new service provider is as follows:
-Any token holder can submit a proposal for a new service provider.
+The process of choosing a new curator is as follows:
+Any token holder can submit a proposal for a new curator.
 In this case, no proposal deposit is required, because an attacker could vote for an extremely high deposit, preventing any splits.
@@
 There is no quorum requirement, so that every token holder has the ability to split into their own DAO.
-The debating period is used to discuss (on or off-chain) the new service provider and conduct a first vote that's non-binding.
+The debating period is used to discuss (on or off-chain) the new curator and conduct a first vote that's non-binding.
 After this first vote, token holders can cast a second one to confirm its results.
-In the case a majority opts to  keep the original service provider, the minority can either change their vote to keep the original service provider in order to avoid a split, or inversely they can confirm their vote for a new service provider and move their portion of the funds to a new DAO.
+In the case a majority opts to  keep the original curator, the minority can either change their vote to keep the original curator in order to avoid a split, or inversely they can confirm their vote for a new curator and move their portion of the funds to a new DAO.
 
@@
  P(t) = \begin{cases}
-0.01 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
-0.01 + 0.0005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
-0.015 & \text{otherwise}
+1 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
+1 + 0.05 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
+1.5 & \text{otherwise}
 \end{cases}
@@
 This results in a constant price in the beginning, until $2$ weeks before the end of the token sale.
-At this time the price increased daily by $0.0005 \: \Xi_c$ per base unit of DAO token.
-Until $4$ days before the closing time when there will be a constant price of $0.015 \: \Xi_c$ per base unit of DAO token.
+At this time the price increased daily by $0.05 \: \Xi_c$ per base unit of DAO token.
+Until $4$ days before the closing time when there will be a constant price of $1.5 \: \Xi_c$ per base unit of DAO token.
 
@@
 In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
-The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from the service provider to the DAO could look like.
+The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from a contractor to the DAO could look like.
 \end{multicols}
@@
 The constructor \verb|TokenSale| initiates the token sale with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateSale|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed.
-
-The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent.
-The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $P(t) \cdot 200$ , as described in section \ref{TokenPrice}.
-
+In order to interact with the contract the following functions can be used:
+
+\subsubsection*{buyTokenProxy}
+This function creates one unit of the DAO token’s minimum denomination for every wei sent.
+The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $20 / P(t)$ , as described in section \ref{TokenPrice}.
 The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.
 
-The function \verb|refund| can be called by any contributor to recieve their wei back if the token sale failed to meet its funding goal.
-
-The function \verb|divisor| is used to calculate the price of the token during the sale in the function \verb|buyTokenProxy|.
+\subsubsection*{refund}
+This function can be called by any contributor to recieve their wei back if the token sale failed to meet its funding goal.
+
+\subsubsection*{divisor}
+This function is used to calculate the price of the token during the sale in the function \verb|buyTokenProxy|.
 
@@
 \begin{multicols}{2}
-The original contract used as a starting point for ‘’DAO’’ was: \url{http://chriseth.github.io/browser-solidity/?gist=192371538cf5e43e6dab} as described in 
+The original contract used as a starting point for the ‘’DAO’’ was: \url{http://chriseth.github.io/browser-solidity/?gist=192371538cf5e43e6dab} as described in 
 \url{https://blog.ethereum.org/2015/12/04}. The main feature added is the splitting mechanism and all that comes with it.
@@
 The list \verb|allowedRecipients| is commonly referred to as ‘’the whitelist.’’ The DAO can only send transactions to itself, the \verb|curator|, \verb|extraBalance| and addresses in the whitelist.
-Only the \verb|curator| can add addresses to the whitelist.
+Only the \verb|curator| can add/remove addresses to/from the whitelist.
 
@@
 
-The integer \verb|proposalDeposit| specifies the minimum deposit to be paid in wei for any proposal that does not include a change in service providers.
+The integer \verb|proposalDeposit| specifies the minimum deposit to be paid in wei for any proposal that does not include a change of the curator.
 
@@
 It is taken from the \verb|msg.value| of a \verb|newProposal| call; its purpose is to prevent spam.
-Its minimal value is set when the contract is deploayed as constructor parameter.
+Its minimal value is set when the contract is deployed as constructor parameter.
 But the creator of the proposal can send any amount above this for the deposit.
@@
 The creator of the proposal will be refunded the entire deposit if quorum is reached, if it is not reached the deposit remains with the DAO.
- \item[newServiceProvider] A boolean which is true if this proposal assigns a new service provider.
- \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new service provider.
+ \item[newCurator] A boolean which is true if this proposal assigns a new curator.
+ \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new curator.
  \item[yea] Number of tokens in favor of the proposal.
- \item[nay] Number of tokens in opposed to the proposal.
+ \item[nay] Number of tokens opposed to the proposal.
  \item[votedYes] Simple mapping to check if a token holder has voted for it.
@@
 \begin{description}
- \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current service provider or an address on the whitelist \verb|allowedRecipients|).
+ \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current curator or an address on the whitelist \verb|allowedRecipients|).
  \item[amount] The amount of wei to be sent in the proposed transaction.
@@
  \item[transactionData] The data of the proposed transaction.
- \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 1 week for a new service provider proposal.
- \item[newServiceProvider] A boolean defining whether this proposal is for a new service provider or not.
+ \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 1 week for a new curator proposal.
+ \item[newCurator] A boolean defining whether this proposal is for a new curator or not.
 \end{description}
@@
 This function can be called by anyone.
-It counts the votes, in order to check whether the quorum is met, and executes the proposal if it passed, unless it is a proposal for a new service provider, than it does nothing.
+It counts the votes, in order to check whether the quorum is met, and executes the proposal if it passed, unless it is a proposal for a new curator, than it does nothing.
 The arguments of the function are:
@@
 \subsubsection*{splitDAO}
-After a new service provider has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new service provider.
+After a new curator has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new curator.
 This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
@@
  \item[proposalID] The proposal ID.
- \item[newServiceProvider] The address of the new service provider of the new DAO.
+ \item[newCurator] The address of the new curator of the new DAO.
 \end{description}
@@
 At the end of this process all original DAO tokens of the sender account are destroyed.
-It is important to notice that in all integer division descirbed above, ther may be remainders which stay with the DAO.
+It is important to notice that in all integer division descirbed above, there may be remainders which stay with the DAO.
 
@@
 This is used to update the contract.
-The new address needs to be approved by the service provider.
+The new address needs to be approved by the curator.
 
@@
 \subsubsection*{transferPaidOut}
-This function is called to when making any transfer of DAO tokens using \verb|transfer| or \verb|transferFrom| and it updates the array \verb|paidOut| to track the amount of rewards which has been paid out already, $P$, and is calculated as follows:
+This function is called when making any transfer of DAO tokens using \verb|transfer| or \verb|transferFrom| and it updates the array \verb|paidOut| to track the amount of rewards which has been paid out already, $P$, and is calculated as follows:
 \begin{equation}
@@
 \subsubsection*{withdrawRewardFor}
-This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
+This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to the address given as a parameter.
 The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
@@
 \end{equation}
-Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount| and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function.
+Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount| and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder address, which is given as a parameter.
 The reward tokens are further elaborated in section \ref{split}.
@@
 \subsubsection*{getNewDAOAdress}
-This is just a helper function to read the address of a newly created `split DAO`. It gets the proposal ID which was used for the split as input parameter and return the address of the new DAO.
+This is just a helper function to read the address of a newly created `split DAO`. It gets the proposal ID which was used for the split as input parameter and returns the address of the new DAO.
 
@@
 This function returns true when the address given as parameter is currently blocked to transfer tokens due to an ongoing vote it has participated in, otherwise it returns false.
+It also unblocks the tokens in the case the voting deadline of the proposal is over.
 
@@
 Then the token holders of the DAOs will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token.
-To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount| (a \verb|ManagedAccount| contract).
+To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount| (a \verb|ManagedAccount| contract) and keeps track of the payouts in \verb|DAOpaidOut|.
 Then and only then will the token holders of the DAOs be able to call the \verb|getMyReward| function and receive their ether.
@@
 
-Let’s assume that during the split, a fraction of DAO tokens, $X$, changes service providers and leaves the DAO.
+Let’s assume that during the split, a fraction of DAO tokens, $X$, changes the curator and leaves the DAO.
 The new DAO created receives $X \cdot \Xi_{\text{DAO pre}}$, a portion of the remaining ether from the original DAO.
@@
 
-The original DAO tokens of the accounts that confirmed the new service provider are destroyed.
+The original DAO tokens of the accounts that confirmed the new curator are destroyed.
 Hence:
@@
     uint public closingTime;
-    // Minimum funding goal of the token sale, denominated in tokens
+    // Minimum fueling goal of the token sale, denominated in ether
     uint public minValue;
-    // True if the DAO reached its minimum funding goal, false otherwise
-    bool public isFunded;   
+    // True if the DAO reached its minimum fueling goal, false otherwise
+    bool public isFueled;
     // For DAO splits - if privateSale is 0, then it is a public sale, otherwise
@@
     // hold extra ether which has been paid after the DAO token price has increased
-    ManagedAccount extraBalance;
+    ManagedAccount public extraBalance;
     // tracks the amount of wei given from each contributor (used for refund)
@@
 
-    /// @dev Constructor setting the minimum funding goal and the 
+    /// @dev Constructor setting the minimum fueling goal and the
     /// end of the Token Sale
-    /// @param _minValue Token Sale minimum funding goal
+    /// @param _minValue Token Sale minimum fueling goal
     /// @param _closingTime Date (in Unix time) of the end of the Token Sale
+    /// @param _privateSale Zero means that the sale is public.  A non-zero
+    /// address represents the only address that can buy Tokens (the address
+    /// can also buy Tokens on behalf of other accounts)
     // This is the constructor: it can not be overloaded so it is commented out
-    //  function TokenSale(uint _minValue, uint _closingTime);
+    //  function TokenSale(
+        //  uint _minValue,
+        //  uint _closingTime,
+        //  address _privateSale
+    //  );
 
@@
     /// @param _tokenHolder The address of the Tokens's recipient
+    /// @return Whether the purchase was successful
     function buyTokenProxy(address _tokenHolder) returns (bool success);
@@
     /// @notice Refund `msg.sender` in the case the Token Sale didn't reach its
-    /// minimum funding goal
+    /// minimum fueling goal
     function refund();
 
-    /// @return the divisor used to calculate the token price during the sale
+    /// @return The divisor used to calculate the token price during the sale
     function divisor() returns (uint divisor);
@@
             && (privateSale == 0 || privateSale == msg.sender)) {
+
             uint token = (msg.value * 20) / divisor();
@@
             totalSupply += token;
-            weiGiven[msg.sender] += msg.value;
+            weiGiven[_tokenHolder] += msg.value;
             SoldToken(_tokenHolder, token);
-            if (totalSupply >= minValue && !isFunded) {
-                isFunded = true;
+            if (totalSupply >= minValue && !isFueled) {
+                isFueled = true;
                 FundingToDate(totalSupply);
@@
     function refund() noEther {
-        if (now > closingTime && !isFunded) {
-            // get extraBalance - will only succeed when called for the first time
+        if (now > closingTime && !isFueled) {
+            // Get extraBalance - will only succeed when called for the first time
             extraBalance.payOut(address(this), extraBalance.accumulatedInput());
 
-            // execute refund
+            // Execute refund
             if (msg.sender.call.value(weiGiven[msg.sender])()) {
@@
 
-    function divisor() returns (uint divisor){
-        // the number of (base unit) tokens per wei is calculated
+    function divisor() returns (uint divisor) {
+        // The number of (base unit) tokens per wei is calculated
         // as `msg.value` * 20 / `divisor`
-        // the funding period starts with a 1:1 ratio
-        if (closingTime - 2 weeks > now) return 20;
-        // followed by 10 days with a daily price increase of 5%
-        else if (closingTime - 4 days > now)
+        // The fueling period starts with a 1:1 ratio
+        if (closingTime - 2 weeks > now) {
+            return 20;
+        // Followed by 10 days with a daily price increase of 5%
+        } else if (closingTime - 4 days > now) {
             return (20 + (now - (closingTime - 2 weeks)) / (1 days));
-        // the last 4 days there is a constant price ratio of 1:1,5
-        else return 30;
+        // The last 4 days there is a constant price ratio of 1:1.5
+        } else {
+            return 30;
+        }
     }
@@
 
-    // Proposals to spend the DAO's ether or to choose a new service provider
+    // The amount of days for which people who try to participate in the sale
+    // by calling the fallback function will still get their money back
+    uint constant saleGracePeriod = 40 days;
+    // The minimum debate period that a generic proposal can have
+    uint constant minProposalDebatePeriod = 2 weeks;
+    // The minimum debate period that a split proposal can have
+    uint constant minSplitDebatePeriod = 1 weeks;
+    // Period of days inside which it's possible to execute a DAO split
+    uint constant splitExecutionPeriod = 27 days;
+    // Period of time after which the minimum Quorum is halved
+    uint constant quorumHalvingPeriod = 52 weeks;
+    // Period after which a proposal can be closed (used in the case `executeProposal`
+    // fails because it throws)
+    uint constant executeProposalPeriod = 5 days;
+
+    // Proposals to spend the DAO's ether or to choose a new Curator
     Proposal[] public proposals;
@@
 
-    // Address of the service provider
+    // Address of the curator
     address public curator;
@@
     // The minimum deposit (in wei) required to submit any proposal that is not
-    // requesting a new service provider (no deposit is required for splits)
+    // requesting a new Curator (no deposit is required for splits)
     uint public proposalDeposit;
+
+    // the accumulated sum of all current proposal deposits
+    uint sumOfProposalDeposits;
 
@@
 
-    // A proposal with `newServiceProvider == false` represents a transaction
+    // A proposal with `newCurator == false` represents a transaction
     // to be issued by this DAO
-    // A proposal with `newServiceProvider == true` represents a DAO split
+    // A proposal with `newCurator == true` represents a DAO split
     struct Proposal {
         // The address where the `amount` will go to if the proposal is accepted
-        // or if `newServiceProvider` is true, the proposed service provider of
+        // or if `newCurator` is true, the proposed Curator of
         // the new DAO).
@@
         uint proposalDeposit;
-        // True if this proposal is to assign a new service provider
-        bool newServiceProvider;
+        // True if this proposal is to assign a new Curator
+        bool newCurator;
         // Data needed for splitting the DAO
         SplitData[] splitData;
-        // Number of Tokens in favour of the proposal
+        // Number of Tokens in favor of the proposal
         uint yea;
@@
 
-    // Used only in the case of a newServiceProvider porposal.
+    // Used only in the case of a newCurator proposal.
     struct SplitData {
@@
 
-    /// @dev Constructor setting the default service provider and the address
+    /// @dev Constructor setting the Curator and the address
     /// for the contract able to create another DAO as well as the parameters
     /// for the DAO Token Sale
-    /// @param _defaultServiceProvider The default service provider
+    /// @param _curator The Curator
     /// @param _daoCreator The contract able to (re)create this DAO
@@
     /// @param _minValue Minimal value for a successful DAO Token Sale
-    /// @param _closingTime Date (in unix time) of the end of the DAO Token Sale
+    /// @param _closingTime Date (in Unix time) of the end of the DAO Token Sale
     /// @param _privateSale If zero the DAO Token Sale is open to public, a
@@
     //  function DAO(
-        //  address _defaultServiceProvider,
+        //  address _curator,
         //  DAO_Creator _daoCreator,
@@
 
-    /// @dev This function is used by the service provider to send money back
+    /// @dev This function is used to send money back
     /// to the DAO, it can also be used to receive payments that should not be
@@
     /// `_recipient` with the transaction data `_transactionData`. If
-    /// `_newServiceProvider` is true, then this is a proposal that splits the
-    /// DAO and sets `_recipient` as the new DAO's service provider.
+    /// `_newCurator` is true, then this is a proposal that splits the
+    /// DAO and sets `_recipient` as the new DAO's Curator.
     /// @param _recipient Address of the recipient of the proposed transaction
@@
     /// @param _debatingPeriod Time used for debating a proposal, at least 2
-    /// weeks for a regular proposal, 10 days for new service provider proposal
-    /// @param _newServiceProvider Bool defining whether this proposal is about
-    /// a new service provider or not
+    /// weeks for a regular proposal, 10 days for new Curator proposal
+    /// @param _newCurator Bool defining whether this proposal is about
+    /// a new Curator or not
     /// @return The proposal ID. Needed for voting on the proposal
@@
         uint _debatingPeriod,
-        bool _newServiceProvider
+        bool _newCurator
     ) onlyTokenholders returns (uint _proposalID);
@@
 
-    /// @notice ATTENTION! I confirm to move my remaining funds to a new DAO
-    /// with `_newServiceProvider` as the new service provider, as has been
+    /// @notice close the proposal (used in the case `executeProposal`
+    /// fails because it throws)
+    /// @param _proposalID The proposal ID
+    function emergenyCloseProposal(uint _proposalID) external;
+
+    /// @notice ATTENTION! I confirm to move my remaining ether to a new DAO
+    /// with `_newCurator` as the new Curator, as has been
     /// proposed in proposal `_proposalID`. This will burn my tokens. This can
@@
     /// @param _proposalID The proposal ID
-    /// @param _newServiceProvider The new service provider of the new DAO
+    /// @param _newCurator The new Curator of the new DAO
     /// @dev This function, when called for the first time for this proposal,
@@
         uint _proposalID,
-        address _newServiceProvider
+        address _newCurator
     ) returns (bool _success);
@@
     /// @dev can only be called by the DAO itself through a proposal
-    /// updates the contract of the DAO by sending all funds and rewardTokens
-    /// to the new DAO. The new DAO needs to be approved by the service provider
+    /// updates the contract of the DAO by sending all ether and rewardTokens
+    /// to the new DAO. The new DAO needs to be approved by the Curator
     /// @param _newContract the address of the new contract
@@
     /// @param _recipient New recipient address
-    /// @dev Can only be called by the current service provider
-    function addAllowedAddress(address _recipient) external returns (bool _success);
+    /// @dev Can only be called by the current Curator
+    /// @return Whether successful or not
+    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
 
@@
 
+    /// @param _proposalID Id of the new curator proposal
+    /// @return Address of the new DAO
+    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
+
     /// @param _account The address of the account which is checked.
@@
         uint amount,
-        bool newServiceProvider,
+        bool newCurator,
         string description
@@
     event ProposalTallied(uint indexed proposalID, bool result, uint quorum);
-    event NewServiceProvider(address indexed _newServiceProvider);
+    event NewCurator(address indexed _newCurator);
     event AllowedRecipientAdded(address indexed _recipient);
@@
 
-        curator = _defaultServiceProvider;
+        curator = _curator;
         daoCreator = _daoCreator;
@@
         minQuorumDivisor = 5; // sets the minimal quorum to 20%
-        proposals.length++; // avoids a proposal with ID 0 because it is used
+        proposals.length = 1; // avoids a proposal with ID 0 because it is used
 
@@
     function () returns (bool success) {
-        if (now < closingTime + 40 days)
+        if (now < closingTime + saleGracePeriod)
             return buyTokenProxy(msg.sender);
@@
         uint _debatingPeriod,
-        bool _newServiceProvider
+        bool _newCurator
     ) onlyTokenholders returns (uint _proposalID) {
@@
         // Sanity check
-        if (_newServiceProvider && (
+        if (_newCurator && (
             _amount != 0
@@
             || msg.value > 0
-            || _debatingPeriod < 1 weeks)) {
-            throw;
-        } else if(
-            !_newServiceProvider
-            && (!isRecipientAllowed(_recipient) || (_debatingPeriod < 2 weeks))
+            || _debatingPeriod < minSplitDebatePeriod)) {
+            throw;
+        } else if (
+            !_newCurator
+            && (!isRecipientAllowed(_recipient) || (_debatingPeriod <  minProposalDebatePeriod))
         ) {
@@
 
-        if (!isFunded
+        if (_debatingPeriod > 8 weeks)
+            throw;
+
+        if (!isFueled
             || now < closingTime
-            || (msg.value < proposalDeposit && !_newServiceProvider)) {
+            || (msg.value < proposalDeposit && !_newCurator)) {
 
@@
         if (now + _debatingPeriod < now) // prevents overflow
+            throw;
+
+        // to prevent a 51% attacker to convert the ether into deposit
+        if (msg.sender == address(this))
             throw;
@@
         //p.proposalPassed = False; // that's default
-        p.newServiceProvider = _newServiceProvider;
-        if (_newServiceProvider)
+        p.newCurator = _newCurator;
+        if (_newCurator)
             p.splitData.length++;
@@
         p.proposalDeposit = msg.value;
+
+        sumOfProposalDeposits += msg.value;
+
         ProposalAdded(
@@
             _amount,
-            _newServiceProvider,
+            _newCurator,
             _description
@@
         Proposal p = proposals[_proposalID];
+
+        if (p.newCurator) {
+            if (now > p.votingDeadline + splitExecutionPeriod) {
+                p.open = false;
+            }
+            return;
+        }
+
         // Check if the proposal can be executed
@@
 
-        if (p.newServiceProvider) {
-            p.open = false;
+        // If the curator removed the recipient from the whitelist, close the proposal
+        // in order to free the deposit and allow unblocking of voters
+        if (!allowedRecipients[p.recipient] && p.open) {
+            closeProposal(_proposalID);
+            p.creator.send(p.proposalDeposit);
             return;
@@
 
+        bool proposalCheck = true;
+
+        if (p.amount > actualBalance())
+            proposalCheck = false;
+
         uint quorum = p.yea + p.nay;
 
+        // require 53% for calling newContract()
+        if (_transactionData.length >= 4 && _transactionData[0] == 0x68
+            && _transactionData[1] == 0x37 && _transactionData[2] == 0xff
+            && _transactionData[3] == 0x1e
+            && quorum < minQuorum(actualBalance() + rewardToken[address(this)])) {
+
+                proposalCheck = false;
+        }
+
         // Execute result
-        if (quorum >= minQuorum(p.amount) && p.yea > p.nay) {
+        if (quorum >= minQuorum(p.amount) && p.yea > p.nay && proposalCheck) {
             if (!p.creator.send(p.proposalDeposit))
                 throw;
-            // Without this throw, the creator of the proposal can repeat this,
-            // and get so much ether
+
+            lastTimeMinQuorumMet = now;
+
             if (!p.recipient.call.value(p.amount)(_transactionData))
                 throw;
+
             p.proposalPassed = true;
             _success = true;
-            lastTimeMinQuorumMet = now;
             rewardToken[address(this)] += p.amount;
             totalRewardToken += p.amount;
-        } else if (quorum >= minQuorum(p.amount) && p.nay >= p.yea) {
+        } else if (quorum >= minQuorum(p.amount) && p.nay >= p.yea || !proposalCheck) {
             if (!p.creator.send(p.proposalDeposit))
@@
 
-        // Since the voting deadline is over, close the proposal
-        p.open = false;
+        closeProposal(_proposalID);
 
@@
 
+    function closeProposal(uint _proposalID) internal {
+        Proposal p = proposals[_proposalID];
+        if (p.open)
+            sumOfProposalDeposits -= p.proposalDeposit;
+        p.open = false;
+    }
+
+    function emergenyCloseProposal(uint _proposalID) external {
+        Proposal p = proposals[_proposalID];
+        if (p.votingDeadline + executeProposalPeriod < now && p.open)
+            closeProposal(_proposalID);
+    }
+
     function splitDAO(
         uint _proposalID,
-        address _newServiceProvider
+        address _newCurator
     ) noEther onlyTokenholders returns (bool _success) {
@@
         if (now < p.votingDeadline  // has the voting deadline arrived?
-            //The request for a split expires 41 days after the voting deadline
-            || now > p.votingDeadline + 41 days
-            // Does the new service provider address match?
-            || p.recipient != _newServiceProvider
-            // Is it a new service provider proposal?
-            || !p.newServiceProvider
+            //The request for a split expires XX days after the voting deadline
+            || now > p.votingDeadline + splitExecutionPeriod
+            // Does the new Curator address match?
+            || p.recipient != _newCurator
+            // Is it a new curator proposal?
+            || !p.newCurator
             // Have you voted for this split?
@@
         if (address(p.splitData[0].newDAO) == 0) {
-            p.splitData[0].newDAO = createNewDAO(_newServiceProvider);
+            p.splitData[0].newDAO = createNewDAO(_newCurator);
             // Call depth limit reached, etc.
@@
                 throw;
-            // p.proposalDeposit should be zero here
-            if (this.balance < p.proposalDeposit)
-                throw;
-            p.splitData[0].splitBalance = this.balance - p.proposalDeposit;
+            // should never happen
+            if (this.balance < sumOfProposalDeposits)
+                throw;
+            p.splitData[0].splitBalance = actualBalance();
             p.splitData[0].rewardToken = rewardToken[address(this)];
@@
 
-        // Move funds and assign new Tokens
+        // Move ether and assign new Tokens
         uint fundsToBeMoved =
@@
             p.splitData[0].totalSupply;
+
+        uint paidOutToBeMoved = DAOpaidOut[address(this)] * rewardTokenToBeMoved /
+            rewardToken[address(this)];
+
         rewardToken[address(p.splitData[0].newDAO)] += rewardTokenToBeMoved;
@@
         rewardToken[address(this)] -= rewardTokenToBeMoved;
+
+        DAOpaidOut[address(p.splitData[0].newDAO)] += paidOutToBeMoved;
+        if (DAOpaidOut[address(this)] < paidOutToBeMoved)
+            throw;
+        DAOpaidOut[address(this)] -= paidOutToBeMoved;
 
@@
         balances[msg.sender] = 0;
-        paidOut[address(p.splitData[0].newDAO)] += paidOut[msg.sender];
         paidOut[msg.sender] = 0;
-
         return true;
@@
         if (msg.sender != address(this) || !allowedRecipients[_newContract]) return;
-        // move all funds
-        _newContract.call.value(address(this).balance)();
+        // move all ether
+        if (!_newContract.call.value(address(this).balance)()) {
+            throw;
+        }
 
@@
         DAO dao = DAO(msg.sender);
+
+        if ((rewardToken[msg.sender] * DAOrewardAccount.accumulatedInput()) /
+            totalRewardToken < DAOpaidOut[msg.sender])
+            throw;
+
         uint reward =
@@
     function withdrawRewardFor(address _account) noEther internal returns (bool _success) {
+        if ((balanceOf(_account) * rewardAccount.accumulatedInput()) / totalSupply < paidOut[_account])
+            throw;
+
         uint reward =
@@
     function transfer(address _to, uint256 _value) returns (bool success) {
-        if (isFunded
+        if (isFueled
             && now > closingTime
@@
     function transferFrom(address _from, address _to, uint256 _value) returns (bool success) {
-        if (isFunded
+        if (isFueled
             && now > closingTime
@@
     function changeProposalDeposit(uint _proposalDeposit) noEther external {
-        if (msg.sender != address(this) || _proposalDeposit > this.balance / 10)
+        if (msg.sender != address(this) || _proposalDeposit > actualBalance() / 10)
             throw;
@@
 
-    function addAllowedAddress(address _recipient) noEther external returns (bool _success) {
+    function changeAllowedRecipients(address _recipient, bool _allowed) noEther external returns (bool _success) {
         if (msg.sender != curator)
             throw;
-        allowedRecipients[_recipient] = true;
+        allowedRecipients[_recipient] = _allowed;
         return true;
@@
 
+    function actualBalance() internal constant returns (uint _actualBalance) {
+        return this.balance - sumOfProposalDeposits;
+    }
+
     function minQuorum(uint _value) internal constant returns (uint _minQuorum) {
@@
         return totalSupply / minQuorumDivisor +
-            (_value * totalSupply) / (3 * (this.balance + totalRewardToken));
+            (_value * totalSupply) / (3 * (actualBalance() + rewardToken[address(this)]));
     }
@@
     function halveMinQuorum() returns (bool _success) {
-        if (lastTimeMinQuorumMet < (now - 52 weeks)) {
+        if (lastTimeMinQuorumMet < (now - quorumHalvingPeriod)) {
             lastTimeMinQuorumMet = now;
@@
 
-    function createNewDAO(address _newServiceProvider) internal returns (DAO _newDAO) {
-        NewServiceProvider(_newServiceProvider);
-        return daoCreator.createDAO(_newServiceProvider, 0, 0, now + 42 days);
+    function createNewDAO(address _newCurator) internal returns (DAO _newDAO) {
+        NewCurator(_newCurator);
+        return daoCreator.createDAO(_newCurator, 0, 0, now + splitExecutionPeriod);
     }
@@
         return proposals.length - 1;
+    }
+
+    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO) {
+        return proposals[_proposalID].splitData[0].newDAO;
     }
@@
         Proposal p = proposals[blocked[_account]];
-        if (!p.open) {
+        if (now > p.votingDeadline) {
             blocked[_account] = 0;
@@
     function createDAO(
-        address _defaultServiceProvider,
+        address _curator,
         uint _proposalDeposit,
@@
         return new DAO(
-            _defaultServiceProvider,
+            _curator,
             DAO_Creator(this),
@@
 }
+
 \end{verbatim}
@@
 
-    address curator;
-    bytes32 hashOfTheContract;
+    address contractor;
+    bytes32 hashOfTheTerms;
     uint minDailyCosts;
@@
                 throw;
-        } else if (msg.sender != curator) {
+        } else if (msg.sender != contractor) {
                 throw;
@@
     function SampleOffer(
-        address _curator,
-        bytes32 _hashOfTheContract,
+        address _contractor,
+        bytes32 _hashOfTheTerms,
         uint _totalCosts,
@@
     ) {
-        curator = _curator;
-        hashOfTheContract = _hashOfTheContract;
+        contractor = _contractor;
+        hashOfTheTerms = _hashOfTheTerms;
         totalCosts = _totalCosts;
@@
             throw;
-        if (!curator.send(oneTimeCosts))
+        if (!contractor.send(oneTimeCosts))
             throw;
@@
     function getDailyPayment() {
-        if (msg.sender != curator)
+        if (msg.sender != contractor)
             throw;
         uint amount = (now - dateOfSignature) / (1 days) * dailyCosts - paidOut;
-        if (curator.send(amount))
+        if (contractor.send(amount))
             paidOut += amount;
@@
         if (deploymentReward > 10 ether)
-            throw; // TODO, set a max defined by service provider, or ideally oracle (set in euro)
+            throw; // TODO, set a max defined by Curator, or ideally oracle (set in euro)
         deploymentReward = _deploymentReward;
@@
 
-    // interface for Slocks
+    // interface for Ethereum Computer
     function payOneTimeReward() returns(bool) {
@@
         } else {
-            if (curator.send(msg.value)) {
+            if (contractor.send(msg.value)) {
                 return true;

### 2016-04-13 tests/scenarios/newcontract/run.py
Add a succesfull newContract transition test
- Adds the test for a succesful new contract transition
- Adjust comment in DAO.sol to not go over the 80 column limit

@@ -1,0 +1,42 @@
+from utils import calculate_bytecode
+
+scenario_description = (
+    """A test of the DAO contract upgrade. We create a new contract with a
+    completely different code and vote to transfer everything to the new
+    contract.
+    """
+)
+
+
+def calculate_reward(tokens, total_tokens, total_rewards):
+    result = (tokens * float(total_rewards)) / float(total_tokens)
+    return result
+
+
+def run(ctx):
+    ctx.assert_scenario_ran('rewards')
+
+    # let's just use an existing account
+    newAddress = ctx.accounts[4]
+    bytecode = calculate_bytecode('6837ff1e', newAddress.strip("0x").zfill(64))
+    ctx.create_js_file(substitutions={
+        "dao_abi": ctx.dao_abi,
+        "dao_address": ctx.dao_addr,
+        "new_contract_address": newAddress,
+        "proposal_deposit": ctx.args.proposal_deposit,
+        "transaction_bytecode": bytecode,
+        "debating_period": ctx.args.proposal_debate_seconds,
+        "prop_id": ctx.next_proposal_id()
+    }
+    )
+    print(
+        "Notice: Debate period is {} seconds so the test will wait "
+        "as much".format(ctx.args.proposal_debate_seconds)
+    )
+
+    ctx.execute(expected={
+        "proposal_passed": True,
+        "dao_balance_after": 0,
+        "money_transferred": True,
+        "reward_tokens_transferred": True
+    })

### 2016-04-13 tests/utils.py

@@ -342,6 +342,8 @@ def calculate_bytecode(function_hash, value):
 
     if value_type is int:
         return "{0}{1:0{2}x}".format(function_hash, value, 64)
+    elif isinstance(value, basestring):
+        return "0x{}{}".format(function_hash, value)
     else:
         print("Error: Invalid value type at 'calculate_bytecode()`")
         sys.exit(1)

### 2016-04-13 tests/scenarios/newcontractfail/run.py
Add test for failed newContract() upgrade
- Adding a test where the newContract() proposal fails due to the quorum
  not reading 53.3%

- Add a test utility function to create a vote array to reach a target
  quorum given as an argument to it.

@@ -1,15 +1,16 @@
-from utils import calculate_bytecode
+from utils import calculate_bytecode, create_votes_array_for_quorum, arr_str
 
 scenario_description = (
-    """A test of the DAO contract upgrade. We create a new contract with a
-    completely different code and vote to transfer everything to the new
-    contract.
+    """A test of the DAO contract upgrade where the proposal's quorum ends up
+    being insufficient (<53.3%) and the proposal gets rejected.
     """
 )
 
-def run(ctx):
-    ctx.assert_scenario_ran('rewards')
 
+def run(ctx):
+    ctx.assert_scenario_ran('fuel')
+
+    votes = create_votes_array_for_quorum(ctx.token_amounts, 0.4, True)
     # let's just use an existing account
     newAddress = ctx.accounts[4]
     bytecode = calculate_bytecode('6837ff1e', newAddress.strip("0x").zfill(64))
@@ -18,6 +19,7 @@ def run(ctx):
         "dao_address": ctx.dao_addr,
         "new_contract_address": newAddress,
         "proposal_deposit": ctx.args.proposal_deposit,
+        "votes": arr_str(votes),
         "transaction_bytecode": bytecode,
         "debating_period": ctx.args.proposal_debate_seconds,
         "prop_id": ctx.next_proposal_id()
@@ -28,8 +30,7 @@ def run(ctx):
     )
 
     ctx.execute(expected={
-        "proposal_passed": True,
-        "dao_balance_after": 0,
-        "money_transferred": True,
-        "reward_tokens_transferred": True
+        "proposal_passed": False,
+        "new_contract_balance": 0,
+        "dao_balance_diff": 0
     })

### 2016-04-13 tests/scenarios/newcontractfail/template.js

@@ -1,0 +1,63 @@
+var dao = web3.eth.contract($dao_abi).at('$dao_address');
+
+// No need to have an actual contract for the purpose of the test
+var newContract = '$new_contract_address';
+addToTest('new_contract_balance_before', web3.fromWei(eth.getBalance(newContract)));
+addToTest('dao_balance_before', web3.fromWei(eth.getBalance(dao.address)));
+console.log("Add new contract as allowed recipient");
+dao.changeAllowedRecipients.sendTransaction(newContract, true, {from: curator, gas: 1000000});
+checkWork();
+
+console.log("Create the proposal to update");
+dao.newProposal.sendTransaction(
+    dao.address,
+    web3.toWei(0, "ether"),
+    'Move all funds to a new contract',
+    '$transaction_bytecode',
+    $debating_period,
+    false,
+    {
+        from: proposalCreator,
+        value: web3.toWei($proposal_deposit, "ether"),
+        gas: 1000000
+    }
+);
+checkWork();
+
+console.log("Vote on the proposal to update");
+var prop_id = $prop_id;
+var votes = $votes;
+for (i = 0; i < votes.length; i++) {
+    dao.vote.sendTransaction(
+        prop_id,
+        votes[i],
+        {
+            from: eth.accounts[i],
+            gas: 4000000
+        }
+    );
+}
+checkWork();
+
+setTimeout(function() {
+    miner.stop(0);
+    console.log("Executing proposal ...");
+    dao.executeProposal.sendTransaction(prop_id, '$transaction_bytecode', {from:curator, gas:1000000});
+    checkWork();
+    addToTest('proposal_passed', dao.proposals(prop_id)[5]);
+
+    addToTest('new_contract_balance_after', web3.fromWei(eth.getBalance(newContract)));
+    addToTest('new_contract_balance', bigDiff(
+        testMap['new_contract_balance_after'],
+        testMap['new_contract_balance_before']
+    ));
+    addToTest('dao_balance_after', web3.fromWei(eth.getBalance(dao.address)));
+    addToTest('dao_balance_diff', bigDiff(
+        testMap['dao_balance_after'],
+        testMap['dao_balance_before']
+    ));
+
+    testResults();
+}, $debating_period * 1000);
+console.log("Wait for end of debating period");
+miner.start(1);

### 2016-04-13 tests/utils.py

@@ -65,12 +65,28 @@ def seconds_in_future(secs):
     return ts_now() + secs
 
 
-def create_votes_array(amounts, succeed):
+def create_votes_array(amounts, approve):
+    """
+    Create an array of votes out of the tokens holders to either pass or
+    reject a proposal.
+        Parameters
+        ----------
+        amounts : list
+        The list of tokens each token holder has
+
+        approve : bool
+        True if we want to pass and false if we want to vote against
+        the proposal
+
+        Returns
+        ----------
+        The array of votes required
+    """
     votes = []
     total = sum(amounts)
     percentage = 0.0
 
-    if not succeed:
+    if not approve:
         for val in amounts:
             ratio = val/float(total)
             if (percentage + ratio < 0.5):
@@ -87,6 +103,45 @@ def create_votes_array(amounts, succeed):
             else:
                 votes.append(False)
 
+    return votes
+
+
+def create_votes_array_for_quorum(amounts, targetQuorum, approve):
+    """
+    Create an array of votes for a proposal that will reach a targetQuorum
+        Parameters
+        ----------
+        amounts : list
+        The list of tokens each token holder has
+
+        targetQuorum : float
+        A target quorum represented by a float ranging from 0.0 to 1.0. It
+        represents percentage of the quorum we want to achieve
+
+        approve : bool
+        True if we want to pass and false if we want to vote against
+        the proposal
+
+        Returns
+        ----------
+        The array of votes required
+    """
+    votes = []
+    total = sum(amounts)
+    percentage = 0.0
+
+    for val in amounts:
+        ratio = val/float(total)
+        if (percentage + ratio < targetQuorum):
+            votes.append(approve)
+            percentage += ratio
+        else:
+            break
+    if not votes or percentage > targetQuorum:
+        print("ERROR: Could not satisfy the target quorum of '{}' with the "
+              "currrent way the token holders bought tokens. Please rerun the "
+              "test in order to get a different set of token holders")
+        sys.exit(1)
     return votes
 
 

### 2016-04-13 tests/sha3.py
Add native python keccak implementation for tests

@@ -1,0 +1,411 @@
+#! /usr/bin/env python
+# coding: utf-8
+
+# The Keccak sponge function was designed by Guido Bertoni, Joan Daemen,
+# Michaël Peeters and Gilles Van Assche. For more information, feedback or
+# questions, please refer to their website: http://keccak.noekeon.org/
+#
+# Based on the implementation by Renaud Bauvin,
+# from http://keccak.noekeon.org/KeccakInPython-3.0.zip
+#
+# Modified by Moshe Kaplan to be hashlib-compliant
+#
+# To the extent possible under law, the implementer has waived all copyright
+# and related or neighboring rights to the source code in this file.
+# http://creativecommons.org/publicdomain/zero/1.0/
+
+
+import math
+
+
+def sha3_224(data=None):
+  return Keccak(c=448, r=1152, n=224, data=data)
+
+
+def sha3_256(data=None):
+  return Keccak(c=512, r=1088, n=256, data=data)
+
+
+def sha3_384(data=None):
+  return Keccak(c=768, r=832, n=384, data=data)
+
+
+def sha3_512(data=None):
+  return Keccak(c=1024, r=576, n=512, data=data)
+
+
+class KeccakError(Exception):
+  """Custom error Class used in the Keccak implementation"""
+
+  def __init__(self, value):
+    self.value = value
+
+  def __str__(self):
+    return repr(self.value)
+
+
+class Keccak:
+  def __init__(self, r, c, n, data=None):
+    # Initialize the constants used throughout Keccak
+    # bitrate
+    self.r = r
+    # capacity
+    self.c = c
+    # output size
+    self.n = n
+
+    self.b = r + c
+    # b = 25*w
+    self.w = self.b // 25
+     # 2**l = w
+    self.l = int(math.log(self.w, 2))
+
+    self.n_r = 12 + 2 * self.l
+
+    self.block_size = r
+    self.digest_size = n
+
+    # Initialize the state of the sponge
+    # The state is made up of 25 words, each word being w bits.
+    self.S = [[0, 0, 0, 0, 0],
+             [0, 0, 0, 0, 0],
+             [0, 0, 0, 0, 0],
+             [0, 0, 0, 0, 0],
+             [0, 0, 0, 0, 0]]
+
+    # A string of hexchars, where each char represents 4 bits.
+    self.buffered_data = ""
+
+    # Store the calculated digest.
+    # We'll only apply padding and recalculate the hash if it's modified.
[…]

### 2016-04-13 tests/sha3.py
State sha3 source and style sha3.py

@@ -1,6 +1,11 @@
 #! /usr/bin/env python
 # coding: utf-8
 
+# Lefteris Karapetsas copied this from here:
+# https://github.com/moshekaplan/python-sha3
+# so that I can include a python-only keccak implementation for the DAO tests
+# without having users of the tests download external packages using pip
+
 # The Keccak sponge function was designed by Guido Bertoni, Joan Daemen,
 # Michaël Peeters and Gilles Van Assche. For more information, feedback or
 # questions, please refer to their website: http://keccak.noekeon.org/
@@ -19,393 +24,406 @@ import math
 
 
 def sha3_224(data=None):
-  return Keccak(c=448, r=1152, n=224, data=data)
+    return Keccak(c=448, r=1152, n=224, data=data)
 
 
 def sha3_256(data=None):
-  return Keccak(c=512, r=1088, n=256, data=data)
+    return Keccak(c=512, r=1088, n=256, data=data)
 
 
 def sha3_384(data=None):
-  return Keccak(c=768, r=832, n=384, data=data)
+    return Keccak(c=768, r=832, n=384, data=data)
 
 
 def sha3_512(data=None):
-  return Keccak(c=1024, r=576, n=512, data=data)
+    return Keccak(c=1024, r=576, n=512, data=data)
 
 
 class KeccakError(Exception):
-  """Custom error Class used in the Keccak implementation"""
+    """Custom error Class used in the Keccak implementation"""
 
-  def __init__(self, value):
-    self.value = value
+    def __init__(self, value):
+        self.value = value
 
-  def __str__(self):
-    return repr(self.value)
+    def __str__(self):
+        return repr(self.value)
 
 
 class Keccak:
-  def __init__(self, r, c, n, data=None):
-    # Initialize the constants used throughout Keccak
-    # bitrate
-    self.r = r
-    # capacity
-    self.c = c
-    # output size
-    self.n = n
+    def __init__(self, r, c, n, data=None):
+        # Initialize the constants used throughout Keccak
+        # bitrate
+        self.r = r
+        # capacity
+        self.c = c
+        # output size
+        self.n = n
 
-    self.b = r + c
-    # b = 25*w
-    self.w = self.b // 25
-     # 2**l = w
-    self.l = int(math.log(self.w, 2))
+        self.b = r + c
+        # b = 25*w
+        self.w = self.b // 25
[…]

### 2016-04-14 tests/scenarios/newcontract/run.py
Tests now calculate transactionData on their own
`calculate_bytecode()` has gotten a big upgrade since it now accepts a
function name and a list of arguments as tuples of type and variable.

Using those it can now calculate the transaction data on its own. Some
cases are missing but will be added as needed

@@ -12,7 +12,7 @@ def run(ctx):
 
     # let's just use an existing account
     newAddress = ctx.accounts[4]
-    bytecode = calculate_bytecode('6837ff1e', newAddress.strip("0x").zfill(64))
+    bytecode = calculate_bytecode('newContract', ('address', ctx.accounts[4]))
     ctx.create_js_file(substitutions={
         "dao_abi": ctx.dao_abi,
         "dao_address": ctx.dao_addr,

### 2016-04-14 tests/scenarios/newcontractfail/run.py

@@ -13,7 +13,7 @@ def run(ctx):
     votes = create_votes_array_for_quorum(ctx.token_amounts, 0.4, True)
     # let's just use an existing account
     newAddress = ctx.accounts[4]
-    bytecode = calculate_bytecode('6837ff1e', newAddress.strip("0x").zfill(64))
+    bytecode = calculate_bytecode('newContract', ("address", newAddress))
     ctx.create_js_file(substitutions={
         "dao_abi": ctx.dao_abi,
         "dao_address": ctx.dao_addr,

### 2016-04-14 tests/utils.py

@@ -5,6 +5,7 @@ import os
 import json
 import sys
 import re
+from sha3 import sha3_256 as sha3
 from datetime import datetime
 from jsutils import js_common_intro
 
@@ -371,10 +372,10 @@ def edit_dao_source(contracts_dir, keep_limits, halve_minquorum):
     return new_path
 
 
-def calculate_bytecode(function_hash, value):
+def calculate_bytecode(function_name, *args):
     """
-    Create the bytecode for calling function with `function_hash` and the
-    given argument value as defined here:
+    Create the bytecode for calling function with `function_name` and the
+    given arguments as defined here:
     https://github.com/ethereum/wiki/wiki/Ethereum-Contract-ABI#examples
 
         Parameters
@@ -382,26 +383,44 @@ def calculate_bytecode(function_hash, value):
         function_hash : string
         The first 4 bytes of the hash of the function signature.
 
-        value : anything
-        The value to encode. Encoding depends on the value's type
+        args : list
+        A list of arguments to encode. Each argument consists of a tuple of
+        the argument type and its value.
 
         Returns
         ----------
         results : string
-        The encoded ABI for the function call with the given argument
+        The encoded ABI for the function call with the given arguments
     """
-    value_type = type(value)
-    if value_type is bool:
-        value_type = int
-        value = 1 if value is True else 0
 
-    if value_type is int:
-        return "{0}{1:0{2}x}".format(function_hash, value, 64)
-    elif isinstance(value, basestring):
-        return "0x{}{}".format(function_hash, value)
-    else:
-        print("Error: Invalid value type at 'calculate_bytecode()`")
-        sys.exit(1)
+    # form the function's hash
+    types = []
+    for arg in args:
+        types.append(arg[0])
+    function_hash = "0x" + sha3("{}({})".format(
+        function_name,
+        ','.join(types)
+    )).hexdigest()[:8]
+
+    bytecode = function_hash
+    for arg in args:
+        # import pdb
+        # pdb.set_trace()
+        arg_type = arg[0]
+        arg_val = arg[1]
+        if arg_type == "bool" or arg_type == "uint256":
+            if arg_type == "bool":
+                arg_val = 1 if arg[1] is True else 0
+            bytecode += "{0:0{1}x}".format(arg_val, 64)
+        elif arg_type == "address":
+            bytecode += arg_val.strip("0x").zfill(64)
+        else:
+            print(
+                "Error: Invalid argument type '{}' given at "
[…]

### 2016-04-14 tests/scenarios/deposit/run.py
Fix the deposit change scenario
Switch from serviceProvider to curator nomenclature

@@ -7,9 +7,12 @@ scenario_description = (
 
 
 def run(ctx):
-    ctx.assert_scenario_ran('fund')
+    ctx.assert_scenario_ran('fuel')
 
-    bytecode = calculate_bytecode('0xe33734fd', ctx.args.deposit_new_value)
+    bytecode = calculate_bytecode(
+        'changeProposalDeposit',
+        ('uint256', ctx.args.deposit_new_value)
+    )
     ctx.create_js_file(substitutions={
             "dao_abi": ctx.dao_abi,
             "dao_address": ctx.dao_addr,

### 2016-04-14 tests/scenarios/deposit/template.js

@@ -39,7 +39,7 @@ checkWork();
 setTimeout(function() {
     miner.stop(0);
     console.log("Executing proposal ...");
-    dao.executeProposal.sendTransaction(prop_id, '$transaction_bytecode', {from:serviceProvider, gas:1000000});
+    dao.executeProposal.sendTransaction(prop_id, '$transaction_bytecode', {from:curator, gas:1000000});
     checkWork();
 
     addToTest('proposal_passed', dao.proposals(prop_id)[5]);

### 2016-04-14 paper/Paper.tex

@@
 Collaboration without a corporate form does not solve these problems, necessarily, and it may introduce others.
-In the absence of a coporate form, an explicit written agreement is substituted for unclear informal ``understandings'' and legal protections provided by a corporate form will not be available.
+In the absence of a corporate form, an explicit written agreement is substituted for unclear informal ``understandings'' and the legal protections provided by a corporate form will not be available.
 
@@
 Crowdfunding (\cite{2015CFReport}) amplifies the problem.
-On the one hand, it has made it easier for small contributors to invest in large projects.
-It has also made it possible for entrepeneurs to receive financial support that might not have been easily available in the past.
-On the other hand, small investors remain vulnerable to financial mismanagement or outright fraud.
-Because they have small stakes in a venture, they may lack power to identify problems, participate in governance decisions, or to easily recover their investment (\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}).
-At the same time, corporate leadership and managment may be accused of malfeasance or mismanagement when they believe that they have acted in good faith, based on their understanding of their obligations and interpretation of applicable rules.
+On the one hand, it has made it easier for small contributors to invest in large projects, and it has also made it possible for entrepreneurs to receive financial support that might not have been easily available in the past.
+On the other hand, small investors remain vulnerable to financial mismanagement or outright fraud, and because they have a small stake in a venture, they may lack power to identify problems, participate in governance decisions, or to easily recover their investment (\cite{9MostDisgracefulCrowdFundings, CrowdfundingFailTC}).
+At the same time, corporate leadership and management may be accused of malfeasance or mismanagement when they believe that they have acted in good faith, based on their understanding of their obligations and interpretation of applicable rules.
 
 We present a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality.
-We illustrate a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2) where governance rules are formalized and automated using software.
+We illustrate a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2) where governance rules are formalized, automated and enforced using software.
 Specifically, we have written generic smart contract code (\cite{szabo1997formalizing, miller1997future}) that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain.
-In this paper we explain how the DAO code works.
-We do so by focusing on some basic formation and governance features, including formation, funding and voting rights.
-
-We first describe the DAO's formation and basic functionality.
+In this paper we explain how a DAO's code works.
+We do so by focusing on some basic formation and governance features, including formation, creation and voting rights.
+
+We first describe a DAO's formation and basic functionality.
 We then discuss minority owner rights and propose a solution to the ``Majority Robbing the Minority Attack'' problem, the ``DAO split''.
@@
 
-Once deployed, the DAO code requires ``ether'' to engage in transactions on Ethereum.
+Once deployed, a DAO's code requires ``ether'' to engage in transactions on Ethereum.
 Ether is the digital fuel that powers the Ethereum network.
-Without ether, a DAO can not do very much and a DAO's first order of business is to receive ether.
-After the DAO code is deployed, ether may be sent to the DAO's smart contract address during an initial funding period which is defined in the DAO code.
-
-In exchange for ether, the DAO code creates tokens that are then assigned to the account of the person who sent the ether.
-A token grants its holder voting and ownership rights.
+Without ether, a DAO can not do anything so a DAO's first order of business is to receive ether.
+After a DAO's code is deployed, ether may be sent to the DAO's smart contract address during an initial Creation Phase which is defined in the DAO's code.
+
+In exchange for ether, a DAO's code creates tokens that are assigned to the account of the person who sent the ether.
+The token grants its holder voting and ownership rights.
 The number of tokens created is proportional to the amount of ether transferred.
 Token price varies over time (see section \ref{TokenPrice}).
-Token ownership is freely transferable on the Ethereum blockchain, when the funding period is over.
-
-A minimum DAO funding goal and funding time-period are set as parameters in the DAO code during to deployment.
-If the minimum funding amount is not reached at the close of the funding period, all ether is returned.
-After the funding period has ended, we denote the total ether raised by $\Xi_{\text{raised}}$ and the total amount of tokens created by $T_{\text{total}}$.
-
-The DAO stores ether and transmits it based on the DAO code.
+Token ownership is freely transferable on the Ethereum blockchain, when the Creation Phase has ended.
+
+A minimum DAO Creation goal and Creation Phase time-period are set as parameters in a DAO's code at the time of deployment.
+If the minimum DAO Creation goal is not reached at the close of the Creation Phase, all ether is returned.
+After the Creation Phase has ended, the total ether raised is denoted by $\Xi_{\text{raised}}$ and the total amount of tokens created is denoted by $T_{\text{total}}$.
+
+A DAO stores ether and other Ethereum based tokens and transmits them based on the DAO's code.
 It does not do much else.
 It cannot build a product, write code or develop hardware.
-It requires what we have called a ``Service Provider'' to accomplish these and other goals.
-The DAO engages a Service Provider by accepting a Service Provider proposal.
-
-DAO token holders may also submit proposals to use the DAO's ether, denoted by $\Xi_{\text{transfer}}$, for a variety of purposes.
+It requires what we have called a ``Contractor'' to accomplish these and other goals.
+A DAO selects a Contractor by accepting a Contractor's proposal.
+
+Any DAO Token Holder may become a Contractor by submitting proposals to use a DAO's ether, denoted by $\Xi_{\text{transfer}}$.
 If a proposal is approved, the DAO transmits ether to a smart contract representing the proposed project.
-Such smart contracts can be parameterized and enable the DAO to interact with and influence the project being funded.
-An example of such an agreement between the DAO and a project to be funded can be found in the appendix (\ref{app:SampleOffer}).
-
-Members of the DAO cast votes weighted by the amount of tokens they control.
-Tokens are divisible, indistinguishable, fungible and can easily be transferred between accounts.
+Such smart contracts can be parameterized and enable a DAO to interact with and influence the project it chose to support.
+An example of such an agreement between a DAO and a project to be funded can be found in the appendix (\ref{app:SampleOffer}).
+
+Members of a DAO cast votes weighted by the amount of tokens they control.
+Tokens are divisible, indistinguishable and can easily be transferred between accounts.
 Within the contracts, the individual actions of members, cannot be directly determined.
-There is a set timeframe $t_p$ to debate and vote on any given proposal.
-In our example, this timeframe is set by the creator of the proposal, and is required to be at least two weeks for a regular proposal.
+There is a set time frame $t_p$ to debate and vote on any given proposal.
+In our example, this time frame is set by the creator of the proposal, and is required to be at least two weeks for a regular proposal.
 
@@
 If this is not the case, the proposal will be closed.
+
 The minimum quorum represents the minimum number of tokens required for a vote to be valid, is denoted by $q_{min}$, and calculated as follows:
@@
 Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
-$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{DAO}}$ is the amount of reward tokens owned by this DAO, as explained in section \ref{RewardToken} (also see \verb|rewardToken| in \ref{app:DAO}).
-The sum $\Xi_{DAO} + R_{\text{DAO}}$ is equal to the amount of ether raised plus the rewards received or said another way, the total amount of ether the DAO has ever received.
+$\Xi_{DAO}$ is the amount of ether owned by a DAO and $R_{\text{DAO}}$ is the amount of reward tokens owned by this DAO, as explained in section \ref{RewardToken} (also see \verb|rewardToken| in \ref{app:DAO}).
+The sum $\Xi_{DAO} + R_{\text{DAO}}$ is equal to the amount of ether used to Create DAO tokens plus the rewards received or said another way, the total amount of ether a DAO has ever received.
 
 This means, initially, a quorum of  $20\%$ of all tokens is required for any proposal to pass.
-In the event $\Xi_{\text{transfer}}$ equals the amount of ether raised during the funding period plus the rewards received, then a quorum of $53.33\%$ is required.
-
-In order to prevent ``proposal spam'', a minimal deposit is required to be paid when creating a proposal, which gets refunded if quorum is achieved.
+In the event $\Xi_{\text{transfer}}$ equals the amount of ether a DAO has ever received, then a quorum of $53.33\%$ is required.
+
+In order to prevent ``proposal spam'', a minimal deposit can be required to be paid when creating a proposal, which gets refunded if quorum is achieved.
 If quorum is not achieved, the DAO keeps the proposal deposit.
@@
 But many of these solutions fail because minority owners may lack voting rights or the ability to ``vote with their feet" and easily retrieve their capital.
-We present a solution to this problem in the DAO code.
+We present a solution to this problem in the DAO's code.
 
@@
 To prevent this, the minority must always have the ability to retrieve their portion of the funds.
-Our solution is to allow the DAO to split into two.
-If an individual, or a group of token holders, disagree with a proposal and want to retrieve their portion of the funds before the proposal gets executed, they can submit a special type of proposal to form a new DAO.
-The minority can then vote to move their funds to this new DAO, leaving the majority alone only able to spend their own money.
+Our solution is to allow a DAO to split into two.
+If an individual, or a group of token holders, disagree with a proposal and want to retrieve their portion of the ether before the proposal gets executed, they can submit and approve a special type of proposal to form a new DAO.
+The token holders that voted for this proposal can then split the DAO moving their portion of the ether to this new DAO, leaving the rest alone only able to spend their own money.
+
 This idea originates from a blog post by Vitalik Buterin (\cite{Vitalik2015subjectivity}).
 
-A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely.
+A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in their DAO and might not follow proposals closely.
 An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act.
-For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their ether.
-Our proposed solution is implemented by limiting each individual DAO to a single curator.
-This curator controls the list of addresses that can receive ether from the DAO, across all proposals.
-This gives the curator of the DAO considerable power.
-To prevent the abuse of this power, it is possible for the DAO to vote for a new curator, which may result in a split of the DAO as described above.
-
-Any token holder can make a proposal to vote for a new curator.
+For a DAO to be considered safe, it is required that inactive token holders must also be protected from losing their ether.
+Our proposed solution is implemented by limiting each individual DAO to a single Curator.
+This Curator controls the list of addresses that can receive ether from the DAO, across all proposals.
+This gives the Curator of a DAO considerable power. To prevent the abuse of this power, it is possible for a DAO to vote for a new Curator, which may result in a split of the DAO as described above.
+
+Any token holder can make a proposal to vote for a new Curator.
 In effect, even a single token holder is able to both retrieve their remaining portion of ether and maintain their right to any future rewards associated to their previous contribution, as these will be sent to the new DAO automatically.
-Rewards are defined as any ether received by the DAO generated from products the DAO funded so far and are explained in further detail in section \ref{RewardToken}.
-
-The process of choosing a new curator is as follows:
-Any token holder can submit a proposal for a new curator.
+Rewards are defined as any ether received by a DAO generated from products the DAO funded so far and are explained in further detail in section \ref{RewardToken}.
+
+The process of choosing a new Curator is as follows:
+Any token holder can submit a proposal for a new Curator.
 In this case, no proposal deposit is required, because an attacker could vote for an extremely high deposit, preventing any splits.
@@
 There is no quorum requirement, so that every token holder has the ability to split into their own DAO.
-The debating period is used to discuss (on or off-chain) the new curator and conduct a first vote that's non-binding.
-After this first vote, token holders can cast a second one to confirm its results.
-In the case a majority opts to  keep the original curator, the minority can either change their vote to keep the original curator in order to avoid a split, or inversely they can confirm their vote for a new curator and move their portion of the funds to a new DAO.
+The debating period is used to discuss (on or off-chain) the new Curator and conduct a first vote that's non-binding.
+After this first vote, token holders can confirm its results or not.
+In the case a majority opts to  keep the original Curator, the minority can either keep the original Curator in order to avoid a split, or inversely they can confirm their vote for a new Curator and move their portion of the ether to a new DAO.
 
 \section{Token Price} \label{TokenPrice}
-DAO Token price increases over time.
-This reflects an assumption that early purchasers have greater risk, as they may have less information about the potential success of the DAO and do not know whether follow-on contribution will lead to full funding of the DAO.
-For the DAO described here, we have chosen the following price schedule:
+DAO Token Creation schedule increases over time.
+This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO.
+For the DAO described here, we have chosen the following Creation schedule:
 \begin{equation}
@@
 Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
-Hence the number of tokens (in it’s base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether payed, denoted in wei.
-This results in a constant price in the beginning, until $2$ weeks before the end of the token sale.
-At this time the price increased daily by $0.05 \: \Xi_c$ per base unit of DAO token.
-Until $4$ days before the closing time when there will be a constant price of $1.5 \: \Xi_c$ per base unit of DAO token.
-
-Price increases during the initial funding period could lead to a situation where a single contributor, having bought tokens during the initial price, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors paying a higher price (\cite{GriffDiscussion}).
-In order to avoid that possibility, all ether that is payed above the initial price of the token, will be sent to an extra account.
+Hence the number of tokens (in its base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel the DAO, denoted in wei.
+This results in a constant Creation ratio in the beginning, until $2$ weeks before the end of the DAO Creation.
+At this time the Creation ratio increases daily by $0.05 \: \Xi_c$ per base unit of DAO token.
+Until $4$ days before the closing time when there will be a constant Creation ratio of $1.5 \: \Xi_c$ per base unit of DAO token.
+
+Creation ratio increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens during at the initial Creation ratio, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having a higher Creation ratio (\cite{GriffDiscussion}).
+In order to avoid that possibility, all ether that is received above the initial Creation ratio of the token, will be sent to an extra account.
 Denoted as \verb|extraBalance| in \ref{app:TokenSale}.
-This money can be sent back to the DAO through a proposal after the DAO has spent at least this amount of ether.
+This ether can be sent back to the DAO through a proposal after the DAO has spent at least this amount of ether.
 This rule is implemented in the internal function \verb|isRecipientAllowed| in section \ref{DAO}.
@@
 
-The address \verb|curator| is set at the creation of the DAO and defines the curator.
+The address \verb|curator| is set at the creation of the DAO and defines the Curator.
 
@@
 
-The integer \verb|proposalDeposit| specifies the minimum deposit to be paid in wei for any proposal that does not include a change of the curator.
+The integer \verb|proposalDeposit| specifies the minimum deposit to be paid in wei for any proposal that does not include a change of the Curator.
 
@@
 The creator of the proposal will be refunded the entire deposit if quorum is reached, if it is not reached the deposit remains with the DAO.
- \item[newCurator] A boolean which is true if this proposal assigns a new curator.
- \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new curator.
+ \item[newCurator] A boolean which is true if this proposal assigns a new Curator.
+ \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new Curator.
  \item[yea] Number of tokens in favor of the proposal.
@@
 \begin{description}
- \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current curator or an address on the whitelist \verb|allowedRecipients|).
+ \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current Curator or an address on the whitelist \verb|allowedRecipients|).
  \item[amount] The amount of wei to be sent in the proposed transaction.
@@
  \item[transactionData] The data of the proposed transaction.
- \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 1 week for a new curator proposal.
- \item[newCurator] A boolean defining whether this proposal is for a new curator or not.
+ \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 1 week for a new Curator proposal.
+ \item[newCurator] A boolean defining whether this proposal is for a new Curator or not.
 \end{description}
@@
 This function can be called by anyone.
-It counts the votes, in order to check whether the quorum is met, and executes the proposal if it passed, unless it is a proposal for a new curator, than it does nothing.
+It counts the votes, in order to check whether the quorum is met, and executes the proposal if it passed, unless it is a proposal for a new Curator, than it does nothing.
 The arguments of the function are:
@@
 \subsubsection*{splitDAO}
-After a new curator has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new curator.
+After a new Curator has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new Curator.
 This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
@@
  \item[proposalID] The proposal ID.
- \item[newCurator] The address of the new curator of the new DAO.
+ \item[newCurator] The address of the new Curator of the new DAO.
 \end{description}
@@
 This is used to update the contract.
-The new address needs to be approved by the curator.
+The new address needs to be approved by the Curator.
 
@@
 \subsubsection*{changeAllowedRecipients}
-This function can add/remove an address to/from the whitelist, \verb|allowedRecipients|. It can only be executed by the curator.
+This function can add/remove an address to/from the whitelist, \verb|allowedRecipients|. It can only be executed by the Curator.
 
@@
 
-Let’s assume that during the split, a fraction of DAO tokens, $X$, changes the curator and leaves the DAO.
+Let’s assume that during the split, a fraction of DAO tokens, $X$, changes the Curator and leaves the DAO.
 The new DAO created receives $X \cdot \Xi_{\text{DAO pre}}$, a portion of the remaining ether from the original DAO.
@@
 
-The original DAO tokens of the accounts that confirmed the new curator are destroyed.
+The original DAO tokens of the accounts that confirmed the new Curator are destroyed.
 Hence:
@@
 
-    // Address of the curator
+    // Address of the Curator
     address public curator;

### 2016-04-14 paper/Paper.tex

@@
 If an individual, or a group of token holders, disagree with a proposal and want to retrieve their portion of the ether before the proposal gets executed, they can submit and approve a special type of proposal to form a new DAO.
-The token holders that voted for this proposal can then split the DAO moving their portion of the ether to this new DAO, leaving the rest alone only able to spend their own money.
+The token holders that voted for this proposal can then split the DAO moving their portion of the ether to this new DAO, leaving the rest alone only able to spend their own ether.
 
@@
 
-Creation ratio increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens during at the initial Creation ratio, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having a higher Creation ratio (\cite{GriffDiscussion}).
+Creation ratio increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens at the initial Creation ratio, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having a higher Creation ratio (\cite{GriffDiscussion}).
 In order to avoid that possibility, all ether that is received above the initial Creation ratio of the token, will be sent to an extra account.
@@
     // The amount of days for which people who try to participate in the sale
-    // by calling the fallback function will still get their money back
+    // by calling the fallback function will still get their ether back
     uint constant saleGracePeriod = 40 days;
@@
     address public curator;
-    // The whitelist: List of addresses the DAO is allowed to send money to
+    // The whitelist: List of addresses the DAO is allowed to send ether to
     mapping (address => bool) public allowedRecipients;
@@
 
-    /// @dev This function is used to send money back
+    /// @dev This function is used to send ether back
     /// to the DAO, it can also be used to receive payments that should not be

### 2016-04-14 tests/utils.py
arr_str() function can now also handle strings

@@ -147,7 +147,28 @@ def create_votes_array_for_quorum(amounts, targetQuorum, approve):
 
 
 def arr_str(arr):
-    return '[ ' + ', '.join([str(x).lower() for x in arr]) + ' ]'
+    """
+    Create a string representation of an array, ready to be imported to js.
+        Parameters
+        ----------
+        arr : list
+        The list from which to create the array string. Can be an array of
+        ints, strings or booleans
+
+        Returns
+        ----------
+        A string representation of the array ready to be imported in a js
+        template
+    """
+    if type(arr) is not list or arr == []:
+        print("ERROR: 'arr_str()' expects a non-empty list")
+        sys.exit(1)
+    has_strings = isinstance(arr[0], basestring)
+    return "[ {} ]".format(
+        ', '.join(['"{}"'.format(
+            str(x).lower()
+        ) if has_strings else str(x).lower() for x in arr])
+    )
 
 
 def extract_test_dict(name, output):

### 2016-04-14 tests/utils.py
compare_values() can now compare floats and ints

@@ -190,18 +190,23 @@ def extract_test_dict(name, output):
     return result
 
 
-def compare_values(a, b):
-    if isinstance(a, float) ^ isinstance(b, float):
-        print("ERROR: float compared with non-float")
-        return False
-    if isinstance(a, float):
-        return abs(a - b) <= 0.01
-    elif isinstance(a, basestring) and isinstance(b, int):
-        return int(a) == b
-    elif isinstance(b, basestring) and isinstance(a, int):
-        return a == int(b)
+def compare_values(got, expect):
+    if isinstance(got, float) ^ isinstance(expect, float):
+        if isinstance(got, int) and expect % 1 <= 0.01:
+            return int(expect) == got
+        elif isinstance(expect, int) and got % 1 <= 0.01:
+            return int(got) == expect
+        else:
+            print("ERROR: float compared with non-float")
+            return False
+    if isinstance(got, float):
+        return abs(got - expect) <= 0.01
+    elif isinstance(got, basestring) and isinstance(expect, int):
+        return int(got) == expect
+    elif isinstance(expect, basestring) and isinstance(got, int):
+        return got == int(expect)
     else:
-        return a == b
+        return got == expect
 
 
 def eval_test(name, output, expected_dict):

### 2016-04-14 tests/scenarios/newcontract/run.py
Fix singlesplit and add new test functions
- Single split scenario needed to give total supply in ether, not WEI

- Add attempt_proposal() function in tests which encapsulates the
  proposal creation, checking and subsequent proposal ID generatio in
  one function

- Add a tests-only external function to check the minQuorum()

- Use attempt_proposal() all around the codebase

- Remove test context's next_proposal_id()

@@ -7,6 +7,7 @@ scenario_description = (
     """
 )
 
+
 def run(ctx):
     ctx.assert_scenario_ran('rewards')
 
@@ -19,8 +20,7 @@ def run(ctx):
         "new_contract_address": newAddress,
         "proposal_deposit": ctx.args.proposal_deposit,
         "transaction_bytecode": bytecode,
-        "debating_period": ctx.args.proposal_debate_seconds,
-        "prop_id": ctx.next_proposal_id()
+        "debating_period": ctx.args.proposal_debate_seconds
     })
     print(
         "Notice: Debate period is {} seconds so the test will wait "

### 2016-04-14 tests/scenarios/singlesplit/template.js

@@ -1,32 +1,19 @@
-var dao = web3.eth.contract($dao_abi).at('$dao_address');
+var dao_abi = $dao_abi;
+var dao = web3.eth.contract(dao_abi).at('$dao_address');
 var newCurator = eth.accounts[1];
 
-
-console.log("Our disgruntled user is creating proposal to change SP to itself...");
-var tx_hash = null;
-dao.newProposal.sendTransaction(
-    newCurator,
-    0,
-    'eth.accounts[1] wants to split out',
-    '',
-    $debating_period,
-    true,
-    {
-        from: newCurator,
-        gas: 1000000
-    }
-    , function (e, res) {
-        if (e) {
-            console.log(e + "at newProposal()!");
-        } else {
-            tx_hash = res;
-            console.log("newProposal tx hash is: " + tx_hash);
-        }
-    }
+var prop_id = attempt_proposal(
+    dao, // DAO in question
+    newCurator, // recipient
+    newCurator, // proposal creator
+    0, // proposal amount in ether
+    'Our disgruntled user wants to split out', // description
+    '', //bytecode
+    $debating_period, // debating period
+    0, // proposal deposit in ether
+    true // whether it's a split proposal or not
 );
-checkWork();
 
-var prop_id = $prop_id;
 console.log("Voting for split proposal '" + prop_id + "' ...");
 for (i = 0; i < eth.accounts.length; i++) {
     dao.vote.sendTransaction(
@@ -56,7 +43,7 @@ setTimeout(function() {
     addToTest('proposal_passed', dao.proposals(prop_id)[5]);
     addToTest('proposal_newdao', dao.splitProposalNewAddress(prop_id, 0));
 
-    var newdao = web3.eth.contract($dao_abi).at(testMap['proposal_newdao']);
+    var newdao = web3.eth.contract(dao_abi).at(testMap['proposal_newdao']);
     // check token balance of each user in both DAOs
     oldDAOBalance = [];
     newDAOBalance = [];
@@ -69,47 +56,36 @@ setTimeout(function() {
     addToTest('newDAOTotalSupply', parseInt(web3.fromWei(newdao.totalSupply())));
 
     setTimeout(function() {
+        console.log("MINQUORUM REQUIRED: " + newdao.extMinQuorum(newdao.totalSupply()));
         // now our disgruntled user has his own DAO and is the SP of that DAO so ...
-        console.log("Angry user proposes to his own DAO to send all funds to himself...");
-        newdao.newProposal.sendTransaction(
[…]

### 2016-04-15 paper/Paper.tex
Changed to American style punctiation

@@
 We first describe a DAO's formation and basic functionality.
-We then discuss minority owner rights and propose a solution to the ``Majority Robbing the Minority Attack'' problem, the ``DAO split''.
-We then explore the smart contract code in detail, and conclude with an explanation and detailed specification of the ``DAO split''.
+We then discuss minority owner rights and propose a solution to the ``Majority Robbing the Minority Attack'' problem, the ``DAO split.'' We then explore the smart contract code in detail, and conclude with an explanation and detailed specification of the ``DAO split.''
 
@@
 
-In order to prevent ``proposal spam'', a minimal deposit can be required to be paid when creating a proposal, which gets refunded if quorum is achieved.
+In order to prevent ``proposal spam,'' a minimal deposit can be required to be paid when creating a proposal, which gets refunded if quorum is achieved.
 If quorum is not achieved, the DAO keeps the proposal deposit.
@@
 
-There is a special function which is called the constructor. It has the same name as the contract ``DAO''. This function is only executed once, when the DAO is created.
+There is a special function which is called the constructor. It has the same name as the contract ``DAO.'' This function is only executed once, when the DAO is created.
 In the DAO constructor, the following variables are set:

### 2016-04-15 paper/Paper.tex
We was removed and function 3 times was fixed

@@
 It can also be used by a registered corporate entity to automate formal governance rules contained in corporate bylaws or imposed by law.
-We first discuss the DAO Concept.
-We then discuss minority rights, and propose a solution to a ``robbing the minority'' attack vector.
-Finally, we provide a practical implementation of a first generation DAO entity using smart contracts written in Solidity on the Ethereum blockchain.
+First the DAO Concept is described, then minority rights is discussed, and a solution to a ``robbing the minority'' attack vector isproposed.
+Finally, a practical implementation of a first generation DAO entity is provided using smart contracts written in Solidity on the Ethereum blockchain.
 \end{abstract}
@@
 
-We present a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality.
-We illustrate a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2) where governance rules are formalized, automated and enforced using software.
-Specifically, we have written generic smart contract code (\cite{szabo1997formalizing, miller1997future}) that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain.
-In this paper we explain how a DAO's code works.
-We do so by focusing on some basic formation and governance features, including formation, creation and voting rights.
-
-We first describe a DAO's formation and basic functionality.
-We then discuss minority owner rights and propose a solution to the ``Majority Robbing the Minority Attack'' problem, the ``DAO split.'' We then explore the smart contract code in detail, and conclude with an explanation and detailed specification of the ``DAO split.''
+This paper presents a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality.
+This paper illustrates a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2)  governance rules are formalized, automated and enforced using software.
+Specifically, generic smart contract code (\cite{szabo1997formalizing, miller1997future}) has been written that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain.
+This paper explains how a DAO's code works, focusing on some basic formation and governance features, including structure, creation and voting rights.
+
+First a DAO's Creation Phase and basic functionality are described.
+Then minority owner rights are discussed and a solution to the ``Majority Robbing the Minority Attack'' problem is proposed: the ``DAO split.'' The smart contract code is then explored in detail, and conclude with an explanation and detailed specification of the ``DAO split.''
 
@@
 Ultimately, how a DAO functions and its legal status will depend on many factors, including how DAO code is used, where it is used, and who uses it.
-We do not speculate about the legal status of DAOs worldwide.
+This paper does not speculate about the legal status of DAOs worldwide.
 This paper is not intended to offer legal advice or conclusions.
@@
 It cannot build a product, write code or develop hardware.
-It requires what we have called a ``Contractor'' to accomplish these and other goals.
+It requires a ``Contractor'' to accomplish these and other goals.
 A DAO selects a Contractor by accepting a Contractor's proposal.
@@
 Throughout this paper, $\Xi$ always represents an amount of ether in its base unit wei. This is defined as $1 \: \text{Wei} = 10^{-18} \: \text{Ether}$ (\cite{Wood2014ethereum}).
-Similarly, DAO tokens are denoted with $T$ and always represent the amount of DAO tokens in its base unit. We define this as $10^{-16}$ DAO token.
+Similarly, DAO tokens are denoted with $T$ and always represent the amount of DAO tokens in its base unit, defined as $10^{-16}$ DAO token.
+
 \section{Majority robs minority attack}
@@
 But many of these solutions fail because minority owners may lack voting rights or the ability to ``vote with their feet" and easily retrieve their capital.
-We present a solution to this problem in the DAO's code.
+This paper presents a solution to this problem in the DAO's code.
 
@@
 This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO.
-For the DAO described here, we have chosen the following Creation schedule:
+The DAO described in this paper has the following Creation schedule:
 \begin{equation}
@@
 Each contract has member variables and functions which can be externally called by sending a transaction to the Ethereum network with the DAO contract address as the recipient and the method ID (optional with parameters) as data.
-In this section we will discuss the meaning of the variables and the functions in detail.
+This section will discuss the meaning of the variables and the functions in detail.
 
@@
 \url{https://blog.ethereum.org/2015/12/04}. The main feature added is the splitting mechanism and all that comes with it.
-Now we will define the member variables and functions one at a time.
+This section will define the member variables and functions from the above smart contract one at a time.
 
@@
 
-We will now discuss the functions of the DAO contract in detail. Many of the member variables that are used in this contract are defined in one of the other three contracts.
+This section will discuss the functions of the DAO contract in detail. Many of the member variables that are used in this contract are defined in one of the other three contracts.
 
@@
 
-In this section we give a description of how reward tokens are implemented in this contract. Much of the information has already been explained, but it is restated here for clarity.
+This section gives a description of how reward tokens are implemented in this contract. Much of the information has already been explained, but it is restated here for clarity.
 
@@
 
-In this section we want to formally describe some parameters and their behavior during a split.
+This section formally describes a few important parameters and their behavior during a split.
 
@@
 But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the address of the new contract as parameter.
-If accepted, the complete DAO moves to the new contract, meaining, all ether and reward tokens are transferred to the new contract.
+If accepted, the complete DAO moves to the new contract, meaning, all ether and reward tokens are transferred to the new contract.
 In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens.

### 2016-04-15 tests/test.py
Add split_execution_period as a test argument

@@ -151,7 +151,8 @@ class TestContext():
         dao_contract = edit_dao_source(
             self.contracts_dir,
             keep_limits,
-            self.args.proposal_halveminquorum
+            self.args.proposal_halveminquorum,
+            self.args.split_execution_period
         )
 
         res = self.compile_contract(dao_contract)

### 2016-04-15 tests/utils.py

@@ -325,7 +325,11 @@ def re_replace_or_die(string, varname, value):
     return new_string
 
 
-def edit_dao_source(contracts_dir, keep_limits, halve_minquorum):
+def edit_dao_source(
+        contracts_dir,
+        keep_limits,
+        halve_minquorum,
+        split_exec_period):
     with open(os.path.join(contracts_dir, 'DAO.sol'), 'r') as f:
         contents = f.read()
 
@@ -334,7 +338,11 @@ def edit_dao_source(contracts_dir, keep_limits, halve_minquorum):
         re.sub
         contents = re_replace_or_die(contents, "minProposalDebatePeriod", "1")
         contents = re_replace_or_die(contents, "minSplitDebatePeriod", "1")
-        contents = re_replace_or_die(contents, "splitExecutionPeriod", "20")
+        contents = re_replace_or_die(
+            contents,
+            "splitExecutionPeriod",
+            str(split_exec_period)
+        )
         contents = re_replace_or_die(contents, "saleGracePeriod", "1")
 
     if halve_minquorum:  # if we are testing halve_minquorum remove year limit

### 2016-04-15 tests/jsutils.py
Add more utils functions and enrich split scenario
- Added util function time_now()
- Added util function attempt_split()
- Split scenario now exports some extra variables

@@ -20,6 +20,10 @@ function checkWork() {
     miner.stop(0);
 }
 
+function time_now() {
+    return Math.floor(Date.now() / 1000);
+}
+
 function bigDiff(astr, bstr) {
     return new BigNumber(astr).minus(new BigNumber(bstr));
 }
@@ -54,8 +58,23 @@ function attempt_proposal(
     is_split_proposal
     ) {
 
+    dao_closing_time = argdao.closingTime();
+
+    if (!argdao.isFueled()) {
+        testFail(
+            "Failed to create a proposal to: '" + desc + "' because the DAO "
+            + "is not fueled."
+        );
+    }
+    if (dao_closing_time.gt(time_now())) {
+        testFail(
+            "Failed to create a proposal to: '" + desc + "' because the DAO's "
+            + "sale time has not yet closed.\\ndao_closing_time: "
+            + dao_closing_time + "\\nnow(): " + time_now()
+        );
+    }
     proposals_num_before = argdao.numberOfProposals();
-    console.log("Creating a new proposal to: " + desc);
+    console.log("Creating a new proposal to: '" + desc + "'");
     argdao.newProposal.sendTransaction(
     recipient,
     web3.toWei(ether_amount, "ether"),
@@ -72,11 +91,31 @@ function attempt_proposal(
     proposals_num_now = argdao.numberOfProposals();
 
     if (!proposals_num_now.equals(proposals_num_before.add(1))) {
-        testFail("Failed to create a proposal to: " + desc);
+        testFail("Failed to create a proposal to: " + desc + "'");
     } else {
         console.log("Proposal succesfully created");
     }
     return proposals_num_now;
+}
+
+function attempt_split(argdao, prop_id, user, new_curator, split_exec_period) {
+    console.log("Account '" + user + "' is calling splitDAO()");
+    var vote_deadline = argdao.proposals(prop_id)[3];
+    if (vote_deadline.gt(time_now())) {
+        testFail("Can't split the DAO while the proposal is still debated.");
+    }
+    var prop_deadline = vote_deadline.add(split_exec_period);
+    console.log("prop_deadline: " + prop_deadline);
+    console.log("now(): " + time_now());
+    if (prop_deadline.lessThan(time_now() + 5)) {
+        testFail("Can no longer vote to split the DAO. 'now > p.votingDeadline + splitExecutionPeriod'");
+    }
+    argdao.splitDAO.sendTransaction(
+        prop_id,
[…]

### 2016-04-15 tests/scenarios/split/run.py

@@ -74,11 +74,12 @@ def prepare_test_split(ctx, split_gas):
         not ctx.args.proposal_fail
     )
     ctx.create_js_file(substitutions={
-            "dao_abi": ctx.dao_abi,
-            "dao_address": ctx.dao_addr,
-            "debating_period": ctx.args.split_debate_seconds,
-            "split_gas": split_gas,
-            "votes": arr_str(votes)
+        "dao_abi": ctx.dao_abi,
+        "dao_address": ctx.dao_addr,
+        "debating_period": ctx.args.split_debate_seconds,
+        "split_execution_period": ctx.args.split_execution_period,
+        "split_gas": split_gas,
+        "votes": arr_str(votes)
         }
     )
     print(
@@ -97,7 +98,7 @@ def run(ctx):
     split_gas = 4000000
 
     votes = prepare_test_split(ctx, split_gas)
-    print("---> VOTES: {}".format(votes))
+    print("---> SPLIT VOTES: {}".format(votes))
     oldBalance, newBalance, oldDAORewards, newDAORewards = tokens_after_split(
         votes,
         ctx.token_amounts,
@@ -119,7 +120,9 @@ def run(ctx):
     #     "newDAOBalance": [0] * len(self.token_amounts),
     # })
     # remember some variables so they can be used in later tests
-    ctx.childDAOAddress = results['proposal_newdao']
-    ctx.childDAOMembers = [
+    ctx.child_dao_closing_time = results['new_dao_closing_time']
+    ctx.child_dao_curator = results['new_curator']
+    ctx.child_dao_address = results['proposal_newdao']
+    ctx.child_dao_members = [
         ctx.accounts[idx] for idx, x in enumerate(votes) if x is True
     ]

### 2016-04-15 tests/scenarios/split/template.js

@@ -1,6 +1,8 @@
 var dao_abi = $dao_abi;
 var dao = web3.eth.contract(dao_abi).at('$dao_address');
 var newCurator = eth.accounts[1];
+var split_execution_period = $split_execution_period;
+addToTest('new_curator', newCurator);
 
 var prop_id = attempt_proposal(
     dao, // DAO in question
@@ -17,6 +19,7 @@ var prop_id = attempt_proposal(
 var votes = $votes;
 console.log("Voting for split proposal '" + prop_id + "' ...");
 for (i = 0; i < votes.length; i++) {
+    console.log("User [" + i + "] is voting '" + votes[i] + "'for split proposal");
     dao.vote.sendTransaction(
         prop_id,
         votes[i],
@@ -36,14 +39,10 @@ setTimeout(function() {
     // now each user who voted for the split should call splitDAO to execute the proposal
     for (i = 0; i < votes.length; i++) {
         if (votes[i]) {
-            dao.splitDAO.sendTransaction(
-                prop_id,
-                newCurator,
-                {from:eth.accounts[i], gas: $split_gas}
-            );
+            console.log("User [" + i + "] is calling splitDAO()");
+            attempt_split(dao, prop_id, eth.accounts[i], newCurator, split_execution_period);
         }
     }
-    checkWork();
     console.log("After split execution");
     addToTest('proposal_passed', dao.proposals(prop_id)[5]);
     addToTest('proposal_newdao', dao.splitProposalNewAddress(prop_id, 0));
@@ -63,6 +62,7 @@ setTimeout(function() {
 
     addToTest('newDAOTotalSupply', parseInt(web3.fromWei(newdao.totalSupply())));
     addToTest('newDAOProposalDeposit', parseInt(web3.fromWei(newdao.proposalDeposit())));
+    addToTest('new_dao_closing_time', parseInt(newdao.closingTime()));
 
     testResults();
 }, $debating_period * 1000);

### 2016-04-15 paper/Paper.tex
Creation Ratio to Creation Rate

@@
 Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
-Hence the number of tokens (in its base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel the DAO, denoted in wei.
-This results in a constant Creation ratio in the beginning, until $2$ weeks before the end of the DAO Creation.
-At this time the Creation ratio increases daily by $0.05 \: \Xi_c$ per base unit of DAO token.
-Until $4$ days before the closing time when there will be a constant Creation ratio of $1.5 \: \Xi_c$ per base unit of DAO token.
-
-Creation ratio increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens at the initial Creation ratio, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having a higher Creation ratio (\cite{GriffDiscussion}).
-In order to avoid that possibility, all ether that is received above the initial Creation ratio of the token, will be sent to an extra account.
+Hence the number of tokens (in its base unit) each buyer Creates is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel the DAO, denoted in wei.
+This results in a constant Creation rate in the beginning, until $2$ weeks before the end of the DAO Creation Phase.
+At this time the Creation rate increases daily by $0.05 \: \Xi_c$ per base unit of DAO token.
+Until $4$ days before the closing time when there will be a constant Creation rate of $1.5 \: \Xi_c$ per base unit of DAO token.
+
+Creation rate increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens at the initial Creation rate, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having fueled a DAO at a higher Creation rate (\cite{GriffDiscussion}).
+In order to avoid that possibility, all ether that is used to fuel the DAO above the initial Creation rate, will be sent to an extra account.
 Denoted as \verb|extraBalance| in \ref{app:TokenSale}.

### 2016-04-15 tests/scenarios/multisplitrewards/template.js
First version of multisplit test plus improvements
- Adding a first passing version of the multisplit test

- `create_votes_array()` will can now create the voting array
  by starting iteration from the last account

- a lot of information is saved at the split test so that it can be
  propagated to later tests

- The child DAO and subsequently the grandchild DAO curators are being
  set a lot more carefully now in order not to coincide

@@ -1,0 +1,52 @@
+var dao_abi = $dao_abi;
+var dao = eth.contract(dao_abi).at('$dao_address');
+var child_dao = eth.contract(dao_abi).at('$child_dao_address');
+var child_curator = '$child_dao_curator';
+var child_dao_members = $child_dao_members;
+var grandchild_curator = '$grandchild_dao_curator';
+var split_execution_period = $split_execution_period;
+addToTest('grandchild_curator_childdao_balance', web3.fromWei(child_dao.balanceOf(grandchild_curator)).ceil());
+if (child_curator == grandchild_curator) {
+    testFail("Child curator can't also be grandchild curator");
+}
+
+var child_prop_id = attempt_proposal(
+    child_dao, // DAO in question
+    grandchild_curator, // recipient
+    grandchild_curator, // proposal creator
+    0, // proposal amount in ether
+    'Proposal to split the child DAO to the grand child DAO', // description
+    '', //bytecode
+    $debating_period, // debating period
+    0, // proposal deposit in ether
+    true // whether it's a split proposal or not
+);
+
+console.log("Vote to split to grandchild DAO.");
+child_dao.vote.sendTransaction(child_prop_id, true, {from: grandchild_curator, gas: 1000000});
+checkWork();
+console.log("After vote to split call");
+setTimeout(function() {
+    miner.stop(0);
+    console.log("Executing grandchild DAO split proposal...");
+    // now each user who voted for the split should call splitDAO to execute the proposal
+    attempt_split(
+        child_dao,
+        child_prop_id,
+        grandchild_curator,
+        grandchild_curator,
+        split_execution_period
+    );
+    checkWork();
+    console.log("After split execution");
+    addToTest('proposal_passed', child_dao.proposals(child_prop_id)[5]);
+    addToTest('proposal_newdao', child_dao.splitProposalNewAddress(child_prop_id, 0));
+
+
+    var grandchild_dao = web3.eth.contract(dao_abi).at(testMap['proposal_newdao']);
+    addToTest('grandchild_dao_total_supply', parseInt(web3.fromWei(grandchild_dao.totalSupply())));
+    addToTest('grandchild_dao_proposal_deposit', parseInt(web3.fromWei(grandchild_dao.proposalDeposit())));
+    addToTest('grandchild_curator_dao_balance', web3.fromWei(grandchild_dao.balanceOf(grandchild_curator)).ceil());
+    testResults();
+}, $debating_period * 1000);
+console.log("Wait for end of debating period");

### 2016-04-15 tests/scenarios/newcontractfail/run.py

@@ -10,7 +10,7 @@ scenario_description = (
 def run(ctx):
     ctx.assert_scenario_ran('fuel')
 
-    votes = create_votes_array_for_quorum(ctx.token_amounts, 0.4, True)
+    votes = create_votes_array_for_quorum(ctx.token_amounts, 0.4, True, False)
     # let's just use an existing account
     newAddress = ctx.accounts[4]
     bytecode = calculate_bytecode('newContract', ("address", newAddress))

### 2016-04-15 tests/scenarios/proposal/run.py

@@ -28,7 +28,8 @@ def run(ctx):
     amount = random.randint(minamount, sum(ctx.token_amounts))
     votes = create_votes_array(
         ctx.token_amounts,
-        not ctx.args.proposal_fail
+        not ctx.args.proposal_fail,
+        False
     )
     yay, nay = count_token_votes(ctx.token_amounts, votes)
     ctx.create_js_file(substitutions={

### 2016-04-15 tests/scenarios/split/run.py

@@ -71,15 +71,25 @@ def prepare_test_split(ctx, split_gas):
 
     votes = create_votes_array(
         ctx.token_amounts,
-        not ctx.args.proposal_fail
+        not ctx.args.proposal_fail,
+        True
     )
+    # remember the account information of the first True votes. They will be
+    # the child dao curator in this scenario and grandchild curator in the next
+    iterator = (
+        (ctx.accounts[i], ctx.token_amounts[i])
+        for i, vote in enumerate(votes) if vote is True
+    )
+    (ctx.child_dao_curator, _) = next(iterator)
+    (ctx.grandchild_dao_curator, ctx.grandchild_dao_curator_before) = next(iterator)
     ctx.create_js_file(substitutions={
         "dao_abi": ctx.dao_abi,
         "dao_address": ctx.dao_addr,
         "debating_period": ctx.args.split_debate_seconds,
         "split_execution_period": ctx.args.split_execution_period,
         "split_gas": split_gas,
-        "votes": arr_str(votes)
+        "votes": arr_str(votes),
+        "child_dao_curator": ctx.child_dao_curator
         }
     )
     print(
@@ -98,7 +108,6 @@ def run(ctx):
     split_gas = 4000000
 
     votes = prepare_test_split(ctx, split_gas)
-    print("---> SPLIT VOTES: {}".format(votes))
     oldBalance, newBalance, oldDAORewards, newDAORewards = tokens_after_split(
         votes,
         ctx.token_amounts,
@@ -113,16 +122,12 @@ def run(ctx):
         "oldDaoRewardTokens": oldDAORewards,
         "newDaoRewardTokens": newDAORewards
     })
-    # if gas != enough
-    #     eval_test('split-insufficient-gas', output, {
-    #     "newDAOProposalDeposit": 0,
-    #     "oldDAOBalance": self.token_amounts,
-    #     "newDAOBalance": [0] * len(self.token_amounts),
-    # })
+
     # remember some variables so they can be used in later tests
     ctx.child_dao_closing_time = results['new_dao_closing_time']
-    ctx.child_dao_curator = results['new_curator']
     ctx.child_dao_address = results['proposal_newdao']
     ctx.child_dao_members = [
         ctx.accounts[idx] for idx, x in enumerate(votes) if x is True
     ]
+    ctx.child_dao_balance_at_creation = results['new_dao_balance']
+    ctx.child_dao_total_supply_at_creation = results['new_dao_total_supply']

### 2016-04-15 tests/scenarios/split/template.js

@@ -1,12 +1,11 @@
 var dao_abi = $dao_abi;
 var dao = web3.eth.contract(dao_abi).at('$dao_address');
-var newCurator = eth.accounts[1];
 var split_execution_period = $split_execution_period;
-addToTest('new_curator', newCurator);
+var child_dao_curator = '$child_dao_curator';
 
 var prop_id = attempt_proposal(
     dao, // DAO in question
-    newCurator, // recipient
+    child_dao_curator, // recipient
     proposalCreator, // proposal creator
     0, // proposal amount in ether
     'Voting to split and change Curator', // description
@@ -40,7 +39,7 @@ setTimeout(function() {
     for (i = 0; i < votes.length; i++) {
         if (votes[i]) {
             console.log("User [" + i + "] is calling splitDAO()");
-            attempt_split(dao, prop_id, eth.accounts[i], newCurator, split_execution_period);
+            attempt_split(dao, prop_id, eth.accounts[i], child_dao_curator, split_execution_period);
         }
     }
     console.log("After split execution");
@@ -60,7 +59,8 @@ setTimeout(function() {
     addToTest('oldDaoRewardTokens', parseFloat(web3.fromWei(dao.rewardToken('$dao_address'))));
     addToTest('newDaoRewardTokens', parseFloat(web3.fromWei(dao.rewardToken(testMap['proposal_newdao']))));
 
-    addToTest('newDAOTotalSupply', parseInt(web3.fromWei(newdao.totalSupply())));
+    addToTest('new_dao_balance', web3.fromWei(eth.getBalance(newdao.address)).ceil());
+    addToTest('new_dao_total_supply', web3.fromWei(newdao.totalSupply()).ceil());
     addToTest('newDAOProposalDeposit', parseInt(web3.fromWei(newdao.proposalDeposit())));
     addToTest('new_dao_closing_time', parseInt(newdao.closingTime()));
 

### 2016-04-15 tests/utils.py

@@ -66,7 +66,7 @@ def seconds_in_future(secs):
     return ts_now() + secs
 
 
-def create_votes_array(amounts, approve):
+def create_votes_array(amounts, approve, reverse):
     """
     Create an array of votes out of the tokens holders to either pass or
     reject a proposal.
@@ -79,16 +79,21 @@ def create_votes_array(amounts, approve):
         True if we want to pass and false if we want to vote against
         the proposal
 
+        reverse : bool
+        True if we need to iterate the list in reverse to give chance for
+        True votes to the last accounts
+
         Returns
         ----------
         The array of votes required
     """
     votes = []
     total = sum(amounts)
+    amounts_for_traversal = list(reversed(amounts)) if reverse else amounts
     percentage = 0.0
 
     if not approve:
-        for val in amounts:
+        for val in amounts_for_traversal:
             ratio = val/float(total)
             if (percentage + ratio < 0.5):
                 votes.append(True)
@@ -96,7 +101,7 @@ def create_votes_array(amounts, approve):
             else:
                 votes.append(False)
     else:
-        for val in amounts:
+        for val in amounts_for_traversal:
             ratio = val/float(total)
             if percentage <= 0.5:
                 votes.append(True)
@@ -104,7 +109,7 @@ def create_votes_array(amounts, approve):
             else:
                 votes.append(False)
 
-    return votes
+    return list(reversed(votes)) if reverse else votes
 
 
 def create_votes_array_for_quorum(amounts, targetQuorum, approve):

### 2016-04-15 tests/scenarios/singlesplit/run.py
singlesplit scenario timing fix
Wait until the split execution deadline in order to be able to send the
money to yourself at the end

@@ -14,8 +14,8 @@ def run(ctx):
         "dao_abi": ctx.dao_abi,
         "dao_address": ctx.dao_addr,
         "proposal_deposit": ctx.args.proposal_deposit,
-        "split_gas": 4000000,
-        "debating_period": ctx.args.proposal_debate_seconds
+        "debating_period": ctx.args.proposal_debate_seconds,
+        "split_execution_period": ctx.args.split_execution_period
     })
     print(
         "Notice: Debate period is {} seconds so the test will wait "

### 2016-04-15 tests/scenarios/singlesplit/template.js

@@ -1,11 +1,12 @@
 var dao_abi = $dao_abi;
 var dao = web3.eth.contract(dao_abi).at('$dao_address');
-var newCurator = eth.accounts[1];
+var split_execution_period = $split_execution_period;
+var new_curator = eth.accounts[1];
 
 var prop_id = attempt_proposal(
     dao, // DAO in question
-    newCurator, // recipient
-    newCurator, // proposal creator
+    new_curator, // recipient
+    new_curator, // proposal creator
     0, // proposal amount in ether
     'Our disgruntled user wants to split out', // description
     '', //bytecode
@@ -31,14 +32,9 @@ addToTest('proposal_nay', parseInt(web3.fromWei(dao.proposals(prop_id)[10])));
 
 setTimeout(function() {
     miner.stop(0);
-    console.log("Executing the split proposal...");
     // now our disgruntled user is the only one to execute the splitDAO function
-    dao.splitDAO.sendTransaction(
-        prop_id,
-        newCurator,
-        {from:newCurator, gas: $split_gas}
-    );
-    checkWork();
+    attempt_split(dao, prop_id, new_curator, new_curator, split_execution_period);
+
     console.log("After split execution");
     addToTest('proposal_passed', dao.proposals(prop_id)[5]);
     addToTest('proposal_newdao', dao.splitProposalNewAddress(prop_id, 0));
@@ -60,8 +56,8 @@ setTimeout(function() {
         // now our disgruntled user has his own DAO and is the SP of that DAO so ...
         var new_prop_id = attempt_proposal(
             newdao, // DAO in question
-            newCurator, // recipient
-            newCurator, // proposal creator
+            new_curator, // recipient
+            new_curator, // proposal creator
             testMap['newDAOTotalSupply'], // proposal amount in ether
             'Send all money to myself!! Screw you guys ... I am going home!', // description
             '', //bytecode
@@ -75,18 +71,18 @@ setTimeout(function() {
             new_prop_id,
             true,
             {
-                from: newCurator,
+                from: new_curator,
                 gas: 1000000
             });
         checkWork();
         addToTest('newdao_proposals_num', newdao.numberOfProposals());
-        addToTest('angry_user_before', web3.fromWei(eth.getBalance(newCurator)));
+        addToTest('angry_user_before', web3.fromWei(eth.getBalance(new_curator)));
         setTimeout(function() {
             // now execute the proposal
[…]

### 2016-04-18 tests/jsutils.py
Reword Sale -> Creation and Buy -> Create

@@ -69,7 +69,7 @@ function attempt_proposal(
     if (dao_closing_time.gt(time_now())) {
         testFail(
             "Failed to create a proposal to: '" + desc + "' because the DAO's "
-            + "sale time has not yet closed.\\ndao_closing_time: "
+            + "creation time has not yet closed.\\ndao_closing_time: "
             + dao_closing_time + "\\nnow(): " + time_now()
         );
     }

### 2016-04-18 tests/scenarios/fuel/run.py

@@ -12,7 +12,7 @@ scenario_description = (
 def run(ctx):
     ctx.assert_scenario_ran('deploy')
 
-    sale_secs = ctx.remaining_time()
+    creation_secs = ctx.remaining_time()
     ctx.total_supply = ctx.args.deploy_min_value + random.randint(1, 100)
     ctx.token_amounts = constrained_sum_sample_pos(
         len(ctx.accounts), ctx.total_supply
@@ -20,13 +20,13 @@ def run(ctx):
     ctx.create_js_file(substitutions={
             "dao_abi": ctx.dao_abi,
             "dao_address": ctx.dao_addr,
-            "wait_ms": (sale_secs-3)*1000,
+            "wait_ms": (creation_secs-3)*1000,
             "amounts": arr_str(ctx.token_amounts)
         }
     )
     print(
         "Notice: Fueling period is {} seconds so the test will wait "
-        "as much".format(sale_secs)
+        "as much".format(creation_secs)
     )
 
     adjusted_amounts = (

### 2016-04-18 tests/scenarios/fuel/template.js

@@ -1,7 +1,7 @@
 var amounts = $amounts;
 
 var dao = web3.eth.contract($dao_abi).at('$dao_address');
-console.log("Buying DAO tokens");
+console.log("Creating DAO tokens");
 for (i = 0; i < eth.accounts.length; i++) {
     web3.eth.sendTransaction({
         from:eth.accounts[i],
@@ -23,11 +23,11 @@ setTimeout(function() {
     }
     addToTest('balances', balances);
 
-    // now also try to purchase some extra tokens after the sale ended
-    // note we use buyTokenProxy() directly because with the edited code
+    // now also try to purchase some extra tokens after the creation ended
+    // note we use createTokenProxy() directly because with the edited code
     // for the test the fallback function becomes a DAO donation code right
-    // after the end of the sale period
-    dao.buyTokenProxy.sendTransaction(eth.accounts[0],{
+    // after the end of the creation period
+    dao.createTokenProxy.sendTransaction(eth.accounts[0],{
         from:eth.accounts[0],
         to: dao.address,
         gas:200000,
@@ -38,5 +38,5 @@ setTimeout(function() {
     addToTest('user0_after', parseFloat(web3.fromWei(dao.balanceOf(eth.accounts[0]))));
     testResults();
 }, $wait_ms);
-console.log("Wait for end of sale");
+console.log("Wait for end of creation");
 miner.start(1);

### 2016-04-18 tests/scenarios/fuel_fail/run.py

@@ -13,7 +13,7 @@ def run(ctx):
     ctx.assert_scenario_ran('deploy')
 
     accounts_num = len(ctx.accounts)
-    sale_secs = ctx.remaining_time()
+    creation_secs = ctx.remaining_time()
     ctx.total_supply = random.randint(5, ctx.args.deploy_min_value - 4)
     ctx.token_amounts = constrained_sum_sample_pos(
         accounts_num, ctx.total_supply
@@ -21,13 +21,13 @@ def run(ctx):
     ctx.create_js_file(substitutions={
             "dao_abi": ctx.dao_abi,
             "dao_address": ctx.dao_addr,
-            "wait_ms": (sale_secs-3)*1000,
+            "wait_ms": (creation_secs-3)*1000,
             "amounts": arr_str(ctx.token_amounts)
         }
     )
     print(
         "Notice: Fueling period is {} seconds so the test will wait "
-        "as much".format(sale_secs)
+        "as much".format(creation_secs)
     )
     ctx.execute(expected={
         "dao_fueled": False,

### 2016-04-18 tests/scenarios/fuel_fail2/run.py

@@ -4,9 +4,9 @@ from utils import constrained_sum_sample_pos, arr_str
 
 scenario_description = (
     "During the fueling period of the DAO, buy DAO tokens from all accounts "
-    "with both normal buying and with buyTokenProxy(). When the goal "
-    "is not reached make sure that the refunds when having used buyTokenProxy "
-    "are distributed back to the users correctly"
+    "with both normal buying and with createTokenProxy(). When the goal "
+    "is not reached make sure that the refunds when having used "
+    "createTokenProxy() are distributed back to the users correctly"
 )
 
 
@@ -18,7 +18,7 @@ def run(ctx):
         print("Please increase the minimum fueling goal for the scenario.")
         sys.exit(1)
 
-    sale_secs = ctx.remaining_time()
+    creation_secs = ctx.remaining_time()
     total_supply = ctx.args.deploy_min_value - 4
     proxy_amounts = constrained_sum_sample_pos(
         accounts_num, total_supply / 2
@@ -34,14 +34,14 @@ def run(ctx):
         substitutions={
             "dao_abi": ctx.dao_abi,
             "dao_address": ctx.dao_addr,
-            "wait_ms": (sale_secs-3)*1000,
+            "wait_ms": (creation_secs-3)*1000,
             "proxy_amounts": arr_str(proxy_amounts),
             "normal_amounts": arr_str(normal_amounts)
         }
     )
     print(
         "Notice: Fueling period is {} seconds so the test will wait "
-        "as much".format(sale_secs)
+        "as much".format(creation_secs)
     )
     ctx.execute(expected={
         "dao_fueled": False,

### 2016-04-18 tests/scenarios/fuel_fail2/template.js

@@ -2,9 +2,9 @@ var proxy_amounts = $proxy_amounts;
 var normal_amounts = $normal_amounts;
 
 var dao = web3.eth.contract($dao_abi).at('$dao_address');
-console.log("Buying DAO tokens");
+console.log("Creating DAO tokens");
 for (i = 0; i < eth.accounts.length; i++) {
-    dao.buyTokenProxy.sendTransaction(
+    dao.createTokenProxy.sendTransaction(
         eth.accounts[eth.accounts.length - 1 - i],
         {
         from:eth.accounts[i],
@@ -68,5 +68,5 @@ setTimeout(function() {
 
     testResults();
 }, $wait_ms);
-console.log("Wait for end of sale");
+console.log("Wait for end of creation");
 miner.start(1);

### 2016-04-18 paper/Paper.tex
White paper buy/create sale/creation changes

@@
 It can also be used by a registered corporate entity to automate formal governance rules contained in corporate bylaws or imposed by law.
-First the DAO Concept is described, then minority rights is discussed, and a solution to a ``robbing the minority'' attack vector isproposed.
+First the DAO concept is described, then minority rights is discussed, and a solution to a ``robbing the minority'' attack vector is proposed.
 Finally, a practical implementation of a first generation DAO entity is provided using smart contracts written in Solidity on the Ethereum blockchain.
@@
 \section{Token Price} \label{TokenPrice}
-DAO Token Creation schedule increases over time.
+DAO Token Creation rate decreases over time.
 This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO.
@@
 \end{equation}
-Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
-Hence the number of tokens (in its base unit) each buyer Creates is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel the DAO, denoted in wei.
+Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenCreation} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
+Hence the number of tokens (in its base unit) each person Creates is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel a DAO, denoted in wei.
 This results in a constant Creation rate in the beginning, until $2$ weeks before the end of the DAO Creation Phase.
-At this time the Creation rate increases daily by $0.05 \: \Xi_c$ per base unit of DAO token.
+At this time the amount of ether required to Create DAO tokens increases daily by $0.05 \: \Xi_c$ per base unit of DAO token.
 Until $4$ days before the closing time when there will be a constant Creation rate of $1.5 \: \Xi_c$ per base unit of DAO token.
 
-Creation rate increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens at the initial Creation rate, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having fueled a DAO at a higher Creation rate (\cite{GriffDiscussion}).
-In order to avoid that possibility, all ether that is used to fuel the DAO above the initial Creation rate, will be sent to an extra account.
-Denoted as \verb|extraBalance| in \ref{app:TokenSale}.
+Creation rate decreases during the Creation Phase could lead to a situation where a single contributor, having Created DAO tokens at the initial Creation rate, could split the DAO immediately after the Creation Phase ends, thereby receiving more ether than they put in due to other contributors having fueled a DAO at a higher Creation rate (\cite{GriffDiscussion}).
+In order to avoid that possibility, all ether that is used to fuel a DAO above the initial Creation rate, will be sent to an extra account.
+Denoted as \verb|extraBalance| in \ref{app:TokenCreation}.
 This ether can be sent back to the DAO through a proposal after the DAO has spent at least this amount of ether.
@@
 The main contract is called 'DAO'.
-It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenSale'.
-‘Token’ defines the inner workings of the DAO Token and ‘TokenSale’ defines how the DAO token is purchased for ether.
+It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenCreation'.
+‘Token’ defines the inner workings of the DAO Token and ‘TokenCreation’ defines how the DAO token is purchased for ether.
 In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
@@
 The map \verb|balances| stores the number of DAO tokens which are controlled by an address.
-All contracts which derive from \verb|TokenInterface| can directly modify this map, but only $4$ functions do so: \verb|buyTokenProxy|, \verb|transfer| , \verb|transferFrom| and \verb|splitDAO|.
+All contracts which derive from \verb|TokenInterface| can directly modify this map, but only $4$ functions do so: \verb|createTokenProxy|, \verb|transfer| , \verb|transferFrom| and \verb|splitDAO|.
 
@@
 
-\subsection{TokenSale}
+\subsection{TokenCreation}
 \begin{verbatim}
-contract TokenSaleInterface {
+contract TokenCreationInterface {
     uint public closingTime;   
@@
     bool public isFueled;
-    address public privateSale;
+    address public privateCreation;
     ManagedAccount extraBalance;
@@
 
-    function TokenSale(uint _minValue, uint _closingTime);
-    function buyTokenProxy(address _tokenHolder) returns (bool success);
+    function TokenCreation(uint _minValue, uint _closingTime);
+    function createTokenProxy(address _tokenHolder) returns (bool success);
     function refund();
@@
 
-    event FundingToDate(uint value);
-    event SoldToken(address indexed to, uint amount);
+    event FuelingToDate(uint value);
+    event CreatedToken(address indexed to, uint amount);
     event Refund(address indexed to, uint value);
@@
 \begin{multicols}{2}
-Above is the interface of the \verb|TokenSale| contract (\ref{app:TokenSale}).
-
-The integer \verb|closingTime| is the (unix) time at which the token sale ends.
+Above is the interface of the \verb|TokenCreation| contract (\ref{app:TokenCreation}).
+
+The integer \verb|closingTime| is the (unix) time at which the Creation Phase ends.
 
@@
 
-The address \verb|privateSale| is used for DAO splits - if it is set to 0, then it is a public sale, otherwise, only the address stored in \verb|privateSale| is allowed to purchase tokens.
-
-The managed account (\ref{app:ManagedAccount}) \verb|extraBalance| is used to hold the excess ether which is received after the token price is increased during the sale.
+The address \verb|privateCreation| is used for DAO splits - if it is set to 0, then it is a public Creation, otherwise, only the address stored in \verb|privateCreation| is allowed to purchase tokens.
+
+The managed account (\ref{app:ManagedAccount}) \verb|extraBalance| is used to hold the excess ether which is received after the Creation rate is decreased during the Creation Phase.
 Anything that has been paid above the initial price goes to this account.
 
-The map \verb|weiGiven| stores the amount of wei given by each contributor during the sale and is only used to refund the contributors if the Token sale does not reach its funding goal.
-
-The constructor \verb|TokenSale| initiates the token sale with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateSale|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed.
+The map \verb|weiGiven| stores the amount of wei given by each contributor during the Creation Phase and is only used to refund the contributors if the Creation Phase does not reach its funding goal.
+
+The constructor \verb|TokenCreation| initiates the Creation Phase with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateCreation|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed.
 In order to interact with the contract the following functions can be used:
 
-\subsubsection*{buyTokenProxy}
+\subsubsection*{createTokenProxy}
 This function creates one unit of the DAO token’s minimum denomination for every wei sent.
@@
 \subsubsection*{refund}
-This function can be called by any contributor to recieve their wei back if the token sale failed to meet its funding goal.
+This function can be called by any contributor to receive their wei back if the Creation Phase failed to meet its funding goal.
 
 \subsubsection*{divisor}
-This function is used to calculate the price of the token during the sale in the function \verb|buyTokenProxy|.
-
-The events \verb|FundingToDate|, \verb|SoldToken| and \verb|Refund| are used to inform lightweight clients of the status of the token sale.
+This function is used to calculate the price of the token during the Creation Phase in the function \verb|createTokenProxy|.
+
+The events \verb|FuelingToDate|, \verb|CreatedToken| and \verb|Refund| are used to inform lightweight clients of the status of the Creation Phase.
 \end{multicols}
@@
         uint _closingTime,
-        address _privateSale
+        address _privateCreation
     )
@@
  \item \verb|closingTime|
- \item \verb|privateSale|
+ \item \verb|privateCreation|
  \item \verb|lastTimeMinQuorumMet|
@@
 There are no direct arguments for this function.
-The fallback function will call \verb|buyTokenProxy| passing the address of the sender as an argument during the token sale.
+The fallback function will call \verb|createTokenProxy| passing the address of the sender as an argument during the Creation Phase.
 This will trigger the immediate purchase of tokens.
-In order to protect users, this function will send the ether received after the end of the sale back to the sender for a time period of $40$ days.
+In order to protect users, this function will send the ether received after the end of the Creation Phase back to the sender for a time period of $40$ days.
 After which this function is repurposed to receive ether as simple deposit to the DAO using the function \verb|receiveEther|.
@@
 Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
-This will be used to effectively buy tokens of the newly created DAO and fund the new DAO just as the original DAO was funded.
+This will be used to effectively create tokens in the newly created DAO and fuel the new DAO just as the original DAO was fueled.
 In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
@@
 
-\subsection{TokenSale}\label{app:TokenSale}
+\subsection{TokenCreation}\label{app:TokenCreation}
 \begin{verbatim}
-contract TokenSaleInterface {
-
-    // End of token sale, in Unix time
+contract TokenCreationInterface {
+
+    // End of token creation, in Unix time
     uint public closingTime;
-    // Minimum fueling goal of the token sale, denominated in ether
+    // Minimum fueling goal of the token creation, denominated in ether
     uint public minValue;
@@
     bool public isFueled;
-    // For DAO splits - if privateSale is 0, then it is a public sale, otherwise
-    // only the address stored in privateSale is allowed to purchase tokens
-    address public privateSale;
-    // hold extra ether which has been paid after the DAO token price has increased
+    // For DAO splits - if privateCreation is 0, then it is a public token
+    // creation, otherwise only the address stored in privateCreation is
+    // allowed to create tokens
+    address public privateCreation;
+    // hold extra ether which has been sent after the DAO token
+    // creation rate has increased
     ManagedAccount public extraBalance;
@@
     /// @dev Constructor setting the minimum fueling goal and the
-    /// end of the Token Sale
-    /// @param _minValue Token Sale minimum fueling goal
-    /// @param _closingTime Date (in Unix time) of the end of the Token Sale
-    /// @param _privateSale Zero means that the sale is public.  A non-zero
-    /// address represents the only address that can buy Tokens (the address
-    /// can also buy Tokens on behalf of other accounts)
+    /// end of the Token Creation
+    /// @param _minValue Token Creation minimum fueling goal
+    /// @param _closingTime Date (in Unix time) of the end of the Token Creation
+    /// @param _privateCreation Zero means that the creation is public.  A
+    /// non-zero address represents the only address that can create Tokens
+    /// (the address can also create Tokens on behalf of other accounts)
     // This is the constructor: it can not be overloaded so it is commented out
-    //  function TokenSale(
+    //  function TokenCreation(
         //  uint _minValue,
         //  uint _closingTime,
-        //  address _privateSale
+        //  address _privateCreation
     //  );
 
-    /// @notice Buy Token with `_tokenHolder` as the initial owner of the Token
+    /// @notice Create Token with `_tokenHolder` as the initial owner of the Token
     /// @param _tokenHolder The address of the Tokens's recipient
     /// @return Whether the purchase was successful
-    function buyTokenProxy(address _tokenHolder) returns (bool success);
-
-    /// @notice Refund `msg.sender` in the case the Token Sale didn't reach its
-    /// minimum fueling goal
+    function createTokenProxy(address _tokenHolder) returns (bool success);
+
+    /// @notice Refund `msg.sender` in the case the Token Creation did
+    /// not reach its minimum fueling goal
     function refund();
 
-    /// @return The divisor used to calculate the token price during the sale
+    /// @return The divisor used to calculate the token creation rate during
+    /// the creation phase
     function divisor() returns (uint divisor);
 
-    event FundingToDate(uint value);
-    event SoldToken(address indexed to, uint amount);
+    event FuelingToDate(uint value);
+    event CreatedToken(address indexed to, uint amount);
     event Refund(address indexed to, uint value);
@@
 
-contract TokenSale is TokenSaleInterface, Token {
-    function TokenSale(uint _minValue, uint _closingTime, address _privateSale) {
+contract TokenCreation is TokenCreationInterface, Token {
+    function TokenCreation(uint _minValue, uint _closingTime, address _privateCreation) {
         closingTime = _closingTime;
         minValue = _minValue;
-        privateSale = _privateSale;
+        privateCreation = _privateCreation;
         extraBalance = new ManagedAccount(address(this));
@@
 
-    function buyTokenProxy(address _tokenHolder) returns (bool success) {
+    function createTokenProxy(address _tokenHolder) returns (bool success) {
         if (now < closingTime && msg.value > 0
-            && (privateSale == 0 || privateSale == msg.sender)) {
+            && (privateCreation == 0 || privateCreation == msg.sender)) {
 
@@
             weiGiven[_tokenHolder] += msg.value;
-            SoldToken(_tokenHolder, token);
+            CreatedToken(_tokenHolder, token);
             if (totalSupply >= minValue && !isFueled) {
                 isFueled = true;
-                FundingToDate(totalSupply);
+                FuelingToDate(totalSupply);
             }
@@
             return 20;
-        // Followed by 10 days with a daily price increase of 5%
+        // Followed by 10 days with a daily creation rate increase of 5%
         } else if (closingTime - 4 days > now) {
             return (20 + (now - (closingTime - 2 weeks)) / (1 days));
-        // The last 4 days there is a constant price ratio of 1:1.5
+        // The last 4 days there is a constant creation rate ratio of 1:1.5
         } else {
@@
 
-    // The amount of days for which people who try to participate in the sale
-    // by calling the fallback function will still get their ether back
-    uint constant saleGracePeriod = 40 days;
+    // The amount of days for which people who try to participate in the
+    // creation by calling the fallback function will still get their ether back
+    uint constant creationGracePeriod = 40 days;
     // The minimum debate period that a generic proposal can have
@@
     uint constant quorumHalvingPeriod = 52 weeks;
-    // Period after which a proposal can be closed (used in the case `executeProposal`
-    // fails because it throws)
+    // Period after which a proposal can be closed
+    // (used in the case `executeProposal` fails because it throws)
     uint constant executeProposalPeriod = 5 days;
+    // Denotes the maximum proposal deposit that can be given. It is given as
+    // a fraction of total Ether spent plus balance of the DAO
+    uint constant maxDepositDivisor = 100;
 
@@
     // totalSupply / minQuorumDivisor
-    uint minQuorumDivisor;
+    uint public minQuorumDivisor;
     // The unix time of the last time quorum was reached on a proposal
-    uint lastTimeMinQuorumMet;
-
-    // Address of the Curator
+    uint  public lastTimeMinQuorumMet;
+
+    // Address of the curator
     address public curator;
@@
     /// for the contract able to create another DAO as well as the parameters
-    /// for the DAO Token Sale
+    /// for the DAO Token Creation
     /// @param _curator The Curator
@@
     /// @param _proposalDeposit The deposit to be paid for a regular proposal
-    /// @param _minValue Minimal value for a successful DAO Token Sale
-    /// @param _closingTime Date (in Unix time) of the end of the DAO Token Sale
-    /// @param _privateSale If zero the DAO Token Sale is open to public, a
-    /// non-zero address means that the DAO Token Sale is only for the address
+    /// @param _minValue Minimal value for a successful DAO Token Creation
+    /// @param _closingTime Date (in Unix time) of the end of the DAO Token Creation
+    /// @param _privateCreation If zero the DAO Token Creation is open to public, a
+    /// non-zero address means that the DAO Token Creation is only for the address
     // This is the constructor: it can not be overloaded so it is commented out
@@
         //  uint _closingTime,
-        //  address _privateSale
+        //  address _privateCreation
     //  );
 
-    /// @notice Buy Token with `msg.sender` as the beneficiary
+    /// @notice Create Token with `msg.sender` as the beneficiary
     /// @return Whether the purchase was successful
@@
     event NewCurator(address indexed _newCurator);
-    event AllowedRecipientAdded(address indexed _recipient);
+    event AllowedRecipientChanged(address indexed _recipient, bool _allowed);
 }
@@
 // The DAO contract itself
-contract DAO is DAOInterface, Token, TokenSale {
+contract DAO is DAOInterface, Token, TokenCreation {
 
@@
         uint _closingTime,
-        address _privateSale
-    ) TokenSale(_minValue, _closingTime, _privateSale) {
+        address _privateCreation
+    ) TokenCreation(_minValue, _closingTime, _privateCreation) {
 
@@
     function () returns (bool success) {
-        if (now < closingTime + saleGracePeriod)
-            return buyTokenProxy(msg.sender);
+        if (now < closingTime + creationGracePeriod)
+            return createTokenProxy(msg.sender);
         else
@@
         // in order to free the deposit and allow unblocking of voters
-        if (!allowedRecipients[p.recipient] && p.open) {
+        if (!isRecipientAllowed(p.recipient) && p.open) {
             closeProposal(_proposalID);
@@
             p.splitData[0].totalSupply;
-        if (p.splitData[0].newDAO.buyTokenProxy.value(fundsToBeMoved)(msg.sender) == false)
+        if (p.splitData[0].newDAO.createTokenProxy.value(fundsToBeMoved)(msg.sender) == false)
             throw;
@@
     function changeProposalDeposit(uint _proposalDeposit) noEther external {
-        if (msg.sender != address(this) || _proposalDeposit > actualBalance() / 10)
-            throw;
+        if (msg.sender != address(this) || _proposalDeposit > (actualBalance() + rewardToken[address(this)])
+            / maxDepositDivisor) {
+
+            throw;
+        }
         proposalDeposit = _proposalDeposit;
@@
         allowedRecipients[_recipient] = _allowed;
+        AllowedRecipientChanged(_recipient, _allowed);
         return true;
@@
 
-    function actualBalance() internal constant returns (uint _actualBalance) {
+    function actualBalance() constant returns (uint _actualBalance) {
         return this.balance - sumOfProposalDeposits;
@@
 }
-
 \end{verbatim}

### 2016-04-18 tests/scenarios/fuel_fail2/run.py

@@ -3,8 +3,8 @@ from utils import constrained_sum_sample_pos, arr_str
 
 
 scenario_description = (
-    "During the fueling period of the DAO, buy DAO tokens from all accounts "
-    "with both normal buying and with createTokenProxy(). When the goal "
+    "During the fueling period of the DAO, create DAO tokens from all accounts "
+    "with both normal creation and with createTokenProxy(). When the goal "
     "is not reached make sure that the refunds when having used "
     "createTokenProxy() are distributed back to the users correctly"
 )

### 2016-04-18 paper/Paper.tex
Purchase -> Create/Creation

@@
 A problem every DAO has to mitigate is the ability for the majority to rob the minority by changing governance and ownership rules after DAO formation.
-For example, an attacker with $51\%$ of the tokens, acquired either during the funding period or purchased afterwards, could make a proposal to send all the funds to themselves.
+For example, an attacker with $51\%$ of the tokens, acquired either during the fueling period or created afterwards, could make a proposal to send all the funds to themselves.
 Since they would hold the majority of the tokens, they would always be able to pass their proposals.
@@
 It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenCreation'.
-‘Token’ defines the inner workings of the DAO Token and ‘TokenCreation’ defines how the DAO token is purchased for ether.
+‘Token’ defines the inner workings of the DAO Token and ‘TokenCreation’ defines how the DAO token is created by fueling the DAO with ether.
 In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
@@
 
-The address \verb|privateCreation| is used for DAO splits - if it is set to 0, then it is a public Creation, otherwise, only the address stored in \verb|privateCreation| is allowed to purchase tokens.
+The address \verb|privateCreation| is used for DAO splits - if it is set to 0, then it is a public Creation, otherwise, only the address stored in \verb|privateCreation| is allowed to create tokens.
 
@@
 This function creates one unit of the DAO token’s minimum denomination for every wei sent.
-The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $20 / P(t)$ , as described in section \ref{TokenPrice}.
+The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to create tokens, and \verb|divisor| is calculated depending on the time: $20 / P(t)$ , as described in section \ref{TokenPrice}.
 The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.
@@
 The fallback function will call \verb|createTokenProxy| passing the address of the sender as an argument during the Creation Phase.
-This will trigger the immediate purchase of tokens.
+This will trigger the immediate creation of tokens.
 In order to protect users, this function will send the ether received after the end of the Creation Phase back to the sender for a time period of $40$ days.
@@
     /// @param _tokenHolder The address of the Tokens's recipient
-    /// @return Whether the purchase was successful
+    /// @return Whether the token creation was successful
     function createTokenProxy(address _tokenHolder) returns (bool success);
@@
     /// @notice Create Token with `msg.sender` as the beneficiary
-    /// @return Whether the purchase was successful
+    /// @return Whether the token creation was successful
     function () returns (bool success);

### 2016-04-18 tests/scenarios/fuel/run.py

@@ -4,7 +4,7 @@ from utils import constrained_sum_sample_pos, arr_str
 
 scenario_description = (
     "During the fueling period of the DAO, send enough ether from all "
-    "accounts to purchase tokens and then assert that the user's balance is "
+    "accounts to create tokens and then assert that the user's balance is "
     "indeed correct and that the minimum fueling goal has been reached"
 )
 

### 2016-04-18 tests/scenarios/fuel/template.js

@@ -23,7 +23,7 @@ setTimeout(function() {
     }
     addToTest('balances', balances);
 
-    // now also try to purchase some extra tokens after the creation ended
+    // now also try to create some extra tokens after the creation ended
     // note we use createTokenProxy() directly because with the edited code
     // for the test the fallback function becomes a DAO donation code right
     // after the end of the creation period

### 2016-04-18 paper/Paper.tex
funding -> fueling

@@
 DAO Token Creation rate decreases over time.
-This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO.
+This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full fueling of the DAO.
 The DAO described in this paper has the following Creation schedule:
@@
 \end{equation}
-Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenCreation} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
+Here $t$ is the unix time in seconds, $t_c$ is the closing time of the fueling period (see \ref{app:TokenCreation} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
 Hence the number of tokens (in its base unit) each person Creates is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel a DAO, denoted in wei.
@@
 
-The map \verb|weiGiven| stores the amount of wei given by each contributor during the Creation Phase and is only used to refund the contributors if the Creation Phase does not reach its funding goal.
+The map \verb|weiGiven| stores the amount of wei given by each contributor during the Creation Phase and is only used to refund the contributors if the Creation Phase does not reach its fueling goal.
 
@@
 \subsubsection*{refund}
-This function can be called by any contributor to receive their wei back if the Creation Phase failed to meet its funding goal.
+This function can be called by any contributor to receive their wei back if the Creation Phase failed to meet its fueling goal.
 

### 2016-04-18 tests/scenarios/fuel_fail2/run.py
Rename minValue to better reflect fueling goal
`minValue` was introduced as the value in ether the DAO needs to accumulate
in order to be considered fueled. With the extra balance also taking in
ether and not counting towards the `totalSupply` this is inaccurate.

For this reason we rewrite the `minValue` as `minTokensToCreate` and
interpret it as the minimum amount of wei-equivalent tokens that the DAO
needs to create in order to be considered fueled.

There is also a fix for the extra balance fueling test which was failing
1 in 3 times exactly because the `minValue` goal was denominated in w

@@ -14,12 +14,12 @@ def run(ctx):
     ctx.assert_scenario_ran('deploy')
 
     accounts_num = len(ctx.accounts)
-    if accounts_num * 2 >= ctx.args.deploy_min_value - 4:
+    if accounts_num * 2 >= ctx.args.deploy_min_tokens_to_create - 4:
         print("Please increase the minimum fueling goal for the scenario.")
         sys.exit(1)
 
     creation_secs = ctx.remaining_time()
-    total_supply = ctx.args.deploy_min_value - 4
+    total_supply = ctx.args.deploy_min_tokens_to_create - 4
     proxy_amounts = constrained_sum_sample_pos(
         accounts_num, total_supply / 2
     )

### 2016-04-19 paper/Paper.tex

@@
     uint public closingTime;   
-    uint public minValue;  
+    uint public minTokensToCreate;
     bool public isFueled;
@@
 
-    function TokenCreation(uint _minValue, uint _closingTime);
+    function TokenCreation(uint _minTokensToCreate, uint _closingTime);
     function createTokenProxy(address _tokenHolder) returns (bool success);
@@
 
-The integer \verb|minValue| is the number of wei which are needed to be received by the DAO in order to get funded.
+The integer \verb|minTokensToCreate| is the number of wei-equivalent tokens which are needed to be created by the DAO in order to be considered fueled.
 
@@
 
-The constructor \verb|TokenCreation| initiates the Creation Phase with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateCreation|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed.
+The constructor \verb|TokenCreation| initiates the Creation Phase with the arguments \verb|minTokensToCreate|, \verb|closingtime| and \verb|privateCreation|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed.
 In order to interact with the contract the following functions can be used:
@@
         uint _proposalDeposit,
-        uint _minValue,
+        uint _minTokensToCreate,
         uint _closingTime,
@@
  \item \verb|DAOrewardAccount|
- \item \verb|minValue|
+ \item \verb|minTokensToCreate|
  \item \verb|closingTime|
@@
     uint public closingTime;
-    // Minimum fueling goal of the token creation, denominated in ether
-    uint public minValue;
+    // Minimum fueling goal of the token creation, denominated in tokens to
+    // be created
+    uint public minTokensToCreate;
     // True if the DAO reached its minimum fueling goal, false otherwise
@@
     /// end of the Token Creation
-    /// @param _minValue Token Creation minimum fueling goal
+    /// @param _minTokensToCreate Minimum required wei-equivalent tokens
+    ///        to be created for a successful DAO Token Creation
     /// @param _closingTime Date (in Unix time) of the end of the Token Creation
@@
     //  function TokenCreation(
-        //  uint _minValue,
+        //  uint _minTokensTocreate,
         //  uint _closingTime,
@@
 contract TokenCreation is TokenCreationInterface, Token {
-    function TokenCreation(uint _minValue, uint _closingTime, address _privateCreation) {
+    function TokenCreation(
+        uint _minTokensToCreate,
+        uint _closingTime,
+        address _privateCreation) {
+
         closingTime = _closingTime;
-        minValue = _minValue;
+        minTokensToCreate = _minTokensToCreate;
         privateCreation = _privateCreation;
-        extraBalance = new ManagedAccount(address(this));
+        extraBalance = new ManagedAccount(address(this), true);
     }
@@
             CreatedToken(_tokenHolder, token);
-            if (totalSupply >= minValue && !isFueled) {
+            if (totalSupply >= minTokensToCreate && !isFueled) {
                 isFueled = true;
@@
     /// @param _proposalDeposit The deposit to be paid for a regular proposal
-    /// @param _minValue Minimal value for a successful DAO Token Creation
+    /// @param _minTokensToCreate Minimum required tokens to be created
+    ///        for a successful DAO Token Creation
     /// @param _closingTime Date (in Unix time) of the end of the DAO Token Creation
@@
         //  uint _proposalDeposit,
-        //  uint _minValue,
+        //  uint _minTokensToCreate,
         //  uint _closingTime,
@@
         uint _proposalDeposit,
-        uint _minValue,
+        uint _minTokensToCreate,
         uint _closingTime,
         address _privateCreation
-    ) TokenCreation(_minValue, _closingTime, _privateCreation) {
+    ) TokenCreation(_minTokensToCreate, _closingTime, _privateCreation) {
 
@@
         proposalDeposit = _proposalDeposit;
-        rewardAccount = new ManagedAccount(address(this));
-        DAOrewardAccount = new ManagedAccount(address(this));
+        rewardAccount = new ManagedAccount(address(this), false);
+        DAOrewardAccount = new ManagedAccount(address(this), false);
         if (address(rewardAccount) == 0)
@@
         uint _proposalDeposit,
-        uint _minValue,
+        uint _minTokensToCreate,
         uint _closingTime
@@
             _proposalDeposit,
-            _minValue,
+            _minTokensToCreate,
             _closingTime,

### 2016-04-19 tests/scenarios/extrabalance/run.py
Create 'spendall` pivot test scenario
- Created a test scenario to spend all of the DAO's money that will act
  as a pivot for all tests dealing with extraBalance.

@@ -1,13 +1,13 @@
 from utils import calculate_bytecode, to_wei
 
 scenario_description = (
-    "The DAO spends all its money and has to resort to retrieving money from "
+    "The DAO spent all its money and has to resort to retrieving money from "
     "the extra balance account. This test checks that this is succesful."
 )
 
 
 def run(ctx):
-    ctx.assert_scenario_ran('fuel')
+    ctx.assert_scenario_ran('spendall')
     extra_balance_ether_to_get = 5
     bytecode = calculate_bytecode(
         'payOut',

### 2016-04-19 tests/scenarios/extrabalance/template.js

@@ -1,24 +1,23 @@
 var dao = web3.eth.contract($dao_abi).at('$dao_address');
 
-addToTest('dao_total_balance_before', web3.fromWei(eth.getBalance(dao.address)));
+addToTest('dao_total_balance_before', web3.fromWei(dao.actualBalance()));
 
-var prop_id = attempt_proposal(
+var extraBalance = dao.extraBalance();
+var claim_prop_id = attempt_proposal(
     dao, // DAO in question
-    curator, // recipient
+    extraBalance, // recipient
     proposalCreator, // proposal creator
-    web3.fromWei(dao.totalSupply())-10, // proposal amount in ether
-    'Spend almost all of the DAOs money', // description
-    '', //bytecode
+    0, // proposal amount in ether
+    'Ask the extraBalance account to pay out to the DAO', // description
+    '$transaction_bytecode', // transaction bytecode
     $debating_period, // debating period
     $proposal_deposit, // proposal deposit in ether
     false // whether it's a split proposal or not
 );
-
-
-console.log("Deadline is: " + dao.proposals(prop_id)[3] + " Voting ... ");
+console.log("Voting on the extra balance payout proposal");
 for (i = 0; i < eth.accounts.length; i++) {
     dao.vote.sendTransaction(
-        prop_id,
+        claim_prop_id,
         true,
         {
             from: eth.accounts[i],
@@ -30,63 +29,23 @@ checkWork();
 
 setTimeout(function() {
     miner.stop(0);
-    console.log("After spending debating period. NOW is: " + Math.floor(Date.now() / 1000));
+    console.log("After extra balance payout debating period. NOW is: " + Math.floor(Date.now() / 1000));
     attempt_execute_proposal(
         dao, // target DAO
-        prop_id, // proposal ID
-        '', // transaction bytecode
+        claim_prop_id, // proposal ID
+        '$transaction_bytecode', // transaction bytecode
         proposalCreator, // proposal creator
         true // should the proposal pass?
     );
 
-    addToTest('dao_total_balance_after_spend', web3.fromWei(dao.actualBalance()));
+    addToTest('dao_total_balance_after_claim', web3.fromWei(dao.actualBalance()));
+    addToTest('dao_balance_diff_after_claim',
+              testMap['dao_total_balance_after_claim'].sub(
+                  testMap['dao_total_balance_before']
+              ).round());
 
-    var extraBalance = dao.extraBalance();
-    var claim_prop_id = attempt_proposal(
[…]

### 2016-04-19 tests/scenarios/spendall/template.js

@@ -1,0 +1,46 @@
+var dao = web3.eth.contract($dao_abi).at('$dao_address');
+
+addToTest('dao_total_balance_before_spend', web3.fromWei(dao.actualBalance()));
+
+var prop_id = attempt_proposal(
+    dao, // DAO in question
+    curator, // recipient
+    proposalCreator, // proposal creator
+    web3.fromWei(dao.totalSupply()), // proposal amount in ether
+    'Spend almost all of the DAOs money', // description
+    '', //bytecode
+    $debating_period, // debating period
+    $proposal_deposit, // proposal deposit in ether
+    false // whether it's a split proposal or not
+);
+
+
+console.log("Deadline is: " + dao.proposals(prop_id)[3] + " Voting ... ");
+for (i = 0; i < eth.accounts.length; i++) {
+    dao.vote.sendTransaction(
+        prop_id,
+        true,
+        {
+            from: eth.accounts[i],
+            gas: 1000000
+        }
+    );
+}
+checkWork();
+
+setTimeout(function() {
+    miner.stop(0);
+    console.log("After spending debating period. NOW is: " + Math.floor(Date.now() / 1000));
+    attempt_execute_proposal(
+        dao, // target DAO
+        prop_id, // proposal ID
+        '', // transaction bytecode
+        proposalCreator, // proposal creator
+        true // should the proposal pass?
+    );
+
+    addToTest('dao_total_balance_after_spend', web3.fromWei(dao.actualBalance()));
+    testResults();
+}, ($debating_period) * 1000);
+console.log("Wait for end of debating period for spending all of the DAO's money");
+miner.start(1);

### 2016-04-19 tests/test.py

@@ -210,6 +210,9 @@ class TestContext():
         output = self.run_script('{}.js'.format(self.running_scenario()))
         return eval_test(self.running_scenario(), output, expected)
 
+    def scenario_uses_extrabalance(self):
+        return ctx.args.scenario in ["extrabalance"]
+
     def running_scenario(self):
         """Get the currently running scenario name"""
         return self.running_scenarios[-1]

### 2016-04-19 tests/jsutils.py
Add extraBalance stealing test
- Added a test that tries to steal the extraBalance() by providing their
  own address in the transaction byte code.

- All `attempt_execute_function_proposal()` calls have been amended to
  include an extra parameter: `expect_closed`. This allows us to use the
  function also when we expect the proposal execution to throw and as
  such leave the proposal open.

@@ -123,6 +123,7 @@ function attempt_execute_proposal(
     prop_id,
     bytecode,
     prop_creator,
+    expect_closed,
     expect_pass) {
     desc = argdao.proposals(prop_id)[2];
     vote_deadline = argdao.proposals(prop_id)[3];
@@ -138,10 +139,11 @@ function attempt_execute_proposal(
         {from: prop_creator, gas:4000000}
     );
     checkWork();
-    if (argdao.proposals(prop_id)[4] == true) {
+    if (argdao.proposals(prop_id)[4] == expect_closed) {
         testFail(
-            "Failed to execute proposal for: '" +desc +"'. Proposal is still "+
-            "open. Perhaps provide more gas?"
+            "Failed to execute proposal for: '" +desc +"'. Expected the " +
+            "proposal to be " + (expect_closed ? "closed" : "open") +
+            " but it's not"
         );
     }
     if (argdao.proposals(prop_id)[5] != expect_pass) {

### 2016-04-19 tests/scenarios/colmattack/template.js

@@ -70,6 +70,7 @@ setTimeout(function() {
             attack_prop_id, // proposal ID
             '', // transaction bytecode
             attacker, // proposal creator
+            true, // should the proposal be closed after this call?
             true // should the proposal pass?
         );
 

### 2016-04-19 tests/scenarios/deposit/template.js

@@ -30,6 +30,7 @@ setTimeout(function() {
         prop_id, // proposal ID
         '$transaction_bytecode', // transaction bytecode
         curator, // proposal creator
+        true, // should the proposal be closed after this call?
         true // should the proposal pass?
     );
 

### 2016-04-19 tests/scenarios/newcontractfail/template.js

@@ -41,6 +41,7 @@ setTimeout(function() {
         prop_id, // proposal ID
         '$transaction_bytecode', // transaction bytecode
         curator, // proposal creator
+        false, // should the proposal be closed after this call?
         false // should the proposal pass?
     );
 

### 2016-04-19 tests/scenarios/proposal/template.js

@@ -56,6 +56,7 @@ setTimeout(function() {
         prop_id, // proposal ID
         '$transaction_bytecode', // transaction bytecode
         curator, // proposal creator
+        true, // should the proposal be closed after this call?
         true // should the proposal pass?
     );
 

### 2016-04-19 tests/scenarios/spendall/template.js

@@ -36,6 +36,7 @@ setTimeout(function() {
         prop_id, // proposal ID
         '', // transaction bytecode
         proposalCreator, // proposal creator
+        true, // should the proposal be closed after this call?
         true // should the proposal pass?
     );
 

### 2016-04-19 tests/test.py

@@ -211,7 +211,11 @@ class TestContext():
         return eval_test(self.running_scenario(), output, expected)
 
     def scenario_uses_extrabalance(self):
-        return ctx.args.scenario in ["extrabalance"]
+        """
+        Check if the target scenario requires late sale, in order to
+        populate the extraBalance account
+        """
+        return ctx.args.scenario in ["extrabalance", "stealextrabalance"]
 
     def running_scenario(self):
         """Get the currently running scenario name"""

### 2016-04-19 paper/Paper.tex
Update WP and increase execute proposal period
- Increased the possible period after the voting deadline at which a
  proposal can be executed to 10 days.

- Added extra `if p.open` check to save gas

- Updated the whitepaper with the changes this PR introduces

@@
 
-\subsubsection*{emergenyCloseProposal}
-This is used in the case `executeProposal` fails because it throws (e.g.
-when returuning the deposit, because the fallback function of this address throws, or when executing the proposed transaction).
-It can be called $5$ days after the voting deadline of the proposal passed.
-It will close the proposal.
 \subsubsection*{splitDAO}
@@
     uint constant quorumHalvingPeriod = 52 weeks;
-    // Period after which a proposal can be closed
+    // Period after which a proposal is closed
     // (used in the case `executeProposal` fails because it throws)
-    uint constant executeProposalPeriod = 5 days;
+    uint constant executeProposalPeriod = 10 days;
     // Denotes the maximum proposal deposit that can be given. It is given as
@@
 
-    /// @notice close the proposal (used in the case `executeProposal`
-    /// fails because it throws)
-    /// @param _proposalID The proposal ID
-    function emergenyCloseProposal(uint _proposalID) external;
-
     /// @notice ATTENTION! I confirm to move my remaining ether to a new DAO
@@
 
-        if (p.newCurator) {
-            if (now > p.votingDeadline + splitExecutionPeriod) {
-                p.open = false;
-            }
+        uint waitPeriod = p.newCurator
+            ? splitExecutionPeriod
+            : executeProposalPeriod;
+        // If we are over deadline and waiting period, assert proposal is closed
+        if (p.open && now > p.votingDeadline + waitPeriod) {
+            closeProposal(_proposalID);
             return;
@@
         p.open = false;
-    }
-
-    function emergenyCloseProposal(uint _proposalID) external {
-        Proposal p = proposals[_proposalID];
-        if (p.votingDeadline + executeProposalPeriod < now && p.open)
-            closeProposal(_proposalID);
     }

### 2016-04-19 tests/scenarios/depositnofunds/template.js
Test changing deposit when DAO is out of funds
Test that the changes introduced in commit
92beee5d27f66793689448903872302d0f4a6287 work correctly

@@ -1,0 +1,40 @@
+var dao = web3.eth.contract($dao_abi).at('$dao_address');
+var prop_id = attempt_proposal(
+    dao, // DAO in question
+    dao.address, // recipient
+    proposalCreator, // proposal creator
+    0, // proposal amount in ether
+    'Changing proposal deposit', // description
+    '$transaction_bytecode', //bytecode
+    $debating_period, // debating period
+    $proposal_deposit, // proposal deposit in ether
+    false // whether it's a split proposal or not
+);
+
+// in this scenario all users vote for the change
+for (i = 0; i < eth.accounts.length; i++) {
+    dao.vote.sendTransaction(
+        prop_id,
+        true,
+        {
+            from: eth.accounts[i],
+            gas: 1000000
+        }
+    );
+}
+checkWork();
+setTimeout(function() {
+    miner.stop(0);
+    attempt_execute_proposal(
+        dao, // target DAO
+        prop_id, // proposal ID
+        '$transaction_bytecode', // transaction bytecode
+        curator, // proposal creator
+        true, // should the proposal be closed after this call?
+        true // should the proposal pass?
+    );
+
+    addToTest('deposit_after_vote', parseInt(dao.proposalDeposit()));
+    testResults();
+}, $debating_period * 1000);
+miner.start(1);

### 2016-04-19 paper/Paper.tex
Generic > Standard

@@
 This paper illustrates a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2)  governance rules are formalized, automated and enforced using software.
-Specifically, generic smart contract code (\cite{szabo1997formalizing, miller1997future}) has been written that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain.
+Specifically, standard smart contract code (\cite{szabo1997formalizing, miller1997future}) has been written that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain.
 This paper explains how a DAO's code works, focusing on some basic formation and governance features, including structure, creation and voting rights.

### 2016-04-19 paper/Paper.tex
remove emergencyClose from interface

--- 2016-04-19 paper/Paper.tex
@@
     ) returns (bool _success);
-    function emergenyCloseProposal(uint _proposalID) external;
     function splitDAO(

### 2016-04-30 paper/Paper.tex

@@
 \end{equation}
-Here $P_{\text{from}}$ is the total amount of ether which has been paid out to the \verb|from| address (the sender), $T_{\text{amount}}$ is the amount of tokens to be transferred and $T_{\text{from}}$ the amount of tokens owned by the \verb|from| address.
+Here $P_{\text{from}}$ is the total amount of ether which has been paid out to the \verb|from| address (the sender), $T_{\text{amount}}$ is the amount of tokens to be transferred and $T_{\text{from}}$ is the amount of tokens owned by the \verb|from| address.
 
@@
 
-This process allows DAO token holders to retrieve their ether from the DAO at any time without losing out on any of the future rewards they are entitled to receive even if they choose to leave the DAO.
+This process allows DAO token holders to retrieve their ether from the DAO at any time without losing out on any of the future rewards.They are entitled to receive even if they choose to leave the DAO.
 
